\section{Just enough category theory to be dangerous}
\subsection{Categories and functors}
\begin{exer}[1.1.A] Groupoids.
    \begin{enumerate}[(a)]
        \item Make sense of the statement ``a group is a groupoid with one element.''
        \begin{soln}
            Let $\mathcal{G}$ be a one element groupoid, call the single element $x$. Then by definition the identity morphism is in $\hom_\mathcal{G}(x,x)$. We will take this to be the identity element of the group $\hom_\mathcal{G}(x,x)$. Any two morphisms are composable, which gives the group composition, and by definition of groupoid any morphism is invertible, yielding the group inverse.

            Conversely, if we have a group $G$ we can make a category with one object whose morphisms are the elements of $G$, and whose identity, composition, and inverses are given by the group structure. This yields a groupoid.
        \end{soln}
        \item Give an example of a groupoid that is not a group.
        \begin{soln}
        A category with more than one object, and only the identity morphisms. 
        \end{soln}
    \end{enumerate}
\end{exer}

\begin{exer}[1.1.B] If $A$ is an object in a category $\mathcal{C}$, show that the invertible elements of $\hom_{\mathcal{C}}(A,A)$ form a group, called the automorphism group. What are the automorphism groups in $\catname{Set}$ and $\catname{Vect}_k$?
    \begin{proof}
    This is exactly the same as part 1 above. The identity morphism serves as the identity, the inverse morphisms yield the group inverses, and the category axioms yield composition. 
    
    The automorphism groups in $\catname{Set}$ are the symmetric groups, and the automorphism groups in $\catname{Vect}_k$ are the general linear groups.
    \end{proof}
\end{exer}

\begin{exer}[1.1.C.] Fix a field $k$. Let $(-)^{\vee\vee}$ be the double dual functor from the category of finite-dimensional $k$-vector spaces to itself. Show that $(-)^{\vee\vee}$ is naturally isomorphic to the identity functor.
    \begin{proof}
    For a fixed vector space $V$, define the map $\alpha_V: V \to V^{\vee\vee} $ by $v \mapsto (\phi\mapsto \phi(v))$. This is injective because if $\phi \mapsto \phi(v)$ is the zero map for every $\phi$, then $v=0$, so by finite-dimensionality $\alpha_V$ is an isomorphism. And it remains to check that for any map of vector spaces $f: V\to W$ and $v \in V$, that 
    \begin{align*}
        \alpha_W(f(v)) &= (\phi \mapsto \phi(f(v))) \\
        &= (\psi \mapsto \psi(v)) \circ f^\vee \\
        &= f^{\vee\vee}(\psi \mapsto \psi(v)) \\
        &= f^{\vee\vee}(\alpha_V(v))
    \end{align*}
    which completes the proof.
    \end{proof}
\end{exer}

\begin{exer}[1.1.D] Let $\mathcal{V}$ be the category whose objects are the $k$-vector spaces $k^n$ for $n\geq 0$, and whose morphisms are linear transformations. There is a functor $F$ from $\mathcal{V}$ to the category of f.d. $k$-vector spaces sending each vector space to itself. Show that $F$ is an equivalence of categories.
    \begin{proof}
    Following Vakil's remark about ignoring set-theoretic conditions, choose a basis for each finite dimensional $k$-vector space. For any vector space of the form $k^n$, choose the standard basis $\{e_i\}$.
    
    Then define a functor $G$ from f.d. $k$-vector spaces to $\mathcal{V}$ by sending an $n$-dimensional $k$-vector space to $k^n$. For a morphism $\phi$ from $V$ to an $m$-dimensional vector space $W$, let $\{v_1, ..., v_n\}$ be the chosen basis for $V$ and $\{w_1, ..., w_m\}$ the chosen basis for $W$. Then define $G\phi$ to be the matrix whose $(i,j)$th entry is the coefficient of $w_j$ in $\phi(v_i)$. 
    
    Define a natural transformation $\alpha$ from $FG$ to the identity functor where $\alpha_V: FGV \to V$ sends $FGV = k^n$ to $V$ by mapping the standard basis vector $e_i$ of $FGV$ to the chosen $i$th basis vector $v_i$ of $V$. Then $\alpha_V$ is an isomorphism. For naturality, we have for a map $\phi: V\to W$ that
    \begin{align*}
        \phi(\alpha_V(e_i)) &=\phi(v_i) \\
        &= \sum_j (G\phi)_{i,j} w_j \\
        &= \alpha_W(\sum_j(G\phi)_{i,j}e_j) \\
        &=\alpha_W (FG \phi)(e_i).
    \end{align*}
    In the other direction, $GF$ is the identity functor, which completes the proof.
    \end{proof}
\end{exer}

\subsection{Universal properties determine an object up to unique
isomorphism}
\begin{exer}[1.2.A] Show that any two initial objects are uniquely isomorphic, and any two final objects are uniquely isomorphic.
    \begin{proof}
    Let $i_1, i_2$ be initial. Then there is exactly one map $f_{12}: i_1 \to i_2$ and likewise $f_{21}: i_2 \to i_1$. Since there is also exactly one map from $i_1$ to itself, the identity, so because $f_{21}\circ f_{12}$ is one such map, it must be the identity. Likewise $f_{12}\circ f_{21}$ is the identity, which yields the unique isomorphisms. The argument is exactly the same for final objects.
    \end{proof}
\end{exer}
\begin{exer}[1.2.B]
What are the initial and final objects (if they exist) in $\catname{Ring}$, $\catname{Set}$, and $\catname{Top}$, or the category of subsets of a set under inclusion, or the category of open subsets of a topological space under inclusion?
\begin{soln}
In $\catname{Ring}$, the initial object is the integers, since $1$ mapping to $1$ dictates where the remaining integers go; the terminal object is the zero ring, since everything must map to zero. In $\catname{Set}$, the initial object is the empty set; the final object is the singleton. In $\catname{Top}$, the initial object is the empty space; the final object is the singleton. In the category of subsets or open sets, the initial object is the empty set/space; the terminal object is the entire set/space.
\end{soln}
\end{exer}

\begin{exer}[1.2.C]
    Let $A$ be a commutative ring and $S$ a multiplicative subset of $A$. Show that $f: A \mapsto S^{-1}A$ via $a \mapsto a/1$ is injective if and only if $S$ contains no zerodivisors.
    \begin{proof}
    First suppose $f$ is not injective, i.e. there is a nonzero element $a \in A$ such that $a/1 = 0/1$. So there exists some $s \in S$ such that $s(a1 - 01) = sa = 0$. Then $s$ is a zerodivisor. 

    Conversely, suppose $S$ contains a zerodivisor $s$, with $st = 0$ for $t$ nonzero. Then $0 = st = s(t1-01)$, $t/1 = 0/1 =0$, so $f(t) = t/1 = 0/1$ and $f$ fails to be injective.
    \end{proof}
\end{exer}

\begin{exer}[1.2.D] Verify that $\iota: A\to S^{-1}A$ is initial among $A$-algebras $B$ where every element of $S$ is sent to an invertible element in $B$, i.e. any map $\phi: A\to B$ sending all elements of $S$ to invertible elements in $B$ factors through $S^{-1}A$.
    \begin{proof}
        Define $\tilde{\phi}: S^{-1}A  \to B$ via $\tilde{\phi}(a/s) := \phi(a)\phi(s)^{-1}$. This makes sense since we have assumed that $\phi(s)$ is invertible. Let $a, b \in A$ and $s,t \in S$. Then 
        \[\tilde{\phi}(ab/st) = \phi(ab)\phi(st)^{-1} = \phi(a)\phi(b)\phi(s)^{-1}\phi(t)^{-1} = \tilde{\phi}(a/s) \tilde{\phi}(b/t)\]
        and 
        \begin{align*}
        \tilde{\phi}(a/s + b/t) &= \tilde{\phi}((at+sb)/st) \\
        &= \phi(at+sb)\phi(st)^{-1} \\
        &= \phi(a)\phi(t)/\phi(s)\phi(t)+\phi(s)\phi(b)/\phi(s)\phi(t) \\
        &= \tilde{\phi}(a/s) + \tilde{\phi}(b/t).
        \end{align*}
        so $\tilde{\phi}$ is a ring homomorphism. And $\tilde{\phi}(\iota(a)) = \tilde{\phi}(a/1) = \phi(a)/\phi(1) = \phi(a)$ as desired. 
    \end{proof}
\end{exer}

\begin{exer}[1.2.E] The localization of an $A$-module $M$ defined via the universal property, actually exists.
    \begin{proof}
        Following the hint, define $S^{-1}M$ to have elements of the form $m/s$ where $m \in M$ and $s \in S$, subject to the equivalence relation where $m/s \sim m'/t$ if there exists an element $s' \in S$ such that $s'(ms - m't) = 0$, with the standard operation and $S^{-1}A$-module operation. Define $\iota: M\to S^{-1}M$ via $m \mapsto m/1$. 

        Let $\phi: M \to N$ be an $A$-module map such that multiplication by any element of $s$ is an isomorphism $N\to N$. Then we can define a map $\tilde{\phi}: S^{-1}M\to N$ via $m/s \mapsto s^{-1}\phi(m)$, which makes sense taking $s^{-1}$ to be the inverse to multiplication by $s$. This is an $A$-module map and $\tilde{\phi}(\iota(m)) = \tilde{\phi}(a/1) = 1^{-1}\phi(a) = \phi(a)$.
    \end{proof}
\end{exer}

\begin{exer}[1.2.F] Properties of localization.
    \begin{enumerate}[(a)]
        \item Localization commutes with finite products, i.e. for $A$-modules $M_1, ..., M_n$ provide an $A$-module isomorphism $S^{-1}(M_1\times \cdots M_n) \to S^{-1}M_1\times \cdots \times S^{-1}M_n$. 
        \begin{proof}
            Define our map via $(m_1, ..., m_n)/s\mapsto (m_1/s, ..., m_n/s)$. For surjectivity, given an element $(m_1/s_1, ..., m_n/s_n)$, the element
            \[(s_2\cdots s_nm_1, ..., s_1 \cdots s_{n-1}m_n)/s_1\cdots s_n\]
            will map to it. For injectivity, suppose $(m_1/s, ..., m_n/s)$ is zero, i.e. there exist elements $t_i \in S$ such that $t_im_i = 0$ for all $i$. Then  $t_1\cdots t_n(m_1, ..., m_n) = 0$, so $(m_1, ..., m_n)/s = 0$.
        \end{proof}
        \item Localization commutes with arbitrary direct sums.
        \begin{proof}
            Let $\Lambda$ be an indexing set. Define a map $S^{-1} (\bigoplus_{\lambda \in \Lambda} M_\lambda) \to \bigoplus_{\lambda \in \Lambda} S^{-1}M_{\lambda}$ via 
            \[(m_\lambda)_{\lambda \in \Lambda}/s \mapsto (m_\lambda/s)_{\lambda \in \Lambda}.\]
            For surjectivity, given an element $(m_\lambda / s_\lambda)_{\lambda \in \Lambda}$, we know that only finitely many indices are nonzero, say $\lambda_1, ..., \lambda_k$. Then let $s= \lambda_1\cdots \lambda_k$, and consider the element $(k_\lambda m_\lambda)_{\lambda \in \Lambda}$ where $k_{\lambda_i} = s/s_i$ for the nonzero indices and zero otherwise. Then it maps to what we want. For injectivity, suppose $(m_\lambda/s)_{\lambda \in \Lambda}$ is zero, i.e. there exist elements $t_\lambda$ such that $t_\lambda m_\lambda = 0$ for all $\lambda$. Again only finitely many of the $m_\lambda$ are nonzero, so take the corresponding $t_\lambda$ and let their product be $t$. Then $t(m_\lambda)_{\lambda \in \Lambda} = 0$ and we are done.
        \end{proof}
        \item Localization does not commute with infinite products, i.e. the same map defined as above is not always an isomorphism for infinite products. 
        \begin{proof}
            We know that $\Z$ localized at $\Z\setminus \{0\}$ is $\Q$, so that $\prod_{\N}\Q$ contains for example the element $x:= (1, 1/2, 1/3, ...)$. On the other hand, suppose there were an element in $(\Z\setminus \{0\})^{-1} (\Z^\N)$ mapping to $x$, i.e. some element $(a_1, a_2, ...)/s$ where $a_i \in \Z$ and $s \in \Z\setminus \{0\}$ such that $a_n/s = 1/n$ for all $n \in \N$. Then $na_n = s$ for all $n \in \N$, i.e. $s$ is an integer divisible by all natural numbers, a contradiction.
        \end{proof}
    \end{enumerate}
\end{exer}

\begin{exer}[1.2.G] Show that $\Z/10 \tensor \Z/12 \cong \Z/2$.
    \begin{proof}
        We define a map $\tilde{f}: \Z/10 \times \Z/12 \to \Z/2$ via $([a],[b]) \mapsto [ab]$. This is clearly bilinear. If $a=a'+10n$ and $b  = b'+12m$, so $[ab] = [a'b'+12ma'+10nb'+120nm] = [a'b']$ in $\Z/2$, so this map is well defined. By the universal property of tensor products, $f$ factors through the tensor product to yield a map $f: \Z/10 \tensor \Z/12\to \Z/2$ such that $[a]\tensor [b] \mapsto [ab]$.

        Consider the map $g: \Z/2 \to \Z/10 \tensor \Z/12$ given by $[a] \mapsto [a]\tensor [1]$. This is again bilinear, and if $a = a' + 2n$, then $[a] \tensor [1] = [a'+2n]\tensor [1] = [a'] \tensor [1] + [12n-10n]\tensor [1] = [a'] \tensor [1] + [1]\tensor [12n] - [10n]\tensor [1] = [a']$, so this is well defined.

        We moreover have $fg([a]) =  f([a]\tensor [1]) = [a]$ and $gf([a],[b]) = g([ab]) = [ab]\tensor [1] = [a]\tensor [b]$. Hence $f$ is an isomorphism. (Note that this argument works to show in general that $\Z/m \tensor \Z/n \cong \Z/\gcd(m,n))$.
    \end{proof}
\end{exer}

\begin{exer}[1.2.H] Show that $(-)\tensor_A N$ is a covariant functor $\catname{Mod}_A \to \catname{Mod}_A$, and that it is right exact.
    \begin{proof}
    Let $f: M\to M'$ be an $A$-module map. Then $(m,n) \to f(m)\tensor n$ is bilinear, so it yields a map $f_*: M\tensor N\to M'\tensor N$, which on generators is given by $m\tensor n\mapsto f(m)\tensor n$. This respects composition, thus making $(-)\tensor N$ into a functor.

    Let $M\xrightarrow{f} M' \xrightarrow{g} M'' \xrightarrow{h} 0$ be exact. Tensoring, we get a complex 
    \[M \tensor N \xrightarrow{f_*} M'\tensor N\xrightarrow{g_*} M''\tensor N \xrightarrow{h_*} 0,\]
    which we need to check is exact.  We know by the first isomorphism theorem that $g$ induces an isomorphism $ M'/\im(f)\to M''$. 
    \begin{claim}
    Tensor products commute with quotients.
    \begin{proof}
        Let $P, Q, R$ be $A$-modules. Suppose $Q$ is a submodule of $P$. Consider the map $\tilde{f}: (P/Q)\times R\to (P\tensor R)/(Q\tensor R)$ given by $([p], r) \mapsto [p\tensor r]$. If $[p]= [p']$, then $[p\tensor r] - [p'\tensor r] = [p-p'\tensor r] = [q \tensor r] = 0$ so this map is well defined. One can also check bilinearity. Hence it extends to a map $f: (P/Q)\tensor R\to(P\tensor R)/(Q\tensor R)$.

        We now define a map $\tilde{g}: P\times R\to (P/Q)\tensor R$ via $(p,r) \mapsto [p]\tensor r$. This is bilinear, hence yields a map $g': P\tensor R \to  (P/Q)\tensor R$, which further factors through the quotient by $Q\tensor R$, yielding a map $g: (P\tensor R)/(Q\tensor R)\to (P/Q)\tensor R$. And $f,g$ are mutually inverse, yielding the claim.
    \end{proof}
    \end{claim}
    By the claim, $g_*$ induces an isomorphism (since functors send isos to isos)
    \[M''\tensor N \leftarrow (M'/\im(f)) \tensor N \cong (M'\tensor N)/\im(f_*)\] 
    so $\im(f_*) = \ker(g_*)$. And surjectivity of $g_*$ follows directly from surjectivity of $g$. 
    \end{proof}

\end{exer}
\begin{exer}[1.2.I]
The tensor product $(T,t)$ of two modules $M, N$ is unique up to unique isomorphism. (Here $t: M\times N \to T$ is the bilinear map given by the universal property.)
\begin{proof}
    Let $(T', t')$ be another pair satisfying the universal property. Then $t'$ must factor through $T$, i.e. there exists a unique map $f: T\to T'$ such that $f\circ t = t'$. Likewise, there exists a unique map $g: T' \to T$ such that $g\circ t' = t$. Plugging these two formulas into each other we get $f\circ g\circ t' =t'$ and $g\circ f \circ t = t$.

    Now we use the universal property again. Since $t'$ is a bilinear map from $M\times N$ to $T'$, it must factor uniquely through $T'$. One such factoring is as above, $(f\circ g)\circ t' =t'$, but another factoring is $\id_{T'} \circ t'$, so by uniqueness, $f\circ g = \id_{T'}$. Likewise, $g\circ f = \id_{T}$, hence $f, g$ are inverses, and the unique isomorphisms between $T, T'$.
\end{proof}
\end{exer}

\begin{exer}[1.2.J]
Show that the tensor product actually exists, i.e. the construction from $\S 1.2.5$ satisfies the universal property.
\begin{proof}
Recall that $M\tensor N$ is the free $A$-module generated by $M\times N$, quotiented by the following relations:
\begin{enumerate}[(a)]
    \item $ (m_1 + m_2, n) - (m_1, n) - (m_2, n) $
    \item  $(m, n_1+n_2)- (m, n_1)- (m, n_2)$
    \item  $a(m, n)- (am, n) $
    \item $ a(m, n)- (m, an)$
\end{enumerate}
for $a \in A, m, m_1, m_2 \in M, n, n_1, n_2 \in N$. Let $f: M\times N \to P$ be a bilinear $A$-module morphism. It follows by bilinearity that 
\begin{enumerate}[(a)]
    \item $f((m_1 + m_2, n) - (m_1, n) - (m_2, n))  = f(m_1, n)  + f(m_2, n) - f(m_1, n) - f(m_2, n)  =  0$
    \item $f((m, n_1+n_2)- (m, n_1)- (m, n_2)) = f(m,n_1) + f(m,n_2) - f(m,n_1)-f(m,n_2) = 0$
    \item $f(a(m, n)- (am, n)) = af(m,n)-af(m,n) = 0$
    \item $f(a(m, n)- (m, an)) = af(m,n) - af(m,n) = 0$
\end{enumerate}
so $f$ factors uniquely through the quotient.
\end{proof}
\end{exer}

\begin{exer}[1.2.K] ``Important exercise''
\begin{enumerate}[(a)]
    \item If $M$ is an $A$-module and $\phi: A\to B$ is a ring morphism, give $B\tensor_A M$ the structure of a $B$-module. Show that this gives a functor $\catname{Mod}_A\to \catname{Mod}_B$.
    \begin{proof}
        Regard $B$ as an $A$-module via the action $A \times B\to B: (a,b) \mapsto \phi(a)b$. Now $B\tensor_A M$ makes sense as an $A$-module. Now for fixed $b\in B$, consider the map $\tilde{f}_b: B\times M\to B\tensor_A M$ given by $(b', m)\to bb'\tensor m$. We compute
        \[\tilde{f}_b(\phi(a)b', m) = b\phi(a)b'\tensor m = \phi(a)(bb'\tensor m) = a\cdot\tilde{f}_b(b',m)\]
        and 
        \[\tilde{f}_b(b' ,am) = bb'\tensor am = a\cdot (bb'\tensor m) = a\cdot \tilde{f}_b(b',m)\]
        so $\tilde{f}_b$ is $A$-bilinear, and it induces a map $f_b: B\tensor_A M \to B \tensor_A M$, which yields the $B$-module structure on $B\tensor_A M$.

        To see that this is a functor, suppose we have an $A$-module morphism $g: M\to N$. Then we get a map $B\times M \to B\tensor_A N$ given by $(b,m)\mapsto b\tensor g(m)$. This is again $A$-bilinear, so it induces a map $g_*: B\tensor_A M\to B \tensor_A N$, which acts on elementary tensors via $b\tensor m \mapsto b\tensor g(m)$.
    \end{proof}
    \item Following notation above, if $\psi: A\to C$ is a ring morphism, then $B\tensor_A C$ has a ring structure.
    \begin{proof}
        Again, $C$ becomes an $A$-module via the action $(a,c) \mapsto \psi(a)c$. Then $B \tensor_A C$ automatically gets an abelian group structure. To define the ring product, note that specifying a map
        \[(B\tensor C)\times (B\tensor C) \to B\tensor C\]
        is the same thing as specifying a map 
        \[B\tensor C \to \hom_{\catname{Mod}_A}(B\tensor C, B\tensor C)\]
        so we can start here. First define a map 
        \[B\times C \to \hom_{\catname{Mod}_A}(B\times C, B\tensor C):  (b_1,c_1) \mapsto ((b_2,c_2)\mapsto b_1b_2 \tensor c_1c_2).\]
        By properties of the tensor product, the image of this map is an $A$-bilinear map, so we get a map 
        \[B\times C \to \hom_{\catname{Mod}_A}(B\tensor C, B\tensor C): b_1, c_1 \mapsto (b_2\tensor c_2 \mapsto b_1b_2 \tensor c_1c_2).\]
        Again, this is also $A$-bilinear. For example we can check 
        \[\phi(a)b_1 \tensor c_1 \mapsto (b_2\tensor c_2 \mapsto \phi(a)b_1b_2 \tensor c_1c_2 ) = (b_2\tensor c_2 \mapsto \phi(a)(b_1b_2 \tensor c_1c_2)).\]
        Hence we get a map 
        \[B\tensor C \to \hom_{\catname{Mod}_A}(B\tensor C, B\tensor C):  b_1\tensor c_1 \mapsto (b_2\tensor c_2 \mapsto b_1b_2 \tensor c_1c_2)\]
        which is equivalent to the map 
        \[\mu: (B\tensor C)\times (B\tensor C) \to B\tensor C: (b_1\tensor c_1), (b_2\tensor c_2)\mapsto b_1b_2\tensor  c_1c_2\]
        which is $A$-bilinear by definition since it comes from the universal property. Now for $x, y, z \in B\tensor C$, we have by bilinearity
        \[\mu(x+y, z) = \mu(x, z)+ \mu(y,z), \quad \mu(x,y+z) = \mu(x,y)+\mu(x,z)\]
        so this satisfies distributivity. The identity element is $1_B\tensor 1_C$, and $\mu$ is obviously associative, so we are done.
    \end{proof}
\end{enumerate}
\end{exer}

\begin{exer}[1.2.L] If $S$ is a multiplicative subset of $A$ and $M$ is an $A$-module, describe a natural isomorphism $(S^{-1}A)\tensor_A M\to S^{-1}M$ (as both $A$-modules and $S^{-1}A$-modules).
    \begin{proof}
    Consider first the map $S^{-1}A\times M \to S^{-1}M$ given by $(a/s, m)\mapsto  (a\cdot m)/ s$. This is $A$-bilinear since 
    \[(a'\cdot a/s, m) = (a'a/s, m) \mapsto (aa'\cdot m)/s = a\cdot (a'\cdot m)/s\]
    and 
    \[(a/s, a'\cdot m) \mapsto (a\cdot(a'\cdot m))/s = (aa'\cdot m)/s = a\cdot (a'\cdot m)/s.\]
    Hence this induces a map $f: (S^{-1}A)\tensor_A M \to S^{-1}M$ which acts on elementary tensors as 
    \[f(a/s \tensor m) = (a\cdot m)/s.\]

    We can define an inverse map as follows. First consider the map $\tilde{g}:M\to (S^{-1}A)\tensor_A M$ via $m \mapsto 1/1 \tensor m$. Since multiplication by elements of $S$ are invertible in $(S^{-1}A)\tensor_A M$, the map $\tilde{g}$ factors through the localization to yield a map $g: S^{-1}M\to (S^{-1}A)\tensor_A M$ which acts via $m/s \mapsto s^{-1} (1/1\tensor m) = (1/s\tensor m)$. Then we can check 
    \[gf(a/s\tensor m) = g((a\cdot m)/s) = (1/s \tensor a\cdot m) = (a/s \tensor m)\]
    and 
    \[fg(m/s) = f(1/s\tensor m) = m/s.\]
    It remains to check that $f$ is also a $S^{-1}A$-module map. Recall from Exercise 1.2.K.1 that $S^{-1}A \tensor_A M$ has the structure of a $S^{-1}A$-module via the map $A\to S^{-1}A, a\mapsto a/1$. So for $a/s, a'/s' \in S^{-1}A, m \in M$, we have 
    \[f(a/s \cdot (a'/s')\tensor m) = f(aa'/ss' \tensor m) = (aa'\cdot m)/ss' = (a'/s')\cdot (am/s)\]
    as desired. For naturality, we need to check that the following diagram commutes for any map of $A$-modules $\phi: M\to N$:
\[\begin{tikzcd}[cramped]
    % https://q.uiver.app/#q=WzAsNCxbMCwwLCIoU157LTF9QSlcXHRlbnNvcl9BIE0iXSxbMCwxLCIoU157LTF9QSlcXHRlbnNvcl9BIE4iXSxbMSwwLCJTXnstMX1NIl0sWzEsMSwiU157LTF9TiJdLFswLDIsImYiXSxbMCwxLCJcXHBoaV8qIiwyXSxbMSwzLCJmIiwyXSxbMiwzLCJcXHBoaV8qIl1d
	{(S^{-1}A)\tensor_A M} & {S^{-1}M} \\
	{(S^{-1}A)\tensor_A N} & {S^{-1}N}
	\arrow["f", from=1-1, to=1-2]
	\arrow["{\phi_*}"', from=1-1, to=2-1]
	\arrow["{\phi_*}", from=1-2, to=2-2]
	\arrow["f"', from=2-1, to=2-2]
\end{tikzcd}\]
    but this is not too bad, for following the top and right arrows we have 
    \[\phi_*(f(a/s\tensor m)) = \phi_*((a\cdot m)/s) = \phi(a\cdot m)/s\]
    and following the left and bottom ones we have 
    \[f(\phi_*(a/s\tensor m )) = f(a/s \tensor \phi(m)) = (a\cdot \phi(m))/s = \phi(a\cdot m)/s\]
    as desired.
    \end{proof}
\end{exer}

\begin{exer}[1.2.M] Show that tensor products commute with arbitrary direct sums, i.e. for $A$-modules $M$ and $\{N_\alpha\}_{\alpha \in \Lambda}$, define an isomorphism $M \tensor (\oplus_{\alpha \in \Lambda} N_{\alpha}) \to \oplus_{\alpha \in \Lambda}(M\tensor N_{\alpha})$.
    \begin{proof}
    As with every map out of a tensor prouduct, we begin by defining a map 
    \[\tilde{f}: M \times (\oplus_{\alpha \in \Lambda} N_{\alpha}) \to \oplus_{\alpha \in \Lambda}(M\tensor N_{\alpha}), (m, (n_\alpha)_{\alpha \in \Lambda}) \mapsto (m\tensor n_\alpha)_{\alpha \in \Lambda}.\]
    This, being bilinear, induces a map $f: M\tensor (\oplus_{\alpha \in \Lambda} N_{\alpha}) \to \oplus_{\alpha \in \Lambda}(M\tensor N_{\alpha})$ which acts on elementary tensors via $m\tensor (n_\alpha)_{\alpha \in \Lambda}\mapsto (m\tensor n_\alpha)_{\alpha \in \Lambda}$.

    For each $\alpha \in \Lambda$, consider the map 
    \[\tilde{g}_\alpha: M\times N_{\alpha}\to M\tensor (\oplus_{\alpha \in \Lambda} N_\alpha), (m, n) \mapsto m\tensor \iota_\alpha(n)\]
    where $\iota_\alpha: N_\alpha \to \oplus_{\alpha}N_\alpha$ is the inclusion. This is $A$-bilinear, so it induces a map $g_\alpha: M\tensor N_\alpha \to M\tensor (\oplus_{\alpha \in \Lambda} N_{\alpha})$. The sum of all the $g_\alpha$ yields a map $g:= \oplus_{\alpha \in \Lambda}(M\tensor N_\alpha) \to M\tensor (\oplus_{\alpha \in \Lambda} N_\alpha)$.

    And we check 
    \begin{align*}
    fg((m_\alpha \tensor n_\alpha)_{\alpha \in \Lambda}) &= f\sum_{\alpha \in \Lambda} (m_\alpha \tensor \iota_\alpha(n_\alpha)) \\
    &= \sum_{\alpha \in \Lambda}f(m_\alpha\tensor \iota(n_\alpha)) \\
    &= \sum_{\alpha \in \Lambda} (..., 0, m_\alpha\tensor n_\alpha, 0, ...) \\
    &= (m_\alpha \tensor n_\alpha)_{\alpha \in \Lambda}
    \end{align*}
    and 
    \[gf( m \tensor (n_\alpha)_{\alpha\in \Lambda}) = g((m\tensor n_\alpha)_{\alpha \in \Lambda}) = \sum_{\alpha \in \Lambda} m\tensor \iota_\alpha(n_\alpha) = m\tensor \sum_{\alpha \in \Lambda} \iota_\alpha(n_\alpha) = m\tensor (n_\alpha)_{\alpha \in \Lambda}\]
    so $f$ is an isomorphism.
    \end{proof}
\end{exer}

\begin{exer}[1.2.H] Show that in $\catname{Set}$, the fiber product is given by $X\times_Z Y = \{(x,y) \in X\times Y: \alpha(x) = \beta(y)\}$.
    \begin{proof}
        Call the right hand side of above $R$.
        Let $W$ be a set with maps $f_X: W\to X$ and $f_Y: W\to Y$ such that $\alpha\circ f_X = \beta\circ f_Y$. Define the map $\phi: W\to R$ via $\phi(w) = (f_X(w), f_Y(w))$. This actually lands in $R$ since $\alpha\circ \pi_X(\phi(w)) = \alpha \circ f_X(w) = \beta \circ f_Y(w) = \beta \circ \pi_Y(\phi(w))$.  Then clearly $\pi_X \circ \phi = f_X$, and $\pi_Y \circ \phi = f_Y$. Thus $R$ satisfies the universal property so it is \emph{the} fiber product in the category of sets.
    \end{proof}
\end{exer}

\begin{exer}[1.2.O]
If $X$ is a topological space, show that fiber products always exist in the category of open sets of $X$ by describing what a fibered product is.
\begin{proof}
    Remember that the morphisms here are just inclusions of open sets. So suppose we have open sets $U, U'$ mapping into $W$, i.e. $U, U'\subset W$. We claim that the fiber product here is just $U\cap U'$ (intersections of two open sets are open), with the morphisms given by inclusions into $U, U'$ . To see this, given another open set $V$ with morphisms $V\to U$ and $V\to U'$ that agree with $U \to W$ and $U' \to W$, then we know that $V$ must be a subset of both $U$ and $U'$. It follows that $V$ is a subset of $U\cap U'$. And by definition, all the morphisms are inclusions, so everything commutes.
\end{proof}
\end{exer}

\begin{exer}[1.2.P] If $Z$ is the final object in the category $\mathcal{C}$, show that the fiber product $X\times_Z Y$ is given by the product $X\times Y$. (Assume all (fiber) products exist.)
    \begin{proof}
        Let $W \in \mathcal{C}$ with maps $f_X: W\to X$ and $f_Y: W\to Y$ as in the setup of the universal property. Then by the universal property of products, we get a map $\phi: W \to X\times Y$ which factors $f_X$ and $f_Y$. Moreover, since $Z$ is the final object, the compositions $X\times Y \to X \to Z$ and $X\times Y \to Y \to Z$ must agree.
    \end{proof}
\end{exer}

\begin{exer}[1.2.Q] Stacking Cartesian squares gives a Cartesian rectangle:
\[\begin{tikzcd}[cramped]
    % https://q.uiver.app/#q=WzAsNixbMCwwLCJVIl0sWzEsMCwiViJdLFswLDEsIlciXSxbMSwxLCJYIl0sWzAsMiwiWSJdLFsxLDIsIloiXSxbMCwyXSxbMiw0XSxbMiwzXSxbMSwzXSxbMyw1XSxbNCw1XSxbMCwxXV0=
	U & V \\
	W & X \\
	Y & Z
	\arrow[from=1-1, to=1-2]
	\arrow[from=1-1, to=2-1]
	\arrow[from=1-2, to=2-2]
	\arrow[from=2-1, to=2-2]
	\arrow[from=2-1, to=3-1]
	\arrow[from=2-2, to=3-2]
	\arrow[from=3-1, to=3-2]
\end{tikzcd}\]
    \begin{proof}
        Suppose we have maps $f_Y: A\to Y$ and $f_V: A\to V$ such that their postcompositions with $Y\to Z$ and $V\to Z$ agree. Then since the bottom square is Cartesian, there is a unique map $f_{AW}: A\to W$ which factors $f_Y$ and $f_{VX}\circ f_V$, i.e. $f_{WX}\circ f_{AW} = f_{VX}\circ f_V$. Now since the top square is Cartesian, there is a unique map $f_{AW}: A \to U$ factoring $f_{AW}$ (hence $f_Y$) and $f_V$, completing the proof. See below for a figure of all the maps involved:
    \[\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsNyxbMSwxLCJVIl0sWzIsMSwiViJdLFsxLDIsIlciXSxbMiwyLCJYIl0sWzEsMywiWSJdLFsyLDMsIloiXSxbMCwwLCJBIl0sWzAsMl0sWzIsNF0sWzIsMywiZl97V1h9Il0sWzEsMywiZl97Vlh9Il0sWzMsNV0sWzQsNV0sWzAsMV0sWzYsNCwiZl9ZIiwyLHsiY3VydmUiOjJ9XSxbNiwyLCJmX3tBV30iLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbNiwxLCJmX1YiLDAseyJjdXJ2ZSI6LTJ9XSxbNiwwLCJmX3tBVX0iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XV0=
        A && \\
        & U & V \\
        & W & X \\
        & Y & Z
        \arrow["{f_{AU}}", dashed, from=1-1, to=2-2]
        \arrow["{f_V}", curve={height=-12pt}, from=1-1, to=2-3]
        \arrow["{f_{AW}}"', dashed, from=1-1, to=3-2]
        \arrow["{f_Y}"', curve={height=12pt}, from=1-1, to=4-2]
        \arrow[from=2-2, to=2-3]
        \arrow[from=2-2, to=3-2]
        \arrow["{f_{VX}}", from=2-3, to=3-3]
        \arrow["{f_{WX}}", from=3-2, to=3-3]
        \arrow[from=3-2, to=4-2]
        \arrow[from=3-3, to=4-3]
        \arrow[from=4-2, to=4-3]
    \end{tikzcd}\]
    \end{proof}
\end{exer}  

\begin{exer}[1.2.R] Given morphisms $X_1\to Y$, $X_2\to Y$, and $Y\to Z$, there is a natural morphism $X_1\times_Y X_2\to X_1\times_Z X_2$ (assuming both fiber products exist).
    \begin{proof}
       Consider the following diagram:
\[\begin{tikzcd}[cramped]
    % https://q.uiver.app/#q=WzAsNyxbMSwxLCJYXzFcXHRpbWVzX1pYXzIiXSxbMSwzLCJYXzEiXSxbMywxLCJYXzIiXSxbMiwzLCJZIl0sWzMsMiwiWSJdLFszLDMsIloiXSxbMCwwLCJYXzFcXHRpbWVzX1kgWF8yIl0sWzAsMl0sWzMsNV0sWzEsM10sWzQsNV0sWzIsNF0sWzAsMV0sWzYsMSwiIiwxLHsiY3VydmUiOjJ9XSxbNiwyLCIiLDEseyJjdXJ2ZSI6LTJ9XSxbNiwwLCIiLDEseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XV0=
	{X_1\times_Y X_2} &&& \\
	& {X_1\times_ZX_2} && {X_2} \\
	&&& Y \\
	& {X_1} & Y & Z
	\arrow[dashed, from=1-1, to=2-2]
	\arrow[curve={height=-12pt}, from=1-1, to=2-4]
	\arrow[curve={height=12pt}, from=1-1, to=4-2]
	\arrow[from=2-2, to=2-4]
	\arrow[from=2-2, to=4-2]
	\arrow[from=2-4, to=3-4]
	\arrow[from=3-4, to=4-4]
	\arrow[from=4-2, to=4-3]
	\arrow[from=4-3, to=4-4]
\end{tikzcd}\]
    where the outside arrows commute by definition. Hence by the universal property we get the dotted morphism.
    \end{proof}
\end{exer}

\begin{exer}[1.2.S] Show that the diagonal-base-change diagram below is Cartesian:
\[\begin{tikzcd}[cramped]
     % https://q.uiver.app/#q=WzAsNCxbMCwwLCJYXzFcXHRpbWVzX1lYXzIiXSxbMSwwLCJYXzFcXHRpbWVzX1ogWF8yIl0sWzAsMSwiWSJdLFsxLDEsIllcXHRpbWVzX1ogWSJdLFswLDJdLFsyLDNdLFsxLDNdLFswLDFdXQ==
	{X_1\times_YX_2} & {X_1\times_Z X_2} \\
	Y & {Y\times_Z Y}
	\arrow[from=1-1, to=1-2]
	\arrow[from=1-1, to=2-1]
	\arrow[from=1-2, to=2-2]
	\arrow[from=2-1, to=2-2]
\end{tikzcd}\]
\begin{proof}
    The top arrow is defined by the diagram from the previous exercise. The left arrow is either composition $X_1\times_Y X_2\to X_i \to Y$. The right arrow is the dotted arrow below:
\[\begin{tikzcd}[cramped]
     % https://q.uiver.app/#q=WzAsNyxbMSwxLCJZXFx0aW1lc19aIFkiXSxbMiwxLCJZIl0sWzEsMiwiWSJdLFsyLDIsIlkiXSxbMCwwLCJYXzFcXHRpbWVzX1lYXzIiXSxbMCwxLCJYXzEiXSxbMSwwLCJYXzIiXSxbMCwyXSxbMiwzXSxbMCwxXSxbMSwzXSxbNCw1XSxbNCw2XSxbNSwyXSxbNiwxXSxbNCwwLCIiLDEseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XV0=
	{X_1\times_YX_2} & {X_2} & \\
	{X_1} & {Y\times_Z Y} & Y \\
	& Y & Y
	\arrow[from=1-1, to=1-2]
	\arrow[from=1-1, to=2-1]
	\arrow[dashed, from=1-1, to=2-2]
	\arrow[from=1-2, to=2-3]
	\arrow[from=2-1, to=3-2]
	\arrow[from=2-2, to=2-3]
	\arrow[from=2-2, to=3-2]
	\arrow[from=2-3, to=3-3]
	\arrow[from=3-2, to=3-3]
\end{tikzcd}\]
    And the bottom arrow is the diagonal map. Stacking the top and right arrow diagrams in front of each other, padding the middle, we get a diagram as follows:
\[\begin{tikzcd}[cramped]
    % https://q.uiver.app/#q=WzAsMTIsWzEsMSwiWF8xXFx0aW1lc19aIFhfMiJdLFs0LDEsIlhfMiJdLFsyLDIsIlhfMVxcdGltZXNfWiBYXzIiXSxbNSwyLCJYXzIiXSxbMywzLCJZXFx0aW1lc19aIFkiXSxbNiwzLCJZIl0sWzEsNCwiWF8xIl0sWzQsNCwiWiJdLFsyLDUsIlhfMSJdLFszLDYsIlkiXSxbNiw2LCJaIl0sWzAsMCwiWF8xXFx0aW1lc19ZIFhfMiJdLFswLDFdLFswLDZdLFsxLDddLFs2LDddLFsyLDNdLFsyLDhdLFs0LDVdLFs0LDldLFs1LDEwXSxbOSwxMF0sWzAsMiwiXFxpZCIsMCx7ImNvbG91ciI6WzAsNjAsNjBdfSxbMCw2MCw2MCwxXV0sWzEsMywiXFxpZCIsMCx7ImNvbG91ciI6WzI0MCw2MCw2MF19LFsyNDAsNjAsNjAsMV1dLFs2LDgsIlxcaWQiLDAseyJjb2xvdXIiOlsyNDAsNjAsNjBdfSxbMjQwLDYwLDYwLDFdXSxbMiw0LCIiLDAseyJjb2xvdXIiOlswLDYwLDYwXSwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzMsNSwiIiwwLHsiY29sb3VyIjpbMjQwLDYwLDYwXX1dLFs4LDksIiIsMCx7ImNvbG91ciI6WzI0MCw2MCw2MF19XSxbNywxMF0sWzExLDAsIiIsMCx7ImNvbG91ciI6WzAsNjAsNjBdLCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMTEsNiwiIiwwLHsiY3VydmUiOjMsImNvbG91ciI6WzI0MCw2MCw2MF19XSxbMTEsMSwiIiwwLHsiY3VydmUiOi0yLCJjb2xvdXIiOlsyNDAsNjAsNjBdfV1d
	{X_1\times_Y X_2} &&&&&& \\
	& {X_1\times_Z X_2} &&& {X_2} \\
	&& {X_1\times_Z X_2} &&& {X_2} \\
	&&& {Y\times_Z Y} &&& Y \\
	& {X_1} &&& Z \\
	&& {X_1} \\
	&&& Y &&& Z
	\arrow[color={rgb,255:red,214;green,92;blue,92}, dashed, from=1-1, to=2-2]
	\arrow[color={rgb,255:red,92;green,92;blue,214}, curve={height=-12pt}, from=1-1, to=2-5]
	\arrow[color={rgb,255:red,92;green,92;blue,214}, curve={height=18pt}, from=1-1, to=5-2]
	\arrow[from=2-2, to=2-5]
	\arrow["\id", color={rgb,255:red,214;green,92;blue,92}, from=2-2, to=3-3]
	\arrow[from=2-2, to=5-2]
	\arrow["\id", color={rgb,255:red,92;green,92;blue,214}, from=2-5, to=3-6]
	\arrow[from=2-5, to=5-5]
	\arrow[from=3-3, to=3-6]
	\arrow[color={rgb,255:red,214;green,92;blue,92}, dashed, from=3-3, to=4-4]
	\arrow[from=3-3, to=6-3]
	\arrow[color={rgb,255:red,92;green,92;blue,214}, from=3-6, to=4-7]
	\arrow[from=4-4, to=4-7]
	\arrow[from=4-4, to=7-4]
	\arrow[from=4-7, to=7-7]
	\arrow[from=5-2, to=5-5]
	\arrow["\id", color={rgb,255:red,92;green,92;blue,214}, from=5-2, to=6-3]
	\arrow[from=5-5, to=7-7]
	\arrow[color={rgb,255:red,92;green,92;blue,214}, from=6-3, to=7-4]
	\arrow[from=7-4, to=7-7]
\end{tikzcd}\]
    So the composition of the red arrows is the unique map coming from the universal property applied to the front square and composition of the blue arrows. On the other hand, if we stack the left and bottom arrow diagrams on top of each other, padding the middle, we get 
\[\begin{tikzcd}[cramped]
     % https://q.uiver.app/#q=WzAsMTQsWzEsMSwiWVxcdGltZXMgX1pZIl0sWzQsMSwiWSJdLFsyLDIsIlkiXSxbNSwyLCJZIl0sWzMsMywiWVxcdGltZXNfWiBZIl0sWzYsMywiWSJdLFsxLDQsIlkiXSxbNCw0LCJaIl0sWzIsNSwiWSJdLFszLDYsIlkiXSxbMCwwLCJYXzFcXHRpbWVzX1kgWF8yIl0sWzYsNiwiWiJdLFswLDIsIlhfMSJdLFsyLDAsIlhfMiJdLFswLDFdLFswLDZdLFsxLDddLFs2LDddLFsyLDNdLFsyLDhdLFs0LDVdLFs0LDldLFswLDIsIiIsMCx7ImNvbG91ciI6WzAsNjAsNjBdfV0sWzEsMywiXFxpZCIsMCx7ImNvbG91ciI6WzI0MCw2MCw2MF19LFsyNDAsNjAsNjAsMV1dLFs2LDgsIlxcaWQiLDAseyJjb2xvdXIiOlsyNDAsNjAsNjBdfSxbMjQwLDYwLDYwLDFdXSxbMiw0LCIiLDAseyJjb2xvdXIiOlswLDYwLDYwXSwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzMsNSwiXFxpZCIsMCx7ImNvbG91ciI6WzI0MCw2MCw2MF19XSxbOCw5LCJcXGlkIiwwLHsiY29sb3VyIjpbMjQwLDYwLDYwXX1dLFsxMCwwLCIiLDAseyJjb2xvdXIiOlswLDYwLDYwXSwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzUsMTFdLFs5LDExXSxbNywxMV0sWzEwLDEyLCIiLDIseyJjdXJ2ZSI6MSwiY29sb3VyIjpbMjQwLDYwLDYwXX1dLFsxMiw2LCIiLDIseyJjdXJ2ZSI6MSwiY29sb3VyIjpbMjQwLDYwLDYwXX1dLFsxMCwxMywiIiwwLHsiY3VydmUiOi0xLCJjb2xvdXIiOlsyNDAsNjAsNjBdfV0sWzEzLDEsIiIsMCx7ImN1cnZlIjotMSwiY29sb3VyIjpbMjQwLDYwLDYwXX1dXQ==
	{X_1\times_Y X_2} && {X_2} &&&& \\
	& {Y\times _ZY} &&& Y \\
	{X_1} && Y &&& Y \\
	&&& {Y\times_Z Y} &&& Y \\
	& Y &&& Z \\
	&& Y \\
	&&& Y &&& Z
	\arrow[color={rgb,255:red,92;green,92;blue,214}, curve={height=-6pt}, from=1-1, to=1-3]
	\arrow[draw={rgb,255:red,214;green,92;blue,92}, dashed, from=1-1, to=2-2]
	\arrow[color={rgb,255:red,92;green,92;blue,214}, curve={height=6pt}, from=1-1, to=3-1]
	\arrow[color={rgb,255:red,92;green,92;blue,214}, curve={height=-6pt}, from=1-3, to=2-5]
	\arrow[from=2-2, to=2-5]
	\arrow[color={rgb,255:red,214;green,92;blue,92}, from=2-2, to=3-3]
	\arrow[from=2-2, to=5-2]
	\arrow[color={rgb,255:red,92;green,92;blue,214}, from=2-5, to=3-6]
	\arrow[from=2-5, to=5-5]
	\arrow[color={rgb,255:red,92;green,92;blue,214}, curve={height=6pt}, from=3-1, to=5-2]
	\arrow[from=3-3, to=3-6]
	\arrow[draw={rgb,255:red,214;green,92;blue,92}, dashed, from=3-3, to=4-4]
	\arrow[from=3-3, to=6-3]
	\arrow[draw={rgb,255:red,92;green,92;blue,214}, from=3-6, to=4-7]
	\arrow[from=4-4, to=4-7]
	\arrow[from=4-4, to=7-4]
	\arrow[from=4-7, to=7-7]
	\arrow[from=5-2, to=5-5]
	\arrow[color={rgb,255:red,92;green,92;blue,214}, from=5-2, to=6-3]
	\arrow[from=5-5, to=7-7]
	\arrow[draw={rgb,255:red,92;green,92;blue,214}, from=6-3, to=7-4]
	\arrow[from=7-4, to=7-7]
\end{tikzcd}\]
    But now the blue arrows on the outside are the same, so by the universal property, the composition of the red arrows in both diagrams must agree, so the square in the exercise commutes.

    Now let $A$ be an object with morphisms to $Y$ and $X_1\times_Z X_2$ such that their postcompositions with the according maps are equal, i.e. the following diagram commutes:  
\[\begin{tikzcd}[cramped]
	A && \\
	& {X_1\times_YX_2} & {X_1\times_ZX_2} \\
	& Y & {Y\times_Z Y}
	\arrow[curve={height=-18pt}, from=1-1, to=2-3]
	\arrow[curve={height=18pt}, from=1-1, to=3-2]
	\arrow[from=2-2, to=2-3]
	\arrow[from=2-2, to=3-2]
	\arrow[from=2-3, to=3-3]
	\arrow[from=3-2, to=3-3]
     % https://q.uiver.app/#q=WzAsNSxbMSwxLCJYXzFcXHRpbWVzX1lYXzIiXSxbMiwxLCJYXzFcXHRpbWVzX1pYXzIiXSxbMSwyLCJZIl0sWzIsMiwiWVxcdGltZXNfWiBZIl0sWzAsMCwiQSJdLFsyLDNdLFswLDJdLFswLDFdLFsxLDNdLFs0LDIsIiIsMix7ImN1cnZlIjozfV0sWzQsMSwiIiwyLHsiY3VydmUiOi0zfV1d
\end{tikzcd}\]
    
    There being a morphism $A \to X_1\times_Z X_2$ implies that we have morphisms $f_i: A\to X_i$ for $i=1,2$, whose postcompositions with $X_i\to Y\to Z$ are equal. The right arrow above is induced by maps $X_1\times_Z X_2\to X_i \to Y$, which both have to agree with $A\to Y$, that is they are equal. Hence the compositions $A\to X_i\to Y$ induce a map $A \to X_1\times_Y X_2$, completing the proof.
\end{proof}
\end{exer}

\begin{exer}[1.2.T] Show that the coproduct in the category of sets is disjoint union.
    \begin{proof}
    Let $X, Y$ be sets and let us take the disjoint union to be 
    \[X\coprod Y:= \{(x,0): x \in X\}\cup \{(y,1): y \in Y\}.\]
    Define the inclusions $\iota_X: X\to X\coprod Y$ via $x \mapsto (x,0)$ and $\iota_Y: Y\to X\coprod Y$ via $y\mapsto (y,1)$.
    Let $A$ be a set with maps $f_X: X\to A$, $f_Y:Y\to A$. Then we can define a map $f: X\coprod Y \to A$ via $(x,0)\mapsto f_X(x)$ and $(y,1)\mapsto f_Y(y)$, which makes everything commute. For uniqueness, if $g: X\coprod Y\to A$ is another map making things commute, we have 
    \[g(x,0) = g(\iota_X(x)) = f_X(x) = f(x,0)\]
    and likewise for $Y$.
    \end{proof}
\end{exer}

\begin{exer}[1.2.U] For ring morphisms $A\to B$, $A\to C$, show that there is a natural morphism $B\to B\tensor_A C$ given by $b\mapsto b\tensor 1$ and likewise $C\to B\tensor_A C$ given by $c\mapsto 1\tensor c$. Show that these maps make the following a cocartesian diagram in the category of rings.
\[\begin{tikzcd}[cramped]
    % https://q.uiver.app/#q=WzAsNCxbMCwwLCJBIl0sWzEsMCwiQiJdLFswLDEsIkMiXSxbMSwxLCJCXFx0ZW5zb3JfQSBDIl0sWzAsMiwiZl9DIiwyXSxbMCwxLCJmX0IiXSxbMSwzXSxbMiwzXV0=
	A & B \\
	C & {B\tensor_A C}
	\arrow["{f_B}", from=1-1, to=1-2]
	\arrow["{f_C}"', from=1-1, to=2-1]
	\arrow[from=1-2, to=2-2]
	\arrow[from=2-1, to=2-2]
\end{tikzcd}\]
\begin{proof}
    To see that $b\to b\tensor 1$ is a ring map, we have $b+b' \mapsto (b+b')\tensor 1 = b\tensor 1 + b'\tensor 1$, and $bb' \mapsto bb' \tensor 1 =( b\tensor 1 )(b'\tensor 1)$, and $1\mapsto 1\tensor 1$. Likewise for $C\to B\tensor_A C$. The square commutes since $f_B(a)\tensor 1 = f_B(a)\cdot 1 \tensor 1 = 1\tensor f_C(a) \cdot 1 = 1\tensor f_C(a)$.

    Let $D$ be another ring with maps $g_B: B\to D$ and $g_C: C\to D$ such that $g_Bf_b = g_Cf_C$. Define a map 
    $B\tensor_A C\to D$ beginning with $B\times C\to D, (b, c)\mapsto g_B(b)g_C(c)$. By virtue of $g_B$ being a ring morphism, we have 
    \[(f_B(a)b, c)\mapsto g_B(f_B(a)b)g_C(c) = g_B(f_B(a))g_B(b)g_C(c)\]
    and likewise in the second argument, so this map is $A$-bilinear. Consequently we have a map $\phi: B\tensor_A C\to D$ acting on basis elements via $b\tensor c\mapsto g_B(b)g_C(c)$. Then $g_B(b) = g_B(b)1 = g_B(b)g_C(1) =\phi(b\tensor 1)$, and likewise $g_C(c) = \phi(1\tensor c)$, so we are done.
\end{proof}
\end{exer}

\begin{exer}[1.2.V]
Show that the composition of two monomorphisms is a monomorphism.
\begin{proof}
Let $X\xrightarrow{f} Y\xrightarrow{g} Z$ be monomorphisms. Suppose $\pi_1, \pi_2: W\to X$ satisfy $(g\circ f) \circ \pi_1 = (g\circ f)\circ \pi_2$. Then by associativity of composition, we have $g \circ (f\circ \pi_1) = g\circ(f\circ \pi_2)$, and because $g$ is a mono, $f\circ \pi_1 = f\circ \pi_2$, and because $f$ is a mono, $\pi_1 = \pi_2$.
\end{proof}
\end{exer}

\begin{exer}[1.2.W]
Show that a morphism $\pi: X\to Y$ is a monomorphism if and only if the fiber product $X\times_Y X$ exists and the induced diagonal map $\delta_\pi: X\to X\times_Y X$ is an isomorphism.
\begin{proof}
Forward direction. We claim that the fiber product is given by any object $X'$ with a chosen isomorphism $\psi: X' \to X$ serving as both projection maps. This exists, for example, by taking $X'=X$ and $\psi = \id$. To see this is the fiber product, it is clear that the square commutes. Given any maps $f_1, f_2: W\to X$ such that $\pi\circ f_1 = \pi \circ f_2$, we know that $f_1 = f_2$ since $\pi$ is a monomorphism. Then defining $W\to X$ by $\psi^{-1} \circ f_1$ makes things commute. If $(X'', \psi'')$ is another fiber product, then $\psi''^{-1}\circ \psi$ gives the unique isomorphism, so $(X', \psi)$ satisfies the universal property. Finally, the diagonal map must satisfy $\psi \circ \delta_\pi = \id$, so it is an isomorphism since $\psi$ is an isomorphism.

Backward direction. By assumption, $\delta_\pi$ is an isomorphism, and it satisfies the identity $\mathrm{pr}_X \circ \delta_\pi = \id$, so both projection maps $\mathrm{pr}_X$ are inverse to $\delta_\pi$, so both projection maps are the same. Then given maps $f_1, f_2: W\to X$ such that $\pi \circ f_1 = \pi \circ f_2$, by the the universal property of fiber products we get a unique map $\phi: W\to X\times_Y X$ such that $f_1 = \delta_\pi^{-1}\circ \phi = f_2$.
\end{proof}
\end{exer}

\begin{exer}[1.2.X]
    Given morphisms $X_1 \to Y$, $X_2\to Y$, and a monomorphism $Y\to Z$, show that $X_1\times_Y X_2 \to X_1\times_Z X_2$ is an isomorphism.
    \begin{proof}
    By the previous exercise, $g$ in the diagonal-base-change diagram below is an isomorphism
    \[\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsNCxbMCwwLCJYXzFcXHRpbWVzX1kgWF8yIl0sWzEsMCwiWF8xXFx0aW1lc19aWF8yIl0sWzAsMSwiWSJdLFsxLDEsIllcXHRpbWVzX1pZIl0sWzAsMiwiaCIsMl0sWzAsMSwiZiJdLFsxLDMsImoiXSxbMiwzLCJnIiwyXV0=
        {X_1\times_Y X_2} & {X_1\times_ZX_2} \\
        Y & {Y\times_ZY}
        \arrow["f", from=1-1, to=1-2]
        \arrow["h"', from=1-1, to=2-1]
        \arrow["j", from=1-2, to=2-2]
        \arrow["g"', from=2-1, to=2-2]
    \end{tikzcd}\]
    We can proceed by showing the more general fact that in an arbitrary Cartesian square
    \[\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsNCxbMCwwLCJBIl0sWzEsMCwiQiJdLFswLDEsIkMiXSxbMSwxLCJEIl0sWzAsMSwiZiJdLFsyLDMsImciXSxbMCwyLCJoIiwyXSxbMSwzLCJqIl1d
        A & B \\
        C & D
        \arrow["f", from=1-1, to=1-2]
        \arrow["h"', from=1-1, to=2-1]
        \arrow["j", from=1-2, to=2-2]
        \arrow["g", from=2-1, to=2-2]
    \end{tikzcd}\]
    that if $g$ is an isomorphism then so is $f$. The trick is to first consider the square 
    \[\begin{tikzcd}[cramped]
         % https://q.uiver.app/#q=WzAsNCxbMCwwLCJCIl0sWzEsMCwiQiJdLFswLDEsIkMiXSxbMSwxLCJEIl0sWzAsMSwiXFxpZCJdLFsyLDMsImciXSxbMCwyLCJnXnstMX1cXGNpcmMgaiIsMl0sWzEsMywiaiJdXQ==
	B & B \\
	C & D
	\arrow["\id", from=1-1, to=1-2]
	\arrow["{g^{-1}\circ j}"', from=1-1, to=2-1]
	\arrow["j", from=1-2, to=2-2]
	\arrow["g", from=2-1, to=2-2]
    \end{tikzcd}\]
    which we claim is Cartesian. It obviously commutes. Given maps $\phi_B: X\to B$ and $\phi_C: X\to C$ such that $j\circ \phi_B = g\circ \phi_C$, the map we want $X\to B$ is just given by $\phi_B$, since $\phi_B = \id\circ \phi_B$, and $g^{-1}\circ j \circ \phi_B = g^{-1}\circ g \circ \phi_C = \phi_C$. So $B$ is another fiber product, and by the universal property there is an isomorphism $u: A\to B$ making the following diagram commute
    \[
\begin{tikzcd}[cramped]
    % https://q.uiver.app/#q=WzAsNSxbMSwxLCJCIl0sWzIsMSwiQiJdLFsxLDIsIkMiXSxbMiwyLCJEIl0sWzAsMCwiQSJdLFs0LDAsInUiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbNCwyLCJoIiwyLHsiY3VydmUiOjJ9XSxbMCwyLCJnXnstMX1cXGNpcmMgaiIsMl0sWzIsMywiZyIsMl0sWzAsMSwiXFxpZCIsMl0sWzEsMywiaCJdLFs0LDEsImYiLDAseyJjdXJ2ZSI6LTJ9XV0=
	A && \\
	& B & B \\
	& C & D
	\arrow["u"', dashed, from=1-1, to=2-2]
	\arrow["f", curve={height=-12pt}, from=1-1, to=2-3]
	\arrow["h"', curve={height=12pt}, from=1-1, to=3-2]
	\arrow["\id"', from=2-2, to=2-3]
	\arrow["{g^{-1}\circ j}"', from=2-2, to=3-2]
	\arrow["h", from=2-3, to=3-3]
	\arrow["g"', from=3-2, to=3-3]
\end{tikzcd}\]
    Because $f$ also makes the diagram commute, $u=f$ and we are done.
    \end{proof}
\end{exer}

\begin{exer}[1.2.Y] Yoneda lemma.
    \begin{enumerate}[(a)]
        \item Let $A, A'$ be objects in a category $\mathcal{C}$. Suppose there exist a collection of maps $i_C: \Hom(C,A)\to \Hom(C,A')$ for $C\in \mathcal{C}$ that commute with the maps $\Hom(Z,X)\to \Hom(Y,X)$ induced by morphisms $Y\to Z$. (i.e. a natural transformation between the functors $\Hom(-,A)$ and $\Hom(-,A')$). Show that the collection of maps $\{i_C\}$ are induced by a unique morphism $g: A\to A'$, i.e. each $i_C$ is of the form $u\mapsto g\circ u$.
        \begin{proof}
            Consider plugging in $C= A$. Then we have a map $i_A: \Hom(A,A)\to \Hom(A,A')$. We know that $\id_A \in \Hom(A,A)$, and we claim that $g = i_A(\id_A)$. Now suppose we have a morphism $\phi: C\to A$. By the naturality/commutativity assumption, this gives rise to a commutative diagram 

            \[\begin{tikzcd}[cramped]
                % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbShBLEEpIl0sWzEsMCwiXFxIb20oQSxBJykiXSxbMCwxLCJcXEhvbShDLEEpIl0sWzEsMSwiXFxIb20oQyxBJykiXSxbMCwyLCItXFxjaXJjXFxwaGkiLDJdLFsyLDMsImlfQyIsMl0sWzEsMywiLVxcY2lyY1xccGhpIl0sWzAsMSwiaV9BIl1d
                {\Hom(A,A)} & {\Hom(A,A')} \\
                {\Hom(C,A)} & {\Hom(C,A')}
                \arrow["{i_A}", from=1-1, to=1-2]
                \arrow["{-\circ\phi}"', from=1-1, to=2-1]
                \arrow["{-\circ\phi}", from=1-2, to=2-2]
                \arrow["{i_C}"', from=2-1, to=2-2]
            \end{tikzcd}\]

            Tracing through the element $\id_A$, the top-right path ends up at $i_A(\id_A)\circ \phi = g\circ \phi$, while the bottom-left path ends up at $i_C(\id_A\circ \phi) = i_C(\phi)$. It follows that $i_C(\phi) = g\circ \phi$, so we are done.
        \end{proof}
        \item If furthermore the $i_C$ are all bijections, show that $g$ is an isomorphism. (So if we have a natural isomorphism of the functors $\Hom(-,A)$ and $\Hom(-,A')$ then we also get an isomorphism $A\to A'$.)
        \begin{proof}
           Since $i_{A'}$ is an isomorphism, there is some $f \in \Hom(A',A)$ such that $i_{A'}(f) = \id_{A'}$. Now consider the same commutative diagram as above with $C=A'$. Let the vertical arrows be precomposition by $f$. Then commutativity yields $g\circ f = i_A(\id_A)\circ f = \id_{A'}$. 
 
           On the other hand, flip this commutative diagram diagonally and swap the direction of the horizontal arrows to get 
        \[\begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbShBJyxBJykiXSxbMSwwLCJcXEhvbShBJyxBKSJdLFswLDEsIlxcSG9tKEEsQScpIl0sWzEsMSwiXFxIb20oQSxBKSJdLFswLDEsImlfe0EnfV57LTF9Il0sWzEsMywiLVxcY2lyYyBnIiwyXSxbMCwyLCItXFxjaXJjIGciLDJdLFsyLDMsImlfe0F9XnstMX0iXV0=
            {\Hom(A',A')} & {\Hom(A',A)} \\
            {\Hom(A,A')} & {\Hom(A,A)}
            \arrow["{i_{A'}^{-1}}", from=1-1, to=1-2]
            \arrow["{-\circ g}"', from=1-1, to=2-1]
            \arrow["{-\circ g}"', from=1-2, to=2-2]
            \arrow["{i_{A}^{-1}}", from=2-1, to=2-2]
        \end{tikzcd}\]
        which yields $f\circ g$ following the top and right paths and $\id_A$ following the bottom left. So $g$ is an isomorphism.
        \end{proof}
    \end{enumerate}
\end{exer}

\begin{exer}[1.2.Z] Yoneda lemma again.
    \begin{enumerate}[(a)]
        \item Let $A,B$ be objects in a category $\mathcal{C}$. Give a bijection between $\Hom(\Hom(A,-), \Hom(B,-))$ and $\Hom(B,A)$.
        \begin{soln}
            (This is Exercise 1.2.Z.c, take $F = \Hom(B,-)$.)
            For the exact same proof, read on. Given a natural transformation $\alpha \in \Hom(\Hom(A,-), \Hom(B,-))$, define $\Phi(\alpha) = \alpha_A(\id_A) \in \Hom(B,A)$. Conversely, given $g \in \Hom(B,A)$, define a natural transformation by $\Psi(g)_C(f) = f\circ g$. This is indeed natural since given any morphism $\varphi: C\to C'$, the square 
            \[\begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbShBLEMpIl0sWzEsMCwiXFxIb20oQixDKSJdLFswLDEsIlxcSG9tKEEsQycpIl0sWzEsMSwiXFxIb20oQixDJykiXSxbMCwyLCJcXHZhcnBoaVxcY2lyYyAtIiwyXSxbMSwzLCJcXHZhcnBoaVxcY2lyYyAtIiwyXSxbMCwxLCItXFxjaXJjIGciXSxbMiwzLCItXFxjaXJjIGciLDJdXQ==
            {\Hom(A,C)} & {\Hom(B,C)} \\
            {\Hom(A,C')} & {\Hom(B,C')}
            \arrow["{-\circ g}", from=1-1, to=1-2]
            \arrow["{\varphi\circ -}"', from=1-1, to=2-1]
            \arrow["{\varphi\circ -}"', from=1-2, to=2-2]
            \arrow["{-\circ g}"', from=2-1, to=2-2]
            \end{tikzcd}\]
            commutes by associativity of morphism composition. 
            
            Now we need to check that $\Phi$ and $\Psi$ are inverses. In one direction, given a natural transformation $\alpha$, $C \in \mathcal{C}$, and $f\in \Hom(A,C)$, we have 
            \[(\Psi \circ \Phi(\alpha))_C(f) = (\Psi(\alpha_A(\id_A)))_C(f) = f\circ \alpha_A(\id_A).\]
            By naturality of $\alpha$, the square
            \[\begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbShBLEEpIl0sWzEsMCwiXFxIb20oQixBKSJdLFswLDEsIlxcSG9tKEEsQykiXSxbMSwxLCJcXEhvbShCLEMpIl0sWzAsMiwiZlxcY2lyYyAtIiwyXSxbMiwzLCJcXGFscGhhX0MiLDJdLFsxLDMsImZcXGNpcmMgLSJdLFswLDEsIlxcYWxwaGFfQSJdXQ==
            {\Hom(A,A)} & {\Hom(B,A)} \\
            {\Hom(A,C)} & {\Hom(B,C)}
            \arrow["{\alpha_A}", from=1-1, to=1-2]
            \arrow["{f\circ -}"', from=1-1, to=2-1]
            \arrow["{f\circ -}", from=1-2, to=2-2]
            \arrow["{\alpha_C}"', from=2-1, to=2-2]
            \end{tikzcd}\]
            yields the equality $f\circ \alpha_A(\id_A) = \alpha_C(f)$, which shows $\Psi\circ\Phi$ is the identity. 

            In the other direction, let $g \in \Hom(B,A)$. We compute 
            \[\Phi(\Psi(g)) = \Psi(g)_A(\id_A) = \id_A\circ g=g\]
            which completes the proof.
        \end{soln}
        \item State and prove the dual statement for $\Hom(\Hom(-,A), \Hom(-,B))$ and $\Hom(A,B)$.
        \begin{proof}
            Let $\Phi: \Hom(\Hom(-,A), \Hom(-,B)) \to \Hom(A,B)$ be the map $\alpha \mapsto \alpha_A(\id_{A})$ from Exercise 1.2.Y.a. Conversely given $g \in \Hom(A,B)$ define a natural transformation $\Psi(g)$ with $\Psi(g)_C(f) = g\circ f$ where $f \in \Hom(C,A)$. Then, given a natural transformation $\alpha$, $C\in\mathcal{C}$, and $f \in \Hom(C,A$), we have
            \[\Psi(\Phi(\alpha))_C(f) =\Psi(\alpha_A(\id_A))_C(f) = \alpha_A(\id_A)\circ f.\]
            Again, by naturality we get a commutative diagram
            \[\begin{tikzcd}[cramped]
                % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbShBLEEpIl0sWzEsMCwiXFxIb20oQSxCKSJdLFswLDEsIlxcSG9tKEMsQSkiXSxbMSwxLCJcXEhvbShDLEIpIl0sWzAsMiwiLVxcY2lyYyBmIiwyXSxbMiwzLCJcXGFscGhhX0MiLDJdLFsxLDMsIi1cXGNpcmMgZiJdLFswLDEsIlxcYWxwaGFfQSJdXQ==
                {\Hom(A,A)} & {\Hom(A,B)} \\
                {\Hom(C,A)} & {\Hom(C,B)}
                \arrow["{\alpha_A}", from=1-1, to=1-2]
                \arrow["{-\circ f}"', from=1-1, to=2-1]
                \arrow["{-\circ f}", from=1-2, to=2-2]
                \arrow["{\alpha_C}"', from=2-1, to=2-2]
            \end{tikzcd}\]
            which yields the equality $\alpha_A(\id_A)\circ f = \alpha_C(f)$, so $\Psi(\Phi(\alpha)) = \alpha$. In the other direction, for $g \in \Hom(A,B)$, we have 
            \[\Phi(\Psi(g)) = (\Psi(g))_A(\id_A) = g\circ \id_A = g\]
            which completes the proof!!!!!!
        \end{proof}
        \item Let $F: \mathcal{C} \to \catname{Set}$ be a covariant functor. Give a bijection between $\Hom(\Hom(A, -), F)$ and $FA$.
        \begin{soln}
            We do the exact same thing as before. In one direction, given a natural transformation $\alpha: \Hom(A,-)\nat F$, define $\Phi(\alpha)$ to be $\alpha_A(\id_A)$. In the other direction, given $X \in FA$, $C \in \mathcal{C}$ and $f \in \Hom(A,C)$, define $\Psi(X)_C(f)  = (Ff)(X)$.

            We check, again, that given a natural transformation $\alpha: \Hom(A,-)\nat F$, $C \in \mathcal{C}$ and $f \in \Hom(A,C)$, that 
            \[\Psi(\Phi(\alpha))_C(f) = \Psi(\alpha_A(\id_A))_C(f) =  (Ff)(\alpha_A(\id(A)))\]
            which by naturality is equal to $\alpha_C(f)$. And on the other hand, given an element $X \in FA$, we have 
            \[\Phi(\Psi(X)) = \Psi(X)_A(\id_A) = (F\id_A)(X) = \id_{FA}(X) = X\]
            which completes the proof.
        \end{soln}
    \end{enumerate}

\end{exer}

\subsection{Limits and colimits}
\begin{exer}[1.3.A] Show that if $\mathcal{I}$ has an initial object $e$, then the limit of any diagram $F: \mathcal{I}\to \mathcal{C}$ exists.
    \begin{proof}
    We claim that the limit is just given by $Fe$, with the structure maps $f_j: Fe \to Fj$ given by the image of the unique morphism $e \to j$ under $F$, say $g_j$. Then for a morphism $m: j\to k$ in $\mathcal{I}$, since $e$ is initial, we know that $m\circ g_j = g_k$, whence it follows that $Fm\circ f_j = Fm\circ Fg_j = F(m\circ Fg_j) = Fg_k = f_k$. 
    
    To see that $Fe$ is final with respect to this property, for any $W\in\mathcal{C}$ with maps $w_j: W\to A_j$ commuting with the relevant things, we immediately have a morphism $w_e: W\to Fe$, and by assumption $w_j = f_j\circ w_e$.
    \end{proof}
\end{exer}

\begin{exer}[1.3.B] Solve 1.2.S by identifying both $X_1\times_Y X_2$ and $Y\times_{(Y\times_Z Y)} (X_1\times_Z X_2)$ as the limit of the diagram 
\begin{equation}\begin{tikzcd}[cramped]
    % https://q.uiver.app/#q=WzAsNCxbMCwwLCJYXzEiXSxbMCwyLCJYXzIiXSxbMSwxLCJZIl0sWzIsMSwiWiJdLFswLDJdLFsyLDNdLFsxLDJdXQ==
	{X_1} && \\
	& Y & Z \\
	{X_2}
	\arrow[from=1-1, to=2-2]
	\arrow[from=2-2, to=2-3]
	\arrow[from=3-1, to=2-2]
\end{tikzcd}\end{equation}
    \begin{proof}
        First to see how this implies the result of 1.2.S, note that the long fiber product $Y\times_{(Y\times_Z Y)} (X_1\times_Z X_2)$ is the limit of the diagram 
        \begin{equation}\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsMyxbMSwwLCJYXzFcXHRpbWVzX1ogWF8yIl0sWzEsMSwiWVxcdGltZXNfWiBZIl0sWzAsMSwiWSJdLFswLDFdLFsyLDFdXQ==
        & {X_1\times_Z X_2} \\
        Y & {Y\times_Z Y}
        \arrow[from=1-2, to=2-2]
        \arrow[from=2-1, to=2-2]
    \end{tikzcd}\end{equation}
        so if we show that $X_1\times_Y X_2$ and this limit coincide, then the square 
    \[\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsNCxbMSwwLCJYXzFcXHRpbWVzX1ogWF8yIl0sWzEsMSwiWVxcdGltZXNfWiBZIl0sWzAsMSwiWSJdLFswLDAsIlhfMVxcdGltZXNfWSBYXzIiXSxbMCwxXSxbMiwxXSxbMywyXSxbMywwXV0=
        {X_1\times_Y X_2} & {X_1\times_Z X_2} \\
        Y & {Y\times_Z Y}
        \arrow[from=1-1, to=1-2]
        \arrow[from=1-1, to=2-1]
        \arrow[from=1-2, to=2-2]
        \arrow[from=2-1, to=2-2]
    \end{tikzcd}\]
    must be Cartesian. Now onto the proof. It is clear that $X_1\times_YX_2$ is the limit of diagram (1.1): the structure maps to $X_i$ are given by the projections from the fiber product, and the structure maps to $Y$ and $Z$ are given by postcomposing with the provided maps $X_i\to Y$, $Y\to Z$. And by the universal property of fiber products, $X_1\times_YX_2$ is final w.r.t. this. 
    
    Now we show that $K:= Y\times_{(Y\times_Z Y)} (X_1\times_Z X_2)$ is also the limit of (1.1). Since it is a fiber product, it comes with a map to $X_1\times_Z X_2$, which is the data of maps $f_i: K \to X_i$ commuting with $X_i\to Z$, as well as a map $f_y: K \to Y$. The map $f_z: K\to Z$ is given by postcomposing with $Y\to Z$. By defintion of all these fiber products, $f_i, f_y, f_z$ must commute with each other. To see $K$ is final w.r.t. this property, suppose we have a maps $g_i$ from $W$ to $X_i, Y, Z$ which commute with the diagram (1.1). Taking the maps to $X_i$ and $Z$, we obtain a map $W\to X_1\times_Z X_2$ by the universal property of the fiber product. On the other hand, we are already given a map $W\to Y$. These fit into the following diagram:
    \[\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsOSxbMSwxLCJYXzFcXHRpbWVzX1ogWF8yIl0sWzIsMSwiWF8xIl0sWzMsMSwiWSJdLFsxLDMsIlkiXSxbMSwyLCJYXzEiXSxbNCw0LCJaIl0sWzIsMiwiWSJdLFszLDMsIllcXHRpbWVzX1pZIl0sWzAsMCwiVyJdLFsxLDJdLFswLDQsIiIsMCx7ImNvbG91ciI6WzI0MCw2MCw2MF19XSxbNCwzXSxbMyw1XSxbMiw1XSxbNiwzXSxbNiwyXSxbNiw3LCIiLDAseyJjb2xvdXIiOlsyNDAsNjAsNjBdLCJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbOCw2LCIiLDAseyJjdXJ2ZSI6LTR9XSxbOCwzLCIiLDAseyJjdXJ2ZSI6Mn1dLFs4LDIsIiIsMCx7ImN1cnZlIjotMn1dLFs3LDNdLFs3LDJdLFs4LDAsIiIsMCx7ImNvbG91ciI6WzI0MCw2MCw2MF0sInN0eWxlIjp7ImJvZHkiOnsibmFtZSI6ImRhc2hlZCJ9fX1dLFs0LDYsIiIsMCx7ImNvbG91ciI6WzI0MCw2MCw2MF19XSxbMCwxLCIiLDIseyJjb2xvdXIiOlsyNDAsNjAsNjBdfV0sWzEsNiwiIiwwLHsiY29sb3VyIjpbMjQwLDYwLDYwXX1dXQ==
        W &&&& \\
        & {X_1\times_Z X_2} & {X_2} & Y \\
        & {X_1} & Y \\
        & Y && {Y\times_ZY} \\
        &&&& Z
        \arrow[color={rgb,255:red,92;green,92;blue,214}, dashed, from=1-1, to=2-2]
        \arrow[curve={height=-12pt}, from=1-1, to=2-4]
        \arrow[curve={height=-24pt}, from=1-1, to=3-3]
        \arrow[curve={height=12pt}, from=1-1, to=4-2]
        \arrow[color={rgb,255:red,92;green,92;blue,214}, from=2-2, to=2-3]
        \arrow[color={rgb,255:red,92;green,92;blue,214}, from=2-2, to=3-2]
        \arrow[from=2-3, to=2-4]
        \arrow[color={rgb,255:red,92;green,92;blue,214}, from=2-3, to=3-3]
        \arrow[from=2-4, to=5-5]
        \arrow[color={rgb,255:red,92;green,92;blue,214}, from=3-2, to=3-3]
        \arrow[from=3-2, to=4-2]
        \arrow[from=3-3, to=2-4]
        \arrow[from=3-3, to=4-2]
        \arrow[color={rgb,255:red,92;green,92;blue,214}, dashed, from=3-3, to=4-4]
        \arrow[from=4-2, to=5-5]
        \arrow[from=4-4, to=2-4]
        \arrow[from=4-4, to=4-2]
    \end{tikzcd}\]
    Where the arrows in blue yield an arrow from $W$ to $K$.
    \end{proof}
\end{exer}

\begin{exer}[1.3.C] In the category of sets, the limit of a diagram $F: \mathcal{I} \to A$ is given by 
    \[L:= \{(a_i)_{i \in \mathcal{I}} \in \prod_{i\in I}A_i: F(m)(a_j) = a_k \text{ for all $m \in \Hom(j,k)$}\}\]
    with the standard projection maps $\pi_i: L \to A_i$.
    \begin{proof}
        By definition of $L$, given $a= (a_i)_{i\in \mathcal{I}} \in L$ and $m: j\to k$, we have by definition of $L$ that $Fm(\pi_j(a)) = Fm(a_j) = a_k = \pi_k(a)$. Hence things commute. To show that $L$ is final, suppose we have a family of functions $g_i: W\to A_i$ commuting with things. Then we can define $g: W\to L$ given by $w \mapsto (g_i(w))_{i \in \mathcal{I}}$. Then $\pi_j(g(w)) = g_j(w)$ for $j \in \mathcal{I}$, completing the proof.
    \end{proof}
\end{exer}

\begin{exer}[1.3.D] Colimits.
    \begin{enumerate}[(a)]
        \item Interpret the statement $\Q = \colim (\frac{1}{n}\Z)$.
        \begin{soln}
            Consider the category of natural numbers $\N$ with morphisms given by divisibility, i.e. there is a morphism $a\to b$ if $a$ divides $b$. Consider the functor $F$ from $\N$ to abelian groups given by $n\mapsto \frac{1}{n}\Z$. Then if there is an arrow $n\to m$, i.e. $nk=m$ for some $k$, we define a homomorphism $\phi_{nm}: \frac{1}{n}\Z\to\frac{1}{m}\Z$ via $x/n\mapsto xk/m$. Thus $F$ is actually a functor, and we claim that $\Q$ is the colimit of this diagram.

            To see this, note that we have maps $\iota_n: \frac{1}{n}\Z \to \Q$ given by inclusion. These commute with the morphisms in $\N$, again with $n,m,k$ as above we have $\iota_n(x/n) = x/n = xk/nk = xk/m =\iota_m(\phi_{nm}(x/n))$. Given another group $K$ with morphisms $g_n: \frac{1}{n}\Z \to K$ for all $n$ commuting with the divisibility maps, we can define a map $\phi: \Q\to K$ via $q=a/b \mapsto g_b(q)$. 
            
            This is well defined, since if $a/b = a'/b'$, then the following diagram commutes
            \[
            \begin{tikzcd}[cramped]
                % https://q.uiver.app/#q=WzAsNSxbMCwwLCJcXGZyYWN7MX17Yn1cXFoiXSxbMCwxXSxbMCwyLCJcXGZyYWN7MX17Yid9XFxaIl0sWzEsMSwiXFxmcmFjezF9e2JiJ31cXFoiXSxbMywxLCJLIl0sWzAsMywiYS9iIFxcbWFwc3RvIGFiJy9iYiciXSxbMiwzLCJhJy9iJ1xcbWFwc3RvIGEnYi9iYiciLDJdLFszLDQsImdfe2JiJ30iLDJdLFswLDQsImdfYiIsMCx7ImN1cnZlIjotMn1dLFsyLDQsImdfe2InfSIsMix7ImN1cnZlIjoyfV1d
                {\frac{1}{b}\Z} &&& \\
                {} & {\frac{1}{bb'}\Z} && K \\
                {\frac{1}{b'}\Z}
                \arrow["{a/b \mapsto ab'/bb'}", from=1-1, to=2-2]
                \arrow["{g_b}", curve={height=-12pt}, from=1-1, to=2-4]
                \arrow["{g_{bb'}}"', from=2-2, to=2-4]
                \arrow["{a'/b'\mapsto a'b/bb'}"', from=3-1, to=2-2]
                \arrow["{g_{b'}}"', curve={height=12pt}, from=3-1, to=2-4]
            \end{tikzcd}\]
            implying that $\phi(a/b) = g_b(a/b) = g_{b'}(a'/b') = \phi(a'/b')$. And $\phi$ trivially commutes with the $\iota_n$ since we have $\phi(\iota_b(a/b)) = \phi(a/b) = g_b(a/b)$ by definition.
        \end{soln}
        \item Interpret the union of subsets of a given set as a colimit.
        \begin{soln}
            Let $A$ be a set and consider the category of subsets $2^A$ of $A$, with a morphism $X\to Y$ if $X\subset Y$. Let $\{A_i\}_{i \in I}$ be the collection of subsets we want to take the union of, interpreted as a subcategory of the category of subsets of $A$. Then we get a diagram from this subcategory to $2^A$ via inclusion, and we claim that $\cup A_i$ is the colimit of this diagram. The commutativity is obvious, if $A_j\subset A_k$, then $A_j \subset A_k \subset \cup A_i$ gives the same thing as $A_j \subset \cup A_i$. 
            If we have another subset of $A$, say $K$ with maps from each $A_i$ commuting with inclusion, this means that $\cup A_i$ is a subset of $K$, automatically giving us the desired extension. Again all the morphisms commute since they are just inclusions.
        \end{soln}
    \end{enumerate}
\end{exer}

\begin{exer}[1.3.E] Let $\mathcal{I}$ be a filtered index category. Prove that any colimit $F: \mathcal{I} \to \catname{Set}$ exists, and is given by
    \[K:= \big\{(a_i, i) \in \coprod_{i \in \mathcal{I}} A_i\big\} \big/\sim\]
where the equivalence relation is 
\[\text{
            $(a_i, i)\sim (a_j, j)$ iff there are $f: A_i \to A_k$  and $g: A_j \to A_k$ in the diagram such that $f(a_i) = g(a_j)$.
        }\]
        and inclusions $\iota_i: A_i\to K$ are just the standard $a \mapsto (a, i)$.
        \begin{proof}
        First we need to show that $\sim$ is an equivalence relation. For reflexivity, we have an identity morhpism $A_i \to A_i$, so because $\mathcal{I}$ is filtered we have a set $A_j$ with a morphism $A_i\to A_j$, so $(a_i, i)\sim (a_i, i)$. Symmetry is obvious. For transitivity, suppose $(a_i, i) \sim (a_j, j)$, witnessed by some $A_{ij}$, and $(a_j, j) \sim (a_k, k)$, witnessed by some $A_{jk}$, as in the solid arrows in the diagram below:
        \[\begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsOCxbMSwwLCJBX2oiXSxbMCwxLCJBX2kiXSxbMSwxLCJBX3tpan0iXSxbMywwLCJBX2oiXSxbMywxLCJBX3tqa30iXSxbNCwxLCJBX2siXSxbMiwyLCJBX2wiXSxbMiwzLCJBX2wnIl0sWzAsMl0sWzEsMl0sWzMsNF0sWzUsNF0sWzIsNiwiIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzQsNiwiIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzYsNywiIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
            & {A_j} && {A_j} & \\
            {A_i} & {A_{ij}} && {A_{jk}} & {A_k} \\
            && {A_l} \\
            && {A_l'}
            \arrow[from=1-2, to=2-2]
            \arrow[from=1-4, to=2-4]
            \arrow[from=2-1, to=2-2]
            \arrow[dashed, from=2-2, to=3-3]
            \arrow[dashed, from=2-4, to=3-3]
            \arrow[from=2-5, to=2-4]
            \arrow[squiggly, from=3-3, to=4-3]
        \end{tikzcd}\]
        Then the dotted arrows and zigzag arrows come from the fact that $\mathcal{I}$ is filtered, so the compositions $A_i \to A_l'$ and $A_k\to A_l'$ show that $(a_i, i) \sim (a_k, k)$. Hence $\sim$ is an equivalence relation.

        Now we check that that $\iota_i$ commute with the morphisms in the diagram. Suppose $m: j\to k$ is a morphism in $\mathcal{I}$. We need to show that $(a, j) = \iota_j(a) = \iota_k \circ Fm(a) = (Fm(a), k)$ for all $a \in A_j$, which by the equivalence relation amounts to finding some $l \in \mathcal{I}$ and maps $f: A_j\to A_l$ and $g: A_k\to A_l$ such that $f(a) = g(Fm(a))$. Since $\mathcal{I}$ is filtered, there exists some $l'$ with maps $\phi_j: A_j \to A_{l'}$ and $\phi_k: A_k \to A_{l'}$. Now $\phi_{l'}$ and $\phi_k\circ Fm$ are two maps $A_j \to A_{l'}$, so again by filteredness there is some $A_l$ and a map $\phi: A_{l'}\to A_l$ such that $\phi \circ \phi_{l'} = \phi \circ \phi_k\circ Fm$. Then taking $f=\phi\circ \phi_{l'}$ and $g= \phi\circ \phi_k$ works. 

        Finally for the universal property. Given another set $L$ with maps $\psi_i: A_i \to L$ commuting with the diagram, define $h: K\to L$ via $(a_i, i) \mapsto \psi_i(a_i)$. This commutes with the $\iota_i$ trivially, so we just need to check it is well-defined. Suppose $(a_i, i)\sim (a_j,j)$. Then there is some $k$ with maps $f: A_i \to A_k$ and $g: A_j\to A_k$ such that $f(a_i) = g(a_j)$. Since the $\psi_i$ commute with these maps, we get $\psi_i = \psi_k(f(a_i)) = \psi_k(g(a_j)) = \psi_j(a_j)$, completing the proof.
        \end{proof}
\end{exer}

\begin{exer}[1.3.F]
    Let $\mathcal{I}$ be a filtered index category, $F: \mathcal{I}\to \catname{Mod}_A$ a diagram. Define the set $K$ as in the previous exercise with the $M_i$. Addition in $K$ is defined as follows. Given $(m_i, i)$ and $(m_j, j)$, choose $l \in \mathcal{I}$ with arrows $u: i\to l$ and $v: j\to l$, and define $(m_i, i) + (m_j, j)$ to be $(Fu(m_i)+Fv(m_j), l)$. Show that $K$ is the colimit of $F$.
    \begin{proof}
        Let us show that $K$ is an $A$-module, upon which the previous exercise shows it is the colimit. To see that addition is well-defined, we need to show it is independent of a few choices:
        \begin{enumerate}
            \item Choice of representative for addition. Suppose $(m_i, i)\sim (m_{i'}, i')$ via maps $\alpha: i\to k$ and $\alpha': i' \to k$. Choose some $l'$ with $u': i' \to l'$ and $v': j\to l'$. Since $\mathcal{I}$ is filtered, there is some $m \in \mathcal{I}$ receiving maps from $l, l',k$, say $\phi_{lm}, \phi_{l'm}, \phi_{km}$. 
            Now we can (co)equalize $F\phi_{lm}\circ Fv$ and $F\phi_{l'}m \circ Fv'$ via $F\alpha_1$. Then equalize $F(\alpha_1\circ F\phi_{lm}\circ u)$ and $F(\alpha_1\circ \phi_{km}\circ \alpha)$ via $F\alpha_2$. Finally, equalize $F(\alpha_2\circ\alpha_1\circ\phi_{km}\circ\alpha')$ and $F(\alpha_2\circ\alpha_1\circ\phi_{l'm}\circ u')$ via $\alpha_3$. Then the image of $Fu(m_i)+Fv(m_j)$ under $F(\alpha_3\circ\alpha_2\circ\alpha_1\circ \phi_{lm})$ is equal to the the image of $F\phi_{lm}(Fv(m_j)) + F(\phi_{km}(alpha))(m_i)$ under $F(\alpha_3\circ\alpha_2\circ\alpha_1)$, which is equal to the image of $F\phi_{l'm}(Fv'(m_j)) + F(\phi_{km}(alpha'))(m_i')$, which is equal to the image of $Fu'(m_i')+Fv'(m_j)$ under $F(\alpha_3\circ\alpha_2\circ\alpha_1\circ \phi_{l'm})$. This shows that $(Fu'(m_i')+Fv'(m_j), l) \sim (Fu(m_i)+Fv(m_j), l)$. This can be pictured using the diagram below, but beware because the two squares at the top do not necessarily commute:
            \[\begin{tikzcd}[cramped]
                % https://q.uiver.app/#q=WzAsMTQsWzAsMCwiTV9qIl0sWzIsMCwiTV9pIl0sWzQsMCwiTV97aSd9Il0sWzYsMCwiTV9qIl0sWzEsMSwiTV9sIl0sWzUsMSwiTV97bCd9Il0sWzMsMSwiTV9rIl0sWzMsMiwiTV9tIl0sWzMsMywiTV97bSd9ICJdLFszLDQsIk1fe20nJ30iXSxbMyw1LCJNX3ttJycnfSJdLFs0LDMsIlxcdGV4dHtlcXVhbGl6ZSB9IE1falxccmlnaHRyaWdodGFycm93cyBNX20iXSxbNCw0LCJcXHRleHR7ZXF1YWxpemUgfU1faVxccmlnaHRyaWdodGFycm93cyBNX3ttJ30iXSxbNCw1LCJcXHRleHR7ZXF1YWxpemUgfSBNX3tpJ31cXHJpZ2h0cmlnaHRhcnJvd3MgTV97bScnfSAiXSxbMCw0LCJGdiJdLFsxLDQsIkZ1IiwyXSxbMSw2LCJGXFxhbHBoYSJdLFsyLDYsIkZcXGFscGhhJyIsMl0sWzIsNSwiRnUnIl0sWzMsNSwiRnYnIiwyXSxbNCw3LCJGXFxwaGlfe2xtfSIsMl0sWzYsNywiRlxccGhpX3trbX0iLDJdLFs1LDcsIkZcXHBoaV97bCdtfSJdLFs3LDgsIkZcXGFscGhhXzEiLDJdLFs4LDksIkZcXGFscGhhXzIiLDJdLFs5LDEwLCJGXFxhbHBoYV8zIiwyXV0=
                {M_j} && {M_i} && {M_{i'}} && {M_j} \\
                & {M_l} && {M_k} && {M_{l'}} \\
                &&& {M_m} \\
                &&& {M_{m'} } & {\text{equalize } M_j\rightrightarrows M_m} \\
                &&& {M_{m''}} & {\text{equalize }M_i\rightrightarrows M_{m'}} \\
                &&& {M_{m'''}} & {\text{equalize } M_{i'}\rightrightarrows M_{m''} }
                \arrow["Fv", from=1-1, to=2-2]
                \arrow["Fu"', from=1-3, to=2-2]
                \arrow["{F\alpha}", from=1-3, to=2-4]
                \arrow["{F\alpha'}"', from=1-5, to=2-4]
                \arrow["{Fu'}", from=1-5, to=2-6]
                \arrow["{Fv'}"', from=1-7, to=2-6]
                \arrow["{F\phi_{lm}}"', from=2-2, to=3-4]
                \arrow["{F\phi_{km}}"', from=2-4, to=3-4]
                \arrow["{F\phi_{l'm}}", from=2-6, to=3-4]
                \arrow["{F\alpha_1}"', from=3-4, to=4-4]
                \arrow["{F\alpha_2}"', from=4-4, to=5-4]
                \arrow["{F\alpha_3}"', from=5-4, to=6-4]
            \end{tikzcd}\]

            \item Choice of $l$. Suppose we take some other $l' \in \mathcal{I}$ with arrows $u': i\to l'$ and $v': j\to l'$. Then there is some $m$ with arrows $w: l \to m$ and $w': l' \to m$. Equalize $w\circ u$ and $w'\circ u'$ via $\alpha_1: m\to m'$, then equalize $\alpha_1\circ m\circ v$ and $\alpha_1\circ m'\circ v'$ via $\alpha_2: m'\to m''$. Then $F(\alpha_2\circ \alpha_1 \circ w\circ u)(m_i) + F(\alpha_2\circ\alpha_1\circ w\circ v)(m_j)= F(\alpha_2\circ\alpha_1\circ w' \circ u')(m_{i}) +F(\alpha_2\circ\alpha_1\circ w'\circ v)(m_j)$, so the maps $F(\alpha_2\circ\alpha_1\circ w)$ and $F(\alpha_2\circ\alpha_1\circ w')$ give the equivalence between $Fu(m_i)+Fv(m_j)$ and $Fu'(m_i)+Fv'(m_j)$.
            
            \item Choice of $u$ and $v$. Suppose we have another morphism $u': i\to l$. We can equalize them via some map $\alpha: l\to k$. Then it follows that $F\alpha(Fu(m_i) + Fv(m_j)) = F\alpha(Fu'(m_i) + Fv(m_j))$.
        \end{enumerate} 
        Finally we check well-definedness of scalar multiplication. Let $a \in A$ and $(m_i, i) \in K$. Define $a\cdot (m_i, i) := (a\cdot m_i, i)$. To see this is well-defined, take some other $(m_j, j) \sim (m_i, i)$, with morphisms $u,v$ as above. Then $Fu(a\cdot m_i)  = a\cdot Fu(m_i) = a\cdot Fv(m_j) = Fv(a\cdot m_j)$ by virtue of $Fu$ being a morphism of $A$-modules, so scalar multiplication is well-defined.
    \end{proof}
\end{exer}



\begin{exer}[1.3.G]
    Suppose $S$ is a multiplicative subset of $A$. Interpret the statement $S^{-1}A = \colim \frac{1}{s}A$.
    \begin{soln}
    This is like 1.3.D.a. Regard $S$ as a category whose objects are $S$, with a morphism $s\to s'$ if there exists $t \in S$ such that $ts = s'$. Then our diagram will be the functor $s \mapsto \frac{1}{s}A$, which sends a morphism $s\to s'$ to the morphism $\phi_{ss'}: a/s \mapsto at /s'$. We claim that $S^{-1}A$ is the colimit of this.  

    The maps $\iota_s: \frac{1}{s}A\to S^{-1}A$ are given by inclusion. These commute with the morphisms with $S$ since $\iota_s(a/s) = a/s =at/s' = \iota_{s'}(\phi_{ss'}(a/s))$. Given another $A$-module $K$ with morphisms $g_s: \frac{1}{s}A\to K$, we define a map $\phi: S^{-1}A\to K$ by $a/s \mapsto g_s(a/s)$. This is well defined by the same logic as 1.3.D.a and commutes with the $\iota_s$ since $\phi(\iota_s(a/s)) = g_s(a/s)$.
    \end{soln}
\end{exer}  

\begin{exer}[1.3.H] Let $F: \mathcal{I}\to \catname{Mod}_A$ be a diagram (write $M_i$ for $Fi$). Show that the colimit of $F$ is given by $K:= \oplus_{i \in \mathcal{I}} M_i$ modulo the relations $m_i - F(n)(m_i)$ for each arrow $n: i\to j$ in $\mathcal{I}$.
    \begin{proof}
    The inclusions $\iota_i: M_i\to K$ send $m_i$ to the element in the direct sum which is $m_i$ in index $i$ and zero everywhere else. Then they commute with the diagram by definition of $K$. Given a family of maps $g_i: M_i\to L$ for some other $A$-module $L$, commuting with the diagram, we can define a map $\phi: K\to L$ via $(m_i)_{i\in \mathcal{I}} \mapsto \sum_{i\in\mathcal{I}} g_i(m_i)$. This is well-defined since $\phi(\iota_i(m_i)) = g_i(m_i) = g_j(Fn(m_i)) = \phi(\iota_j(Fn(m_i)))$, and the same thing shows that it commutes with the families of maps $\iota_i$ and $g_i$.
    \end{proof}
\end{exer}

\subsection{Adjoints}
\begin{exer}[1.4.A] Write down the naturality square in the second argument for an adjoint pair $F: \mathcal{A}\rightleftarrows \mathcal{B}: G$ with natural transformation $\tau_{AB}: \Hom_{\mathcal{B}}(FA, B) \to \Hom_{\mathcal{A}}(A,GB)$.
    \begin{soln}
        For each $g: B\to B'$ in $\mathcal{B}$, we require that 
        \begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbV97XFxtYXRoY2Fse0F9fShGQSxCKSJdLFswLDEsIlxcSG9tX1xcbWF0aGNhbHtCfShBLEdCKSJdLFsxLDAsIlxcSG9tX1xcbWF0aGNhbHtBfShGQSwgQicpIl0sWzEsMSwiXFxIb21fXFxtYXRoY2Fse0J9KEEsR0InKSJdLFswLDEsIlxcdGF1X3tBQn0iLDJdLFswLDIsImdfKiJdLFsxLDMsIkdnXyoiLDJdLFsyLDMsIlxcdGF1X3tBQid9Il1d
            {\Hom_{\mathcal{A}}(FA,B)} & {\Hom_\mathcal{A}(FA, B')} \\
            {\Hom_\mathcal{B}(A,GB)} & {\Hom_\mathcal{B}(A,GB')}
            \arrow["{g_*}", from=1-1, to=1-2]
            \arrow["{\tau_{AB}}"', from=1-1, to=2-1]
            \arrow["{\tau_{AB'}}", from=1-2, to=2-2]
            \arrow["{Gg_*}"', from=2-1, to=2-2]
        \end{tikzcd}
        commutes. Here $g_*$ is postcomposition by $g$, and $Gg_*$ is postcomposition by $Gg$.
    \end{soln}
\end{exer}  

\begin{exer}[1.4.B] Show that for an adjoint pair as above, the following properties are satisfied. 
    \begin{enumerate}
        \item For each $A$ there is a map $\eta: A\to GFA$ (called the unit) such that for any $g: FA\to B$, the corresponding $\tau_{AB}g: A\to GB$ is given by the composition $A\xrightarrow{\eta} GFA\xrightarrow{Gg} GB$.
        \begin{proof}
            Let $H$ be the functor $\Hom_\mathcal{A}(A, G(-)): \mathcal{B} \to \catname{Set}$. By the Yoneda lemma, natural transformations 
            \[\tau_{A, -}: \Hom_{\mathcal{B}}(FA, -) \nat H\]
            are in bijection with elements of $H(FA) = \Hom_\mathcal{A}(A, GFA)$. Call this bijection $\Psi$. We claim that $\Psi(\tau_{A,-})$ is the desired $\eta$. To see this, we know that under the inverse of this bijection, $\Psi(\tau_{A,-})$ maps to the function
            \[\Hom_\mathcal{B}(FA, B) \to HB, \quad g \mapsto H(g)(\Psi(\tau_{A,B})) = Gg\circ \Psi(\tau_{A,B})\]
            but because $\Psi$ is a bijection this function must coincide with $\tau_{A,B}$, so $\tau_{A,B} = Gg\circ \Psi(\tau_{A,B})$.
        \end{proof}
        \item For each $B$ there is a map $\epsilon: FG(B)\to B$ (called the counit) so that for each $f: A\to GB$, the corresponding $\tau^{-1}_{AB}(f): FA\to B$ is given by the composition $F(A) \xrightarrow{f} FGB \xrightarrow{\epsilon} B$.
        \begin{proof}
            Let $H$ be the functor $\Hom_{\mathcal{B}}(F(-),B): \mathcal{A}\to\catname{Set}$. By the contravariant Yoneda lemma, natural transformations 
            \[\tau^{-1}_{-,B}: \Hom_{\mathcal{A}}(-, GB) \to H\]
            are in bijection with elements of $H(GB) = \Hom_\mathcal{B}(FGB, B)$, call this bijection $\Psi$. Then $\Psi:\tau^{-1}_{AB}$ is the desired $\epsilon$. To see this, under the inverse of $\Psi$ we know that $\Psi(\tau^{-1}_{-,B})$ maps to the function
            \[\Hom(A,GB)\to \Hom(FA, B), f \mapsto Hf(\Psi(\tau^{-1}_{A,B})) = \Psi(\tau^{-1}_{A,B})\circ Ff\] 
            so $\tau^{-1}_{-,B}(f) = \Psi(\tau^{-1}_{A,B}) \circ Ff$.
        \end{proof}
    \end{enumerate}
\end{exer}

\begin{exer}[1.4.C]
Let $M, N, P$ be $A$-modules. Describe a bijection between $\Hom(M\tensor_A N, P)$ and $\Hom(M, \Hom_A(N, P))$.
\begin{soln}
    Let us start with $\Phi_{M,P}: \Hom(M\tensor_A N, P) \to\Hom(M, \Hom_A(N, P))$. By the universal property of tensor products, the data of $f \in \Hom(M\tensor N, P)$ is equivalent to the data of a bilinear map $\tilde{f}: M\times N \to P$ satisfying $f(m\tensor n) = \tilde{f}(m, n)$. So define $\Phi_{M, P}(f)$ via $\Phi_{M,P}(f)(m) = \tilde{f}(m, -)$.
    
    In the other direction, define $\Psi_{M,P}: \Hom(M, \Hom_A(N, P))\to \Hom(M\tensor_A N, P)$ as follows. Given $g$ in the domain, $g(m)$ is an $A$-linear map $N\to P$, so $g(-)(-): M\times N\to P$ is bilinear. Hence it induces a map $M\tensor N\to P$ which we call $\Psi_{M,P}(g)$, satisfying $\Psi_{M,P}(g)(m\tensor n) = g(m)(n)$. 

    To see these are mutually inverse, we check that 
    \[\Psi_{M,P}(\Phi_{M,P}(f))(m\tensor n) = \Phi_{M,P}(f)(m)(n) = \tilde{f}(m,n) = f(m\tensor n).\]
    \[\Phi_{M,P}(\Psi_{M,P}(g))(m)(n) = \widetilde{\Psi_{M,P}}(g)(m, n) = \Psi_{M,P}(g)(m\tensor n) = g(m)(n)\]
    which completes the bijection.
\end{soln}
\end{exer}

\begin{exer}[1.4.D] Show that $(-)\tensor N$ and $\Hom(N, -)$ are adjoint.
    \begin{proof}
    Let us stick to the notation above. We need to show that $\Phi$ is natural in $M$ and $P$. So let $\pi: M \to M'$ and $\tau: P \to P'$ be morphisms. In the first argument, we have the diagram
    \[\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbShNJ1xcdGVuc29yIE4sIFApIl0sWzEsMCwiXFxIb20oTScsIFxcSG9tKE4sUCkpIl0sWzEsMSwiXFxIb20oTSwgXFxIb20oTixQKSkiXSxbMCwxLCJcXEhvbShNXFx0ZW5zb3IgTiwgUCkiXSxbMCwzLCJcXGNpcmNcXHBpIiwyXSxbMSwyLCJcXGNpcmNcXHBpIl0sWzAsMSwiXFxQaGlfe00nLFB9Il0sWzMsMiwiXFxQaGlfe00sUH0iLDJdXQ==
        {\Hom(M'\tensor N, P)} & {\Hom(M', \Hom(N,P))} \\
        {\Hom(M\tensor N, P)} & {\Hom(M, \Hom(N,P))}
        \arrow["{\Phi_{M',P}}", from=1-1, to=1-2]
        \arrow["{\pi^*}"', from=1-1, to=2-1]
        \arrow["{\circ\pi}", from=1-2, to=2-2]
        \arrow["{\Phi_{M,P}}"', from=2-1, to=2-2]
    \end{tikzcd}\]
    We verify for $f$ in the upper left corner that
    \[\Phi_{M',P}(f)(\pi(m))(n) = \tilde{f}(\pi(m), n) = f(\pi(m)\tensor n)\]
    and
    \[\Phi_{M, P}(f \circ \pi_*)(m)(n) = \widetilde{f\circ \pi^*}(n, m) = f(\pi^*(n\tensor m)) = f(\pi(n)\tensor m).\]
    For the other diagram: 
    \[    
    \begin{tikzcd}[cramped]
         % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbShNXFx0ZW5zb3IgTiwgUCkiXSxbMSwxLCJcXEhvbShNLCBcXEhvbShOLFAnKSkiXSxbMCwxLCJcXEhvbShNXFx0ZW5zb3IgTiwgUCcpIl0sWzEsMCwiXFxIb20oTSwgXFxIb20oTiwgUCkpIl0sWzAsMiwiXFx0YXVcXGNpcmMgLSIsMl0sWzIsMSwiXFxQaGlfe00sUCd9Il0sWzAsMywiXFxQaGlfe00sUH0iXSxbMywxLCJcXHRhdV8qIiwyXV0=
        {\Hom(M\tensor N, P)} & {\Hom(M, \Hom(N, P))} \\
        {\Hom(M\tensor N, P')} & {\Hom(M, \Hom(N,P'))}
        \arrow["{\Phi_{M,P}}", from=1-1, to=1-2]
        \arrow["{\tau\circ -}"', from=1-1, to=2-1]
        \arrow["{\tau_*}"', from=1-2, to=2-2]
        \arrow["{\Phi_{M,P'}}", from=2-1, to=2-2]
    \end{tikzcd}\]
    Take $g$ in the upper left corner, and verify: 
    \[\tau_*(\Phi_{M,P}(g))(m)(n) = \tau\circ \Phi_{M,P}(g)(m)(n) = \tau(g(m\tensor m))\]
    and 
    \[\Phi_{M, P'}(\tau\circ g)(m)(n) = \tau(g(m\tensor m))\]
    which completes the proof.
    \end{proof}
\end{exer}

\begin{exer}[1.4.E] Let $\phi: B\to A$ be a morphism of rings. For an $A$-module $M$, we can regard it as a $B$-module $M_B$ via this morphism, which yields a functor $(-)_B: \catname{Mod}_A\to \catname{Mod}_B$. Show that this functor is right adjoint to $(-)\tensor_B A$.
    \begin{proof}
        Let us describe the bijection $\Phi: \Hom(N\tensor_BA, M) \to \Hom(N, M_B)$. Start with $f$ on the left. Define $\Psi(f)(n) := f(n\tensor 1_A)$. This is a valid $B$-module morphism, since $\Psi(f)(b\cdot n) = f(b\cdot n\tensor 1_A) = f(n\tensor \phi(b)) = \phi(b)\cdot f(n\tensor 1) = b\cdot f(n\tensor 1)$.

        On the other hand, given $g$ on the right, first consider the map $\tilde{\Psi}(g): N\times A \to M$ given by $(n,a)\mapsto a\cdot g(n)$. This is $B$-bilinear since $\Psi(g)(b\cdot n, a) = a\cdot g(b\cdot n) = a \cdot \phi(b) \cdot g(n) = \phi(b)\cdot (a\cdot g(n)) = \phi(b)\cdot \Psi(g)(n,a)$, and in the second variable $\Psi(g)(n, \phi(b)a) = \phi(b)a \cdot g(n) = \phi(b)\cdot (a\cdot g(n))$. Hence $\tilde{\Psi}(g)$ factors through the tensor product to yield a map $\Psi(g): N\tensor A \to M$ with $\Psi(g)(n\tensor a) = \tilde{\Psi(g)}(n,a) =a\cdot g(n)$.

        These are mutually inverse since 
        \[\Phi(\Psi(g))(n) = \Psi(g)(n\tensor 1) = 1\cdot g(n) =g(n)\]
        and 
        \[\Psi(\Phi(f))(n\tensor a) = a\cdot \Phi(f)(n) = a\cdot f(n\tensor 1) = f(n\tensor a).\]

        For naturality, let $\pi: N\to N'$ and $\tau: M\to M'$ be morphisms. The first square to check is   
        \[\begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNSxbMCwxLCJcXEhvbV9BKE5cXHRlbnNvcl9CQSwgTSkiXSxbMSwxLCJcXEhvbV9CKE4sTV9CKSJdLFswLDJdLFswLDAsIlxcSG9tX0EoTidcXHRlbnNvciBBLCBNKSJdLFsxLDAsIlxcSG9tX0IoTicsTV9CKSJdLFszLDAsIlxccGleKiIsMl0sWzQsMSwiXFxjaXJjIFxccGkiLDJdLFszLDQsIlxcUGhpX3tOJyxNfSJdLFswLDEsIlxcUGhpX3tOLE19IiwyXV0=
            {\Hom_A(N'\tensor A, M)} & {\Hom_B(N',M_B)} \\
            {\Hom_A(N\tensor_BA, M)} & {\Hom_B(N,M_B)} \\
            {}
            \arrow["{\Phi_{N',M}}", from=1-1, to=1-2]
            \arrow["{\pi^*}"', from=1-1, to=2-1]
            \arrow["{\circ \pi}"', from=1-2, to=2-2]
            \arrow["{\Phi_{N,M}}"', from=2-1, to=2-2]
        \end{tikzcd}\]
        Choose $f$ in the top left, then we get 
        \[\Phi_{N',M}(f)(\pi(n)) = f(\pi(n)\tensor 1)\]
        \[\Phi_{N,M}(\pi^*(f))(n) = \pi^*f(n \tensor 1) = f(\pi(n)\tensor 1).\]
        The other square is 
        \[\begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbV9BKE5cXHRlbnNvciBBLCBNKSJdLFswLDEsIlxcSG9tX0EoTlxcdGVuc29yIEEsIE0pIl0sWzEsMCwiXFxIb20oTixNX0IpIl0sWzEsMSwiXFxIb20oTixNJ19CKSJdLFswLDEsIlxcdGF1IFxcY2lyYyIsMl0sWzAsMiwiXFxQaGlfe04sTX0iXSxbMSwzLCJcXFBoaV97TixNJ30iLDJdLFsyLDMsIlxcdGF1XFxjaXJjIl1d
            {\Hom_A(N\tensor A, M)} & {\Hom(N,M_B)} \\
            {\Hom_A(N\tensor A', M)} & {\Hom(N,M'_B)}
            \arrow["{\Phi_{N,M}}", from=1-1, to=1-2]
            \arrow["{\tau \circ}"', from=1-1, to=2-1]
            \arrow["{\tau\circ}", from=1-2, to=2-2]
            \arrow["{\Phi_{N,M'}}"', from=2-1, to=2-2]
        \end{tikzcd}\]
        Choosing $g$ in the top left we get 
        \[\tau\circ \Phi_{N,M}(g)(n) = \tau(g(n\tensor 1))\]
        \[\Phi_{N,M'}(\tau\circ g) = \tau(g(n\tensor 1))\]
        which proves the adjunction.
    \end{proof}
\end{exer}

\begin{exer}[1.4.F]
    Show that if an abelian semigroup $S$ is already an abelian group then its groupification is the identity morphism $S \to S$.
    \begin{proof}
    Let $G$ be an abelian group and let $f: S\to G$ be a map of abelian semigroups. Then clearly $f\circ \id = f$, so $f$ factors through the identity map uniquely. It remains to check that $f$ is an abelian group homomorphism. We have 
    \[f(0) = f(0+0) = f(0) + f(0)\]
    so $f(0) = 0$ and 
    \[f(0) = f(a-a) = f(a)+f(-a)\]
    so $f(-a) = -f(a)$.
    \end{proof}
\end{exer}

\begin{exer}[1.4.G]
    Construct the groupification functor $H$ from the category of nonempty abelian semigroups to the category of groups, and show it is left adjoint to the forgetful functor.
    \begin{proof}
    Define $H(S)$ to be the set $S\times S$ modulo the equivalence relation $(a,b)\sim (c,d)$ if there exists $e \in S$ such that $a+d+e = b+c+e$. Let's check this is an equivalence relation. Clearly $(a,b)\sim (a,b)$ since we can take $e$ to be any element. Symmetry is also obvious. For transitivity, suppose $a+d+e = b+c+e$ and $c+y+e' = d+x+e'$. Then adding both equations shows that $(a,b)\sim (x,y)$. The group operation is given by $(a,b)+(c,d) = (a+c,b+d)$. The identity is $(a,a)$ for any $a \in S$, and the inverse of $(a,b)$ is $(b,a)$, so $H(S)$ is indeed an abelian group. Define the map $\phi: S\to H(S)$ by $s \mapsto (s+s, s)$. This is an abelian semigroup morphism since $s+t \mapsto (s+t+s+t, s+t) = (s+s, s) +(t+t, t)$.

    Now let $f: S\to G$ be a map of abelian semigroups. Define $\tilde{f}: H(S)\to G$ via $\tilde{f}(a,b) = f(a)-f(b)$. This is well-defined: suppose $a+d+e = b+c+e$. Then $\tilde{f}(c,d) =f(c)-f(d) = f(a)-f(b)+f(e)-f(e) = \tilde{f}(a,b)$. And $f$ we have $f(s) = \tilde{f}(\phi(s)) = \tilde{f}(s+s, s) = f(s+s)-f(s) = f(s)$. Suppose we have another map $g$ with $f = g\circ \phi$. Then $g$ and $\tilde{f}$ agree on elements of the form $(s+s,s)$. Since we can rewrite any $(s,t) \in H(S)$ as $(s+s, s)- (t+t, t)$, we get that $g(s,t) = g(s+s, s) - g(t+t,t) = g(\phi(s)) - g(\phi(t)) = \tilde{f}(s,t)$. Given a map $\pi: S\to S'$, we define $H(\pi): H(S) \to H(S')$ via $(s,t)\mapsto (\pi(s), \pi(t))$, making $H$ into a functor.

    Now to show adjointness. Let $F$ be the forgetful functor and $G$ and abelian group. Consider the function $\Phi: \Hom(H(S), G)\to \Hom(S, FG)$ given by $\Phi(f)(s) = f(s+s, s)$. In the other direction define $\Psi: \Hom(S, FG)\to \Hom(H(S), G)$ by $\Psi(g)(a,b) = g(a)-g(b)$, which is well-defined by the same reason as above. We check that 
    \[\Phi(\Psi(g))(s) = \Psi(g)(s+s, s) = g(s+s)-g(s) = g(s)\]
    \[\Psi(\Phi(f))(a,b) = \Phi(f)(a)-\Phi(f)(b) = f(a+a, a)-f(b+b,b) = f(a,b).\]

    Now for naturality, let $\pi: S\to S'$ be a map of abelian semigroups and $\tau: G\to G'$ an abelian group homomorphism. The first square to check is 
    \[\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsNCxbMCwxLCJcXEhvbShIKFMpLCBHKSJdLFswLDAsIlxcSG9tKEgoUycpLEcpIl0sWzEsMCwiXFxIb20oUycsRkcpIl0sWzEsMSwiXFxIb20oUyxGRykiXSxbMSwwLCItIFxcY2lyYyBIXFxwaSIsMl0sWzEsMiwiXFxQaGkiXSxbMiwzLCItXFxjaXJjIFxccGkiXSxbMCwzLCJcXFBoaSIsMl1d
        {\Hom(H(S'),G)} & {\Hom(S',FG)} \\
        {\Hom(H(S), G)} & {\Hom(S,FG)}
        \arrow["\Phi", from=1-1, to=1-2]
        \arrow["{- \circ H\pi}"', from=1-1, to=2-1]
        \arrow["{-\circ \pi}", from=1-2, to=2-2]
        \arrow["\Phi"', from=2-1, to=2-2]
    \end{tikzcd}\]
    where $\Phi(f)(\pi(s)) = f(\pi(s)+\pi(s), \pi(s))$ and $\Phi(f\circ H\pi)(s) = (f\circ H\pi)(s+s, s) = f(\pi(s)+\pi(s), \pi(s))$.
    The second square to check is 
    \[\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbShIKFMpLEcpIl0sWzAsMSwiXFxIb20oSChTKSxHJykiXSxbMSwwLCJcXEhvbShTLEZHKSJdLFsxLDEsIlxcSG9tKFMsRkcnKSJdLFswLDIsIlxcUGhpIl0sWzIsMywiRlxcdGF1XFxjaXJjIC0iXSxbMCwxLCJcXHRhdVxcY2lyYyAtIiwyXSxbMSwzLCJcXFBoaSIsMl1d
        {\Hom(H(S),G)} & {\Hom(S,FG)} \\
        {\Hom(H(S),G')} & {\Hom(S,FG')}
        \arrow["\Phi", from=1-1, to=1-2]
        \arrow["{\tau\circ -}"', from=1-1, to=2-1]
        \arrow["{F\tau\circ -}", from=1-2, to=2-2]
        \arrow["\Phi"', from=2-1, to=2-2]
    \end{tikzcd}\]
    where $F\tau(\Phi(g))(s) = \tau(g(s+s,s))$ and $\Phi(\tau\circ g)(s) = \tau(g(s+s,s))$, completing the proof.
    \end{proof}
\end{exer}

\begin{exer}[1.4.H] Let $S$ be a multiplicative subset of $A$. Show that $S^{-1}(-): \catname{Mod}_A\to \catname{Mod}_{S^{-1}A}$ is left adjoint to the forgetful functor $F: \catname{Mod}_{S^{-1}A} \to \catname{Mod}_A$.
    \begin{proof}
        Let us first construct the bijection for $M \in \Mod_A$ and $N \in \Mod_{S^{-1}A}$
        \[\Phi: \Hom_{\Mod_{S^{-1}A}}(S^{-1}M, N) \to \Hom_{\Mod_A}(M,FN).\]
        by sending $f$ on the left to $\Phi(f)(m):= f(m/1)$. In the other direction send $g$ on the right to $\Psi(g)(n/s) = g(n)/s$. These are clearly compatible with the module actions. Then 
        \[\Phi(\Psi(g))(m) = \Psi(g)(m/1) = g(m)/1=g(m) \]
        \[\Psi(\Phi(f))(n/s) = \Phi(f)(n)/s = f(n/1)/s = f(n/s).\]
        Let's check the squares! For morphisms $\pi: M\to M'$ and $\tau: N\to N'$, we have 
        \[
        \begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbV97XFxNb2Rfe1Neey0xfUF9fShTXnstMX1NJywgTikiXSxbMSwwLCJcXEhvbV97XFxNb2RfQX0oTScsIEZOKSJdLFsxLDEsIlxcSG9tX3tcXE1vZF9BfShNLCBGTikiXSxbMCwxLCJcXEhvbV97XFxNb2Rfe1Neey0xfUF9fShTXnstMX1NLCBOKSJdLFswLDEsIlxcUGhpIl0sWzMsMiwiXFxQaGkiLDJdLFsxLDIsIi1cXGNpcmMgXFxwaSJdLFswLDMsIi0gXFxjaXJjIFNeey0xfVxccGkiLDJdXQ==
            {\Hom_{\Mod_{S^{-1}A}}(S^{-1}M', N)} & {\Hom_{\Mod_A}(M', FN)} \\
            {\Hom_{\Mod_{S^{-1}A}}(S^{-1}M, N)} & {\Hom_{\Mod_A}(M, FN)}
            \arrow["\Phi", from=1-1, to=1-2]
            \arrow["{- \circ S^{-1}\pi}"', from=1-1, to=2-1]
            \arrow["{-\circ \pi}", from=1-2, to=2-2]
            \arrow["\Phi"', from=2-1, to=2-2]
        \end{tikzcd}\]
        where $\Phi(f)(\pi(m)) = f(\pi(m)/1)$ and $\Phi(f\circ S^{-1}\pi)(m) = \Phi(f)(S^{-1}\pi(m)) = f(\pi(m)/1)$. The other square is 
        \[\begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXEhvbV97XFxNb2Rfe1Neey0xfUF9fShTXnstMX1NLCBOKSJdLFsxLDAsIlxcSG9tX3tcXE1vZF9BfShNLCBGTikiXSxbMSwxLCJcXEhvbV97XFxNb2RfQX0oTSwgRk4nKSJdLFswLDEsIlxcSG9tX3tcXE1vZF97U157LTF9QX19KFNeey0xfU0sIE4nKSJdLFswLDEsIlxcUGhpIl0sWzMsMiwiXFxQaGkiLDJdLFsxLDIsIkZcXHRhdSBcXGNpcmMgLSJdLFswLDMsIlxcdGF1IFxcY2lyYyAtIiwyXV0=
            {\Hom_{\Mod_{S^{-1}A}}(S^{-1}M, N)} & {\Hom_{\Mod_A}(M, FN)} \\
            {\Hom_{\Mod_{S^{-1}A}}(S^{-1}M, N')} & {\Hom_{\Mod_A}(M, FN')}
            \arrow["\Phi", from=1-1, to=1-2]
            \arrow["{\tau \circ -}"', from=1-1, to=2-1]
            \arrow["{F\tau \circ -}", from=1-2, to=2-2]
            \arrow["\Phi"', from=2-1, to=2-2]
        \end{tikzcd}\]
        where $F\tau\circ \Phi(g)(m)= \tau(g(m/1))$ and $\Phi(\tau\circ g)(m) = \tau(g(m/1))$ which completes the proof.
    \end{proof}
\end{exer}

\subsection{An introduction to abelian categories}
\begin{exer}[1.5.H] Given a complex $A^\bullet$, describe exact sequences 
    \[0\to \im f^i \to A^{i+1}\to \coker f^i\to 0\]
    \[0 \to H^i(A) \to \coker f^{i-1}\to \im f^i \to 0\]
    \begin{soln}
        Let us first show that kernels are monomorphisms and cokernels are epimorphisms. Let $\phi: A\to B$ be a morphism, and let $u: \ker \phi \to A$, $v: B\to \coker \phi$. Suppose we have morphisms $f,g: K\to \ker\phi$ such that $u \circ f = u \circ g$. Then we have the following commutative diagram,
        \[\begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNSxbMSwxLCJcXGtlclxccGhpIl0sWzEsMiwiQSJdLFsyLDIsIkIiXSxbMiwxLCIwIl0sWzAsMCwiSyJdLFswLDNdLFswLDFdLFsxLDIsIlxccGhpIiwyXSxbMywyXSxbNCwwLCJnIiwyLHsib2Zmc2V0IjoxfV0sWzQsMCwiZiIsMCx7Im9mZnNldCI6LTF9XSxbNCwxLCJ1XFxjaXJjIGY9dVxcY2lyYyBnIiwyLHsiY3VydmUiOjJ9XSxbNCwzLCIiLDIseyJjdXJ2ZSI6LTJ9XV0=
            K && \\
            & {\ker\phi} & 0 \\
            & A & B
            \arrow["g"', shift right, from=1-1, to=2-2]
            \arrow["f", shift left, from=1-1, to=2-2]
            \arrow[curve={height=-12pt}, from=1-1, to=2-3]
            \arrow["{u\circ f=u\circ g}"', curve={height=12pt}, from=1-1, to=3-2]
            \arrow[from=2-2, to=2-3]
            \arrow["u",from=2-2, to=3-2]
            \arrow[from=2-3, to=3-3]
            \arrow["\phi"', from=3-2, to=3-3]
        \end{tikzcd}\] 
        which implies $f=g$. Likewise, suppose we have morphisms $f', g': \coker \to L$ such that $f'\circ v = g'\circ v$. Then we get the following commutative diagram
        \[\begin{tikzcd}[cramped]
            % https://q.uiver.app/#q=WzAsNSxbMCwwLCJBIl0sWzAsMSwiQiJdLFsxLDAsIjAiXSxbMSwxLCJcXGNva2VyIFxccGhpIl0sWzIsMiwiTCJdLFsxLDMsInYiLDJdLFswLDEsIlxccGhpIiwyXSxbMCwyXSxbMiwzXSxbMyw0LCJnJyIsMCx7Im9mZnNldCI6LTF9XSxbMyw0LCJmJyIsMix7Im9mZnNldCI6MX1dLFsxLDQsImYnXFxjaXJjIHYgPWcnXFxjaXJjIHYiLDIseyJjdXJ2ZSI6Mn1dLFsyLDQsIiIsMix7ImN1cnZlIjotMn1dXQ==
            A & 0 & \\
            B & {\coker \phi} \\
            && L
            \arrow[from=1-1, to=1-2]
            \arrow["\phi"', from=1-1, to=2-1]
            \arrow[from=1-2, to=2-2]
            \arrow[curve={height=-12pt}, from=1-2, to=3-3]
            \arrow["v"', from=2-1, to=2-2]
            \arrow["{f'\circ v =g'\circ v}"', curve={height=12pt}, from=2-1, to=3-3]
            \arrow["{g'}", shift left, from=2-2, to=3-3]
            \arrow["{f'}"', shift right, from=2-2, to=3-3]
        \end{tikzcd}\]
        which implies $f'=g'$.

        Onto the problem. The first sequence can be written as 
        \[0\to \ker(\coker f^i) \xrightarrow{\alpha} A^{i+1} \xrightarrow{\beta} \coker f^i \to 0.\]
        By what we have just done, this is exact in the first and third entry. Because in abelian categories every monomorphism is the kernel of its cokernel, we have 
        \[\im\alpha = \ker\coker \alpha = \alpha = \ker\coker f^i = \ker \beta\]
        here we are switching back and forth between referring to the map in the (co)kernel and the objects involved. This shows exactness in the middle.

        \textbf{For the next sequence}... epic fail when I tried to do it in an arbitrary abelian category, so let us just stick to Vakil's suggestion of working with modules for now. We can rewrite the sequence as 
        \[0 \to \ker f^i/ \im f^{i-1}\xrightarrow{\alpha} A^i / \im f^{i-1} \xrightarrow{\beta} \im f^i \to 0.\]
        Then we can define $\alpha$ to be the map induced by the composition $\ker f^i \to A^i\to A^i/\im f^i$, which obviously factors through $\im f^{i-1}$. This is injective, making the sequence exact in the first entry. For $\beta$, let it be the map induced by $f^i$, which factors through $\im f^{i-1}$ since $A$ is a complex. This is again surjective since it is just a quotient. We have $\beta(\alpha([x])) = f(x) = 0$ so $\im \alpha \subset \ker \beta$, and conversely if $\beta([y]) = 0$ then $y \in \ker f$ which completes the proof. 
    \end{soln} 
\end{exer}

\begin{exer}[1.5.B] Let 
    \[0\xrightarrow{d^0} A^1 \xrightarrow{d^1} \cdots \xrightarrow{d^{n-1}} A^n \xrightarrow{d^n} 0\]
    be a cochain complex of finite dimensional vector spaces. Define $h^i(A) = \dim H^i(A)$. Show that $\sum (-1)^i \dim A^i = \sum (-1)^i h^i(A)$.
    \begin{proof}
        Let us begin with the right. We know 
        \[h^i(A) = \dim H^i(A) = \dim (\ker d^i / \im d^{i-1}) = \dim \ker d^i - \dim \im d^{i-1}\]
        so taking the alternating sum we have
        \begin{align*}
            \sum (-1)^i h^i(A) &= \sum (-1)^i (\dim \ker d^i - \dim \im d^{i-1}) \\
            &= (\dim \ker d^0 - \dim \im d^{-1}) \\
            &- \dim \ker d^1 + \dim \im d^0 \\
            &+ \cdots \\
            &+ (-1)^n (\dim \ker d^n - \dim \im d^{n-1})\end{align*}
        but note that $\dim \ker d^n = \dim A^n$ and $\dim \im d^{-1} = 0$, so by rank-nullity this sum, after regrouping, is equal to $\sum(-1)^i \dim A^i$ as desired.
    \end{proof}
\end{exer}

\begin{exer}[1.5.C]
Let $\mathcal{C}$ be an abelian category. Show that the category of complexes in $\mathcal{C}$, denoted $\Ch(\mathcal{C})$, is also abelian.
\begin{proof}
    Let us show the axioms one by one. 
    \begin{enumerate}
    \item[A1] \textit{Homsets are abelian groups}. Let $A, B \in \Ch(\mathcal{C})$. Then $\Hom_{\Ch(\mathcal{C})}(A, B)$ is the subgroup of $\prod_{n\in \Z} \Hom_{\mathcal{C}}(A^n, B^n)$ consisting of those morphisms that commute with the maps in $A$ and $B$. This distributes over addition by virtue of the individual morphisms distributing in each $A^n$ and $B^n$.
    \item[A2] \textit{Zero object} The zero object is given by $\cdots \to 0 \to 0 \to 0 \to \cdots$, where $0$ is the zero object in $\mathcal{C}$.
    \item[A3] \textit{Finite products.} Let $A, B \in \Ch(\mathcal{C})$. We claim that their product is given by the chain complex whose $n$th entry is $A^n\times B^n$, and differential defined as follows. Take $A^n\times B^n$ with the projections $\pi_{A^n}$ and $\pi_{B^n}$. Postcompose these with the differentials $A^n\to A^{n+1}$ and $B^n \to B^{n+1}$. This gives maps from $A^n\times B^n \to A^{n+1}$ and $A^n\times B^n \to B^{n+1}$, which by the universal property of products yields our map $d_{A\times B}^n: A^n\times B^n \to A^{n+1}\times B^{n+1}$. Then $d_{A\times B}^2 =0$ by commutativity of the following diagram:
    \[\begin{tikzcd}[cramped]
        % https://q.uiver.app/#q=WzAsOSxbMCwxLCJBXm5cXHRpbWVzIEJebiJdLFs0LDEsIkFee24rMn1cXHRpbWVzIEJee24rMn0iXSxbMiwxLCJBXntuKzF9XFx0aW1lcyBCXntuKzF9Il0sWzEsMiwiQl5uIl0sWzMsMiwiQl57bisxfSJdLFsxLDAsIkFebiJdLFszLDAsIkFee24rMX0iXSxbNSwwLCJBXntuKzJ9Il0sWzUsMiwiQl57bisyfSJdLFswLDVdLFswLDNdLFs1LDYsImRfQV5uIl0sWzIsNl0sWzMsNCwiZF9CXm4iLDJdLFsyLDRdLFswLDIsImRfe0FcXHRpbWUgc0J9Xm4iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMiwxLCJkX3tBXFx0aW1lcyBCfV57bisxfSJdLFs2LDcsImRfQV57bisxfSJdLFs0LDgsImRfQl57bisxfSIsMl0sWzEsOF0sWzEsN11d
        & {A^n} && {A^{n+1}} && {A^{n+2}} \\
        {A^n\times B^n} && {A^{n+1}\times B^{n+1}} && {A^{n+2}\times B^{n+2}} \\
        & {B^n} && {B^{n+1}} && {B^{n+2}}
        \arrow["{d_A^n}", from=1-2, to=1-4]
        \arrow["{d_A^{n+1}}", from=1-4, to=1-6]
        \arrow[from=2-1, to=1-2]
        \arrow["{d_{A\times B}^n}", dashed, from=2-1, to=2-3]
        \arrow[from=2-1, to=3-2]
        \arrow[from=2-3, to=1-4]
        \arrow["{d_{A\times B}^{n+1}}", from=2-3, to=2-5]
        \arrow[from=2-3, to=3-4]
        \arrow[from=2-5, to=1-6]
        \arrow[from=2-5, to=3-6]
        \arrow["{d_B^n}"', from=3-2, to=3-4]
        \arrow["{d_B^{n+1}}"', from=3-4, to=3-6]
    \end{tikzcd}\]
    To show this satisfies the universal property of the product, suppose we have maps $f:C\to A$ and $g: C\to B$ in $\Ch(\mathcal{C})$. Then by definition we get maps $f^n: C^n\to A^n$ and $g^n: C^n \to B^n$ which by the universal property of products in $\mathcal{C}$, we get a map $h^n: C^n \to A^n\times B^n$. Then the $h^n$ assemble into a map $C \to A\times B$ as desired.
    \item[A4] \textit{Every map has a kernel and a cokernel.} Let $f^\bullet: A^\bullet \to B^\bullet$ be a map of complexes. We claim that its kernel is given by the complex $K^\bullet$ with $K^n = \ker f^n$ and levelwise maps $\iota^n: K^n\to A^n$. We first need to elaborate on what the differentials in $K$ are. Consider the following diagram:
    \[ \begin{tikzcd}
        % https://q.uiver.app/#q=WzAsNixbMCwxLCJBXm4iXSxbMCwyLCJCXm4iXSxbMSwyLCJCXntuKzF9Il0sWzEsMSwiQV57bisxfSJdLFswLDAsIlxca2VyIGZebiJdLFsxLDAsIlxca2VyIGZee24rMX0iXSxbMSwyLCJkX0JebiIsMl0sWzAsMywiZF5uX0EiLDJdLFs0LDAsIlxcaW90YV5uIiwyXSxbMCwxLCJmXm4iLDJdLFszLDIsImZee24rMX0iXSxbNCwzLCJkX0FeblxcY2lyYyBcXGlvdGFebiIsMl0sWzQsNSwiIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzUsMywiXFxpb3RhXntuKzF9Il1d
        {\ker f^n} & {\ker f^{n+1}} \\
        {A^n} & {A^{n+1}} \\
        {B^n} & {B^{n+1}}
        \arrow[dashed, from=1-1, to=1-2]
        \arrow["{\iota^n}"', from=1-1, to=2-1]
        \arrow["{d_A^n\circ \iota^n}"', from=1-1, to=2-2]
        \arrow["{\iota^{n+1}}", from=1-2, to=2-2]
        \arrow["{d^n_A}"', from=2-1, to=2-2]
        \arrow["{f^n}"', from=2-1, to=3-1]
        \arrow["{f^{n+1}}", from=2-2, to=3-2]
        \arrow["{d_B^n}"', from=3-1, to=3-2]
    \end{tikzcd}\]
    Since the bottom square commutes, the diagonal map composed with $f^{n+1}$ is zero, so $d_A^n\circ \iota^n$ factors through $\iota^{n+1}$ to yield our map $d_K^n$ from $\ker f^n$ to $\ker f^{n+1}$. To see $d_K^2 = 0$, we can extend the diagram 
    \[\begin{tikzcd}
    % https://q.uiver.app/#q=WzAsNixbMCwxLCJBXm4iXSxbMSwxLCJBXntuKzF9Il0sWzAsMCwiXFxrZXIgZl5uIl0sWzEsMCwiXFxrZXIgZl57bisxfSJdLFsyLDAsIlxca2VyIGZee24rMn0iXSxbMiwxLCJBXntuKzF9Il0sWzAsMSwiZF5uX0EiLDJdLFsyLDAsIlxcaW90YV5uIiwyXSxbMiwxXSxbMiwzLCIiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMywxLCJcXGlvdGFee24rMX0iXSxbMyw0LCIiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMSw1LCJkXntuKzF9X0EiLDJdLFs0LDUsIlxcaW90YV57bisyfSJdLFszLDVdXQ==
	{\ker f^n} & {\ker f^{n+1}} & {\ker f^{n+2}} \\
	{A^n} & {A^{n+1}} & {A^{n+1}}
	\arrow[dashed, from=1-1, to=1-2]
	\arrow["{\iota^n}"', from=1-1, to=2-1]
	\arrow[from=1-1, to=2-2]
	\arrow[dashed, from=1-2, to=1-3]
	\arrow["{\iota^{n+1}}", from=1-2, to=2-2]
	\arrow[from=1-2, to=2-3]
	\arrow["{\iota^{n+2}}", from=1-3, to=2-3]
	\arrow["{d^n_A}"', from=2-1, to=2-2]
	\arrow["{d^{n+1}_A}"', from=2-2, to=2-3]
    \end{tikzcd}\]
    which tells us $\iota^{n+2} \circ d_K^2 = d_A^2\circ \iota^n = 0$, so because $\iota$ is a monomorphism we are done. Thus $K$ is a complex. Now we need to check that % https://q.uiver.app/#q=WzAsNCxbMCwwLCJLIl0sWzAsMSwiQSJdLFsxLDEsIkIiXSxbMSwwLCIwIl0sWzAsM10sWzMsMl0sWzAsMV0sWzEsMl1d
    \begin{tikzcd}
        K & 0 \\
        A & B
        \arrow[from=1-1, to=1-2]
        \arrow[from=1-1, to=2-1]
        \arrow[from=1-2, to=2-2]
        \arrow[from=2-1, to=2-2]
    \end{tikzcd}
    is a Cartesian square. It obviously commutes. Let $\pi: D\to A$ be a map of complexes whose composition with $f$ is zero. Then $f^n\circ \pi^n = 0$ for all $n$, so there is an induced map $\tilde{\pi}^n: D^n\to K^n$ for all $n$ such that $\iota^n \circ \tilde{\pi}^n = \pi^n$. It follows that $\iota \circ \tilde{\pi} = \pi$, so once we show that $\tilde{\pi}$ is a map of complexes are are done. Consider below:
    \[\begin{tikzcd}
        % https://q.uiver.app/#q=WzAsOSxbNCwxLCJLXntuKzF9Il0sWzQsMiwiQV57bisxfSJdLFs1LDIsIkJee24rMX0iXSxbNSwxLCIwIl0sWzMsMCwiRF5uIl0sWzAsMSwiRF5uIl0sWzAsMiwiS15uIl0sWzEsMSwiRF57bisxfSJdLFsxLDIsIktee24rMX0iXSxbMCwzXSxbMywyXSxbMCwxLCJcXGlvdGFee24rMX0iLDJdLFsxLDJdLFs0LDEsImRfQV5uXFxjaXJjIFxccGlebiIsMix7ImN1cnZlIjoyfV0sWzQsMywiIiwwLHsiY3VydmUiOi0yfV0sWzQsMCwiIiwxLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzUsNywiZF9EIl0sWzUsNiwiXFx0aWxkZXtcXHBpfV5uIiwyXSxbNiw4LCJkX0siXSxbNyw4LCJcXHRpbGRle1xccGl9XntuKzF9Il1d
        &&& {D^n} && \\
        {D^n} & {D^{n+1}} &&& {K^{n+1}} & 0 \\
        {K^n} & {K^{n+1}} &&& {A^{n+1}} & {B^{n+1}}
        \arrow[dashed, from=1-4, to=2-5]
        \arrow[curve={height=-12pt}, from=1-4, to=2-6]
        \arrow["{d_A^n\circ \pi^n}"', curve={height=12pt}, from=1-4, to=3-5]
        \arrow["{d_D}", from=2-1, to=2-2]
        \arrow["{\tilde{\pi}^n}"', from=2-1, to=3-1]
        \arrow["{\tilde{\pi}^{n+1}}", from=2-2, to=3-2]
        \arrow[from=2-5, to=2-6]
        \arrow["{\iota^{n+1}}"', from=2-5, to=3-5]
        \arrow[from=2-6, to=3-6]
        \arrow["{d_K}", from=3-1, to=3-2]
        \arrow[from=3-5, to=3-6]
        \end{tikzcd}\]
    To see that the guy on the left commutes, we will show that they make the pullback diagram on the right commute if we put them in place of the dotted arrow, whence by the universal property they are equal. We compute for the top-right path
    \[\iota^{n+1} \circ \tilde{\pi}^{n+1}\circ d_D =  \pi^{n+1}\circ d_D^n = d_A^n\circ \pi^n\]
    since $\pi$ is a map of complexes. And we compute for the bottom-left path 
    \[\iota^{n+1}\circ d^n_K\circ \tilde{\pi}^n = d_A^n \circ \iota^n \circ \tilde{\pi}^n = d_A^n \circ \pi^n\]
    as desired, using the fact that $\iota$ is a map of complexes. This completes the proof. The cokernel is exactly the same.
    \item[A5] \textit{Every monomorphism is the kernel of its cokernel.} Let $f: A\to B$ be a monomorphism and $p: B\to \coker f$ its cokernel. Since $f$ is a monomorphism, its kernel is zero, so $\ker f^n = 0$, so each $f^n$ is a monomorphism. Now $\ker \coker f$ is the complex which is levelwise $\ker \coker f^n$, and because $\mathcal{C}$ is abelian, this is equal to $f^n$ since it is a monomorphism. Hence the kernel of the cokernel of $f$ is the complex which is levelwise $f^n$, so it is itself. 
    \item[A6] \textit{Every epimorphism is the cokernel of its kernel.} By the exact same logic as above. If $g: A\to B$ is an epi, then each $g^n$ is an epi, so $\coker \ker g^n = g^n$, so $\coker \ker g =g$. 
    \end{enumerate}
    Whew!
\end{proof}
\end{exer}

\begin{exer}[1.5.D] Show that a map of complexes $f: A^\bullet \to B^\bullet$ induces a map on cohomology $H^i(A)\to H^i(B)$.
    \begin{proof}
        Let us work with modules. First note that $f^i$ sends the kernel of $d^i_A$ to the kernel of $d_i(B)$, since $d_B^i(f_i(x)) = f^{i+1}d_A^i(x) = 0$. Moreover, $f^i\circ d_A^{i-1} = d_B^{i-1} \circ f^{i-1}$, so $f^i$ sends the image of $d_A^{i-1}$ to the image of $d_B^{i-1}$. Hence $f^i$ induces a map $H^i(A)\to H^i(B)$. 
        
        \textit{Side note: I tried to do this inside an arbitrary abelian category, but could not figure it out... One day I will return.}
    \end{proof}
\end{exer}

\begin{exer}[1.5.E]
    Show that two homotopic maps $f, g: C\to D$ induce the same maps on homology.
    \begin{proof}
        We work with modules again. Let $\omega: C^\bullet \to D^{\bullet-1}$ be the homotopy. Pick some $x \in \ker d_A^i$. We know that 
        \[(f-g)(x) = d_D^{i-1}(\omega^i(x)) + \omega^{i+1}(d_A^i(x)) = d_D^{i-1}(\omega^i(x)).\]
        That is, $f(x)$ and $g(x)$ differ by something in the image of $d_D^{i-1}$, so they are homologous. 
    \end{proof}
\end{exer}  

\begin{exer}[1.5.F]
    Show that applying an exact functor $F: \mathcal{C}\to \mathcal{D}$ to an exact sequence preserves exactness.
    \begin{proof}
        Let $A \xrightarrow{f} B \xrightarrow{g} C$ be exact. We will show that $F$ preserves kernels and images, from which it follows that $\im Ff = F \im f = F\ker g = \ker Fg$. 
        
        Let $f: A\to B$ be a morphism. Then by exactness of $F$ and the sequences 
        \[0\to \ker f\to A \to B, \quad A\to B \to \coker f \to 0\]
        we know that 
        \[0\to F(\ker f)\to FA\to FB,\quad FA\to FB\to F(\coker f)\to 0\]
        are also exact, so $F(\ker f)$ is a mono and $F(\coker f)$ is an epi. By exactness, we obtain 
        \[\ker Ff = \im(F(\ker f)) = F\ker f\]
        since the image of a mono is itself. And from the second sequence
        \[\im Ff = \ker (F\coker f) = F (\ker\coker f) = F(\im f)\]
        where in the middle equality we used what we just proved, that $F$ preserves kernels.
    \end{proof}
\end{exer}

\begin{exer}[1.5.G] Let $A$ be a ring, $S$ a multiplicative subset, and $M$ an $A$-module.
    \begin{enumerate}[(a)]
        \item Show that $S^{-1}(-): \Mod_A\to \Mod_{S^{-1}A}$ is an exact functor.
        \begin{proof}
            Let $N\xrightarrow{f}N'\xrightarrow{g} N''$ be exact. Since $S^{-1}(-)$ is a functor, it is immediate that $S^{-1}g\circ S^{-1}f = 0$, so $\im S^{-1}g \subset \ker S^{-1}f$. To show the other containment, let $a/b \in \ker S^{-1}g$, i.e. $S^{-1}g(a/b) = g(a)/b = 0$. Then there is some $t \in S$ such that $tg(a) = 0$, which gives $g(ta) = 0$, so $ta \in \ker g = \im f$, so let $y \in N$ such that $f(y) = ta$. Then $S^{-1}(y/tb) = ta/tb = a/b$, so $a/b \in \im S^{-1}g$, proving exactness.
        \end{proof}
        \item Show that $(-)\tensor M$ is right exact. 
        \begin{proof}
        This is Exercise 1.2.H.
        \end{proof}
        \item Show that $\Hom(M, -)$ is left exact. For $\mathcal{C}$ an abelian category and $C \in \mathcal{C}$ show that $\Hom(C,-)$ is a left exact functor $\mathcal{C} \to \catname{Ab}$.
        \begin{proof}
            The first part of this follows from the second part. Let $0\to X\xrightarrow{f}Y\xrightarrow{g} Z$ be exact. Let us first show that $f_*$ is a monomorphism. Let $H$ be an abelian group with morphisms $h_1, h_2: H\to \Hom(C,X)$ such that $(f_* \circ h_1)(h) = (f_* \circ h_2)(h)$ for all $h \in H$. But $f_*$ is just postcomposition by $f$, so $f\circ h_1(h) = f\circ h_2(h)$ implies $h_1(h) = h_2(h)$ since $f$ is a mono, so $f_*$ is a mono. 

            Now for exactness at $\Hom(C,Y)$. Take $\phi \in \Hom(C,X)$. Then $g_*f_*(\phi) = g\circ f\circ \phi$. This is the zero homomorphism since $g\circ f = 0$, hence $\im f_*\subset \ker g_*$. Conversely, take some $\psi \in \ker g_*$, i.e. $g\circ \psi$ is the zero morphism. This implies that $\psi$ factors through $\ker g = \im f = f$ since $f$ is a mono. Hence there exists some $\psi'$ such that $f\circ \psi' = \psi$, so $\psi \in \im f_*$. 
        \end{proof}
        \item Likewise, show $\Hom(-,M)$ is left exact. For $\mathcal{C}$ an abelian category and $C \in \mathcal{C}$ show that $\Hom(-,C)$ is a left exact contravariant functor $\mathcal{C} \to \catname{Ab}$.
        \begin{proof}
            Let $X\xrightarrow{f}Y\xrightarrow{g} Z\to 0$ be exact. Let us first show that $g^*$ is a monomorphism. Again let $H$ be an abelian group and $h_1, h_2: H\to \Hom(Z,C)$ such that $(g^*\circ h_1)(h) = (g^*\circ h_2)(h)$ for all $h \in H$. This implies $h_1(h)\circ g = h_2(h)\circ g$, for all $h$, and because $g$ is an epi, we obtain $h_1=h_2$, so $g^*$ is a mono.
            
            For exactness in the midle, take $\phi \in \Hom(Z,C)$. Then $f^*(g^*(\phi)) = \phi \circ g\circ f = 0$, so $\im g^*\subset \ker f^*$. Conversely, let $\psi \in \ker f^*$. Then $\psi\circ f = 0$, so $\psi$ factors through $\coker f = \im g$ by exactness. It follows that there exists some $\tilde{\psi}: \im g\to C$ such that $\psi = \tilde{\psi}\circ g$, so $\psi \in \im g^*$.  
        \end{proof}
    \end{enumerate}
\end{exer}

\begin{exer}[1.5.H]
    Suppose $M$ is a finitely presented $A$-module, i.e. it fits in an exact sequence 
    \[A^{\oplus q}\to A^{\oplus p}\to M\to 0.\] Use this and the left-exactness of $\Hom$ to describe an isomorphism 
    \[S^{-1}\Hom_A(M,N) \to \Hom_{S^{-1}A}(S^{-1}M, S^{-1}N).\]
    \begin{proof}
        By the previous exercise, we know that
        \[S^{-1}A^{\oplus q} \to S^{-1}A^{\oplus q} \to S^{-1}M \to 0\]
        is also exact. Applying $\Hom(-,N)$ to both of these, we get exact sequences 
        \[0\to \Hom(M, N)\to \Hom(A^{\oplus p}, N) \to \Hom(A^{\otimes q}, N)\]
        \[0\to \Hom(S^{-1}M, S^{-1}N)\to \Hom(S^{-1}A^{\oplus p}, S^{-1}N) \to \Hom(S^{-1}A^{\otimes q},S^{-1} N).\]
        We know that localization is exact,  commutes with direct sum, and maps out of a finite direct sum of modules correspond to a finite direct sum of maps, so the sequences become
        \[0\to S^{-1}\Hom(M, N)\to S^{-1}\oplus_p \Hom(A,N)\to S^{-1}\oplus_q\Hom(A,N)\]
        \[0\to \Hom(S^{-1}M, S^{-1}N)\to \oplus_p \Hom(S^{-1}A,S^{-1}N)\to \oplus_q \Hom(S^{-1}A,S^{-1}N)\]
        Finally, for any ring $R$ and $R$-module $L$ we know $\Hom_R(R,L) \cong L$ naturally, so our exact sequences become 
        \[0\to S^{-1}\Hom(M,N) \to (S^{-1}N)^{\oplus p}\to (S^{-1}M)^{\oplus q}\]
        and 
        \[0\to \Hom(S^{-1}M,S^{-1}N) \to (S^{-1}N)^{\oplus p}\to (S^{-1}M)^{\oplus q}\]
        so these two things are the kernel of the same map, hence are isomorphic.
    \end{proof}
\end{exer}

\begin{exer}[1.5.I]
    Let $F:\mathcal{A}\to\mathcal{B}$ be a functor of abelian categories, and let $C^\bullet$ be a complex in $\mathcal{A}$. 
    \begin{enumerate}[(a)]
        \item If $F$ is right exact, show that there is a natural morphism $FH^i(C)\to H^i(FC)$.
        \begin{proof}
            Consider the exact sequence $C^i\xrightarrow{d^i} C^{i+1}\to \coker d^i \to 0$. Since $F$ is right exact, the sequence $FC^i\xrightarrow{Fd^i} FC^{i+1}\to \coker Fd^i \to 0$ remains exact, hence we have an isomorphism $F\coker d^i \cong \coker Fd^i$. Now, applying $F$ to the exact sequence $0\to \im d^i\to C^{i+1}\to \coker d^i\to 0$, we get an exact sequence
            \[F\im d^i \to FC^{i+1}\to F\coker d^i \to 0\]
            so by the universal property of kernels, we have an epimorphism
            \[q: F \im d^i \to \ker F\coker d^i \cong \ker \coker Fd^i = \im Fd^i.\] Finally, we have exact sequences 
            \[0 \to H^i(C) \to \coker d^{i-1}\to \im d^i \to 0\]
            and 
            \[0\to H^i(FC)\to \coker Fd^{i-1} \to \im Fd^i \to 0.\]
            Applying $F$ to the first, we obtain an exact sequence 
            \[FH^i(C) \to F\coker d^{i-1}\to F\im d^i\to 0.\]
            We are now in the following situation:
            \[\begin{tikzcd}
                % https://q.uiver.app/#q=WzAsOSxbMSwwLCJGSF5pKEMpIl0sWzIsMCwiRlxcY29rZXIgZF57aS0xfSJdLFszLDAsIkZcXGltIGReaSJdLFs0LDAsIjAiXSxbMSwxLCJIXmkoRkMpIl0sWzAsMSwiMCJdLFsyLDEsIlxcY29rZXIgRmRee2ktMX0iXSxbMywxLCJcXGltIEZkXmkiXSxbNCwxLCIwIl0sWzAsMV0sWzEsMl0sWzIsM10sWzcsOF0sWzYsN10sWzUsNF0sWzQsNl0sWzEsNiwiXFxjb25nIiwxXSxbMiw3LCJxIl1d
                & {FH^i(C)} & {F\coker d^{i-1}} & {F\im d^i} & 0 \\
                0 & {H^i(FC)} & {\coker Fd^{i-1}} & {\im Fd^i} & 0
                \arrow[color={rgb,255:red,92;green,92;blue,214}, from=1-2, to=1-3]
                \arrow[from=1-3, to=1-4]
                \arrow["\cong"{description}, color={rgb,255:red,92;green,92;blue,214}, from=1-3, to=2-3]
                \arrow[from=1-4, to=1-5]
                \arrow["q", from=1-4, to=2-4]
                \arrow[from=2-1, to=2-2]
                \arrow[from=2-2, to=2-3]
                \arrow[color={rgb,255:red,92;green,92;blue,214}, from=2-3, to=2-4]
                \arrow[from=2-4, to=2-5]
            \end{tikzcd}\]
            where the blue composite is zero, hence there is a factoring $FH^i(C)\to H^i(FC)$ since the latter is the kernel of the final blue arrow.
        \end{proof}
        \item If $F$ is left exact, show that there is a natural morphism $FH^i(C)\leftarrow H^i(FC)$.
        \begin{proof}
            By the dual argument as above, or by 1.5.F, we have an isomorphism $F\ker d^i\cong \ker F d^i$. Now apply $F$ to the exact sequence $0\to \ker d^i \to C^i\to \im d^i\to 0$ to obtain an exact sequence 
            \[0\to F\ker d^i \to FC^i \to F \im d^i\]
            hence $FC^i \to F\im d^i$ factors through the kernel to yield a monomorphism $j: \im Fd^i =\coker(F \ker d^i)\to F\im d^i$.

            To finish, we have exact sequences 
            \[0\to \im d^{i-1}\to \ker d^i \to H^i(C) \to 0\]
            \[0 \to \im Fd^{i-1} \to \ker Fd^i \to H^i(FC)\to 0.\]
            Applying $F$ to the first, we get 
            \[0\to F\im d^{i-1}\to F\ker d^i \to FH^i(C)\]
            which yields the diagram
            \[\begin{tikzcd}
                % https://q.uiver.app/#q=WzAsOSxbMCwwLCIwIl0sWzEsMCwiXFxpbSBGZF57aS0xfSJdLFsyLDAsIlxca2VyIEZkXmkiXSxbMywwLCJIXmkoRkMpIl0sWzQsMCwiMCJdLFswLDEsIjAiXSxbMSwxLCJGXFxpbSBkXntpLTF9Il0sWzIsMSwiRlxca2VyIGReaSJdLFszLDEsIkZIXmkoQykiXSxbMCwxXSxbMSwyLCIiLDAseyJjb2xvdXIiOlswLDYwLDYwXX1dLFsyLDNdLFszLDRdLFs1LDZdLFs2LDddLFs3LDgsIiIsMCx7ImNvbG91ciI6WzAsNjAsNjBdfV0sWzEsNiwiaiIsMl0sWzIsNywiXFxjb25nIiwxLHsiY29sb3VyIjpbMCw2MCw2MF19LFswLDYwLDYwLDFdXV0=
                0 & {\im Fd^{i-1}} & {\ker Fd^i} & {H^i(FC)} & 0 \\
                0 & {F\im d^{i-1}} & {F\ker d^i} & {FH^i(C)}
                \arrow[from=1-1, to=1-2]
                \arrow[color={rgb,255:red,214;green,92;blue,92}, from=1-2, to=1-3]
                \arrow["j"', from=1-2, to=2-2]
                \arrow[from=1-3, to=1-4]
                \arrow["\cong"{description}, color={rgb,255:red,214;green,92;blue,92}, from=1-3, to=2-3]
                \arrow[from=1-4, to=1-5]
                \arrow[from=2-1, to=2-2]
                \arrow[from=2-2, to=2-3]
                \arrow[color={rgb,255:red,214;green,92;blue,92}, from=2-3, to=2-4]
            \end{tikzcd}\]
            where the red arrows compose to zero, implying that the composition of the last two arrows factors through $H^i(FC)$ by the universal property of the cokernel, thus yielding a map $H^i(FC)\to FH^i(C)$.
        \end{proof}
        \item If $F$ is exact, show that the maps above are inverses, hence isomorphisms.
        \begin{proof}
            If $F$ is exact, then the two diagrams at the end of (a) and (b) become stacks of short exact sequences
            \[\begin{tikzcd}
            % https://q.uiver.app/#q=WzAsMTAsWzEsMCwiRkheaShDKSJdLFsyLDAsIkZcXGNva2VyIGRee2ktMX0iXSxbMywwLCJGXFxpbSBkXmkiXSxbNCwwLCIwIl0sWzEsMSwiSF5pKEZDKSJdLFswLDEsIjAiXSxbMiwxLCJcXGNva2VyIEZkXntpLTF9Il0sWzMsMSwiXFxpbSBGZF5pIl0sWzQsMSwiMCJdLFswLDAsIjAiXSxbMCwxXSxbMSwyXSxbMiwzXSxbNyw4XSxbNiw3XSxbNSw0XSxbNCw2XSxbMSw2LCJcXGNvbmciLDFdLFsyLDcsInEiXSxbOSwwXSxbMCw0LCIiLDEseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XV0=
            0 & {FH^i(C)} & {F\coker d^{i-1}} & {F\im d^i} & 0 \\
            0 & {H^i(FC)} & {\coker Fd^{i-1}} & {\im Fd^i} & 0
            \arrow[from=1-1, to=1-2]
            \arrow[from=1-2, to=1-3]
            \arrow[dashed, from=1-2, to=2-2]
            \arrow[from=1-3, to=1-4]
            \arrow["\cong"{description}, from=1-3, to=2-3]
            \arrow[from=1-4, to=1-5]
            \arrow["q", from=1-4, to=2-4]
            \arrow[from=2-1, to=2-2]
            \arrow[from=2-2, to=2-3]
            \arrow[from=2-3, to=2-4]
            \arrow[from=2-4, to=2-5]
            \end{tikzcd}\]
            and
            \[\begin{tikzcd}
                % https://q.uiver.app/#q=WzAsMTAsWzAsMCwiMCJdLFsxLDAsIlxcaW0gRmRee2ktMX0iXSxbMiwwLCJcXGtlciBGZF5pIl0sWzMsMCwiSF5pKEZDKSJdLFs0LDAsIjAiXSxbMCwxLCIwIl0sWzEsMSwiRlxcaW0gZF57aS0xfSJdLFsyLDEsIkZcXGtlciBkXmkiXSxbMywxLCJGSF5pKEMpIl0sWzQsMSwiMCJdLFswLDFdLFsxLDJdLFsyLDNdLFszLDRdLFs1LDZdLFs2LDddLFs3LDhdLFsxLDYsImoiLDJdLFsyLDcsIlxcY29uZyIsMV0sWzgsOV0sWzMsOCwiIiwxLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV1d
                0 & {\im Fd^{i-1}} & {\ker Fd^i} & {H^i(FC)} & 0 \\
                0 & {F\im d^{i-1}} & {F\ker d^i} & {FH^i(C)} & 0
                \arrow[from=1-1, to=1-2]
                \arrow[from=1-2, to=1-3]
                \arrow["j"', from=1-2, to=2-2]
                \arrow[from=1-3, to=1-4]
                \arrow["\cong"{description}, from=1-3, to=2-3]
                \arrow[from=1-4, to=1-5]
                \arrow[dashed, from=1-4, to=2-4]
                \arrow[from=2-1, to=2-2]
                \arrow[from=2-2, to=2-3]
                \arrow[from=2-3, to=2-4]
                \arrow[from=2-4, to=2-5]
            \end{tikzcd}\]
            implying they are isomorphisms.
        \end{proof}
    \end{enumerate}
\end{exer}

\begin{exer}[1.5.J] Let $\mathcal{C}$ be an abelian category and $a,b: \mathcal{I}\to \mathcal{C}$ are diagrams. (Write $A_i = a(i), B_i = b(i)$). Let $h$ be a natural transformation $a \to b$. Then the maps $h_i$ yield another diagram in $\mathcal{C}$ indexed by $\mathcal{I}$. Assuming all limits exist, describe a canonical isomorphism $\lim \ker(h_i) \to \ker(\lim A_i\to \lim B_i)$.
\begin{proof}
    We have projections $\lim \ker(h_i)$ to each $\ker h_i$, which we can compose with the maps $\ker h_i \to A_i $ to yield maps $\lim \ker(h_i) \to A_i$ for each $i$ whose composition with $h_i$ is zero. Therefore we get a map $\lim\ker h_i \to \lim A_i$ whose composition with $\lim A_i\to \lim B_i$ is zero. Thus we get an induced map $\lim \ker h_i\to \ker(\lim A_i\to \lim B_i)$, say $\Phi$.

    We construct an inverse to $\Phi$. First consider the monomorphism $\ker(\lim A_i\to \lim B_i) \to \lim A_i$. We can postcompose with the projection maps $\lim A_i\to A_i$ to obtain maps $\ker(\lim A_i\to \lim B_i) \to A_i$ which are zero after postcomposing with $h_i$. Hence each of these maps factors through $\ker h_i$. By the universal property of the limit these yields a map $\Psi: \ker(\lim A_i\to \lim B_i) \to \lim \ker h_i$.

    Let us check that these are inverse. First for $\Psi\circ \Phi$. Let $\pi_i: \lim \ker h_i \to \ker h_i$ be the projections and $\iota_i: \ker h_i \to A_i$ be the inclusions. It suffices to show that $\pi_i \circ \Psi\circ \Phi = \pi_i$ for every $i$. The way we have defined $\Phi$ and $\Psi$ means that they are the maps making the following diagram commute: 
    \[\begin{tikzcd}
        % https://q.uiver.app/#q=WzAsNyxbMiwxLCJcXGtlcihcXGxpbSBBX2lcXHRvIFxcbGltIEJfaSkiXSxbMiwyLCJcXGxpbSBcXGtlciBoX2kiXSxbMSwyLCJcXGtlciBoX2kiXSxbMCwyLCJBX2kiXSxbMSwxLCJcXGxpbSBBX2kiXSxbMiwwLCJcXGxpbSBcXGtlciBoX2kiXSxbMSwwLCJcXGtlciBoX2kiXSxbMCwxLCJcXFBzaSJdLFsxLDIsIlxccGlfaSJdLFsyLDNdLFswLDRdLFs0LDNdLFs1LDAsIlxcUGhpIl0sWzUsNiwiXFxwaV9pIiwyXSxbNiwzLCIiLDIseyJjdXJ2ZSI6Mn1dLFs1LDRdXQ==
        & {\ker h_i} & {\lim \ker h_i} \\
        & {\lim A_i} & {\ker(\lim A_i\to \lim B_i)} \\
        {A_i} & {\ker h_i} & {\lim \ker h_i}
        \arrow[curve={height=12pt}, from=1-2, to=3-1]
        \arrow["{\pi_i}"', from=1-3, to=1-2]
        \arrow[from=1-3, to=2-2]
        \arrow["\Phi", from=1-3, to=2-3]
        \arrow[from=2-2, to=3-1]
        \arrow[from=2-3, to=2-2]
        \arrow["\Psi", from=2-3, to=3-3]
        \arrow[from=3-2, to=3-1]
        \arrow["{\pi_i}", from=3-3, to=3-2]
    \end{tikzcd}\]
    which implies that $\iota_i \circ \pi_i \circ \Psi\circ \Phi = \iota_i \circ \pi_i$ for every $i$, whereupon we are done since $\iota_i$ is a monomorphism. 

    In the other direction, let $j$ be the inclusion $\ker(\lim A_i\to \lim B_i)\to \lim A_i$. The diagram
    \[ \begin{tikzcd}
            % https://q.uiver.app/#q=WzAsNixbMiwyLCJcXGtlcihcXGxpbSBBX2lcXHRvIFxcbGltIEJfaSkiXSxbMiwxLCJcXGxpbSBcXGtlciBoX2kiXSxbMiwwLCJcXGtlcihcXGxpbSBBX2lcXHRvIFxcbGltIEJfaSkiXSxbMSwwLCJcXGxpbSBBX2kiXSxbMCwwLCJBX2kiXSxbMCwxLCJcXGtlciBoX2kiXSxbMSwwLCJcXFBoaSIsMCx7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6ImRhc2hlZCJ9fX1dLFsyLDEsIlxcUHNpIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzIsM10sWzMsNF0sWzIsNSwiIiwyLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzEsNV0sWzUsNF0sWzEsMywiIiwyLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzAsM11d
            {A_i} & {\lim A_i} & {\ker(\lim A_i\to \lim B_i)} \\
            {\ker h_i} && {\lim \ker h_i} \\
            && {\ker(\lim A_i\to \lim B_i)}
            \arrow[from=1-2, to=1-1]
            \arrow[from=1-3, to=1-2]
            \arrow[dashed, from=1-3, to=2-1]
            \arrow["\Psi", dashed, from=1-3, to=2-3]
            \arrow[from=2-1, to=1-1]
            \arrow[dashed, from=2-3, to=1-2]
            \arrow[from=2-3, to=2-1]
            \arrow["\Phi", dashed, from=2-3, to=3-3]
            \arrow[from=3-3, to=1-2]
        \end{tikzcd}\]
    tells us $j\circ \Phi\circ \Psi = j$, and since $j$ is a mono we are done.
\end{proof}
\end{exer}

\begin{exer}[1.5.K] Make sense of the statement ``limits commute with limits'' in a general category and prove it. 
    \begin{proof}
        Let $\mathcal{I}$ and $\mathcal{J}$ be indexing categories, $\mathcal{C}$ an arbitrary category. Let $F: \mathcal{I}\times \mathcal{J} \to \mathcal{C}$ be a functor. Fixing $j \in \mathcal{J}$, we can consider the functors $i \mapsto F(i,j)$. This yields a functor $F(-,-)$ from $\mathcal{J}$ to $\catname{Fun}(\mathcal{I}, \mathcal{C})$, so we can consider the limit $\lim_{j \in \mathcal{J}} F(-,j)$ in this functor category. This limit is a functor $\mathcal{I} \to \mathcal{C}$, so we can again consider its limit $\lim_{i\in\mathcal{I}} F(-,j)(i) = \lim_{i \in \mathcal{I}} \lim_{j \in \mathcal{J}} F(i,j)$ which yields an object of $\mathcal{C}$. Likewise we could have started by fixing an element of $\mathcal{J}$ to get $\lim_{j \in \mathcal{J}} \lim_{i \in \mathcal{I}} F(i,j)$. The statement is that these two things are isomorphic. Let us prove this.

        Let $X$ be an element of $\mathcal{C}$ with maps $\pi_i: X \to\lim_jF(i,j)$ commuting with morphisms in $\mathcal{I}$. By the universal property of limits, each $\pi_i$ is the data of maps $\pi_{i,j}: X\to F(i,j)$ commuting with morphisms in $\mathcal{J}$. But now these $\pi_{i,j}$ also give a family of maps $\pi_{j}: X\to \lim_iF(i,j)$ commuting with the morphisms in $\mathcal{J}$, upon which we see that $X$ maps to $\lim_iF(i,j)$. So any cone over $i\mapsto \lim_jF(i,j)$ is a cone over $j\mapsto \lim_iF(i,j)$, so the terminal cones, i.e. the limits, are the same in both cases (if they exist).
    \end{proof}
\end{exer}

\begin{exer}[1.5.L] Show that in $\Mod_A$, colimits over filtered index categories are exact. 
    \begin{proof}
    We know that colimits commute with colimits, so colimits commute with cokernels. We just have to show that filtered colimits commute with kernels. Let $\mathcal{I}$ be a filtered indexing category and $F, G: \mathcal{I} \to \Mod_A$ be diagrams of $A$-modules. Let $h$ be a natural transformation $F\to G$. Then we claim that $\colim \ker h_i = \ker (\colim F_i\to \colim G_i)$. Recall that the colimit of a diagram of modules is the direct sum over the diagram of the modules modulo the equivalence relation of ``being in the image of one of the maps from the diagram.'' (Exercise 1.3.E, 1.3.F).

    Let $x \in \ker(\colim F_i\to \colim G_i)$. Then $x$ is represented by some $a \in F_i$ such that $h_i(a)$ is zero in $\colim G_i$. Let $0 \in G_k$. Then by definition of the colimit, there is some $j \in \mathcal{I}$ and morphisms $u: i\to j$ and $v: k\to j$ such that $Gu(h_i(a)) = Gv(0) = 0 \in G_j$. By naturality of $h$, this implies $h_j(Fu(a)) = 0$, so that $Fu(a) \in \ker h_j$. But $Fu(a)$ and $a$ represent the same element in $\colim F_i$, hence $a \in \ker h_j$, so $x \in \colim(\ker h_i)$.

    Conversely, if $y \in \colim(\ker h_i)$, then $y$ is represented by some $b \in \ker h_i$ for some $i$, so $h_i(b) = 0$, so $b$ represents an element in $\ker (\colim F_i\to \colim G_i)$.
    \end{proof}
\end{exer}

\begin{exer}[1.5.M] Show that filtered colimits commute with homology in $\Mod_A$.
    \begin{proof}
        Filtered colimits commute with colimits, so they are right exact. By the previous exercise they also commute with kernels, so they must commute with homology.
    \end{proof}
\end{exer}

\begin{exer}[1.5.N]
    Let $(0\to A_i\to B_i\to C_i \to 0)$ be an inverse system of exact sequences of modules. Call the transition maps $\alpha_i: A_i\to A_{i-1}$, $\beta_i: B_i\to B_{i-1}$, and $\gamma_i: C_i\to C_{i-1}$. Assume that the $\alpha_i$ are surjective. Show that the limit $0\to \lim A_i\to \lim B_i\to \lim C_i\to 0$ is also exact.
    \begin{proof}
    To define the maps, we have $\lim A_i \to A_i\to B_i$ commuting with the structure maps, which induces a map $\lim A_i\to \lim B_i$, and likewise for $\lim B_i\to \lim C_i$. We are in the following situation:
    \[
    \begin{tikzcd}
        % https://q.uiver.app/#q=WzAsOSxbMCwxLCJBX3tpKzF9Il0sWzIsMSwiQV9pIl0sWzAsMywiQl97aSsxfSJdLFsyLDMsIkJfaSJdLFswLDUsIkNfe2krMX0iXSxbMiw1LCJDX2kiXSxbMSwwLCJcXGxpbSBBX2kiXSxbMSwyLCJcXGxpbSBCX2kiXSxbMSw0LCJcXGxpbSBDX2kiXSxbNiwwXSxbMCwyLCJmX3tpKzF9IiwyXSxbMiw0LCJnX3tpKzF9IiwyXSxbNiwxXSxbMSwzLCJmX2kiXSxbMyw1LCJnX2kiXSxbNywyXSxbNywzXSxbOCw0XSxbOCw1XSxbMiwzXSxbMCwxXSxbNCw1XSxbNiw3LCJmXyoiLDIseyJsYWJlbF9wb3NpdGlvbiI6NzB9XSxbNyw4LCJnXyoiLDIseyJsYWJlbF9wb3NpdGlvbiI6NzB9XV0=
        & {\lim A_i} & \\
        {A_{i+1}} && {A_i} \\
        & {\lim B_i} \\
        {B_{i+1}} && {B_i} \\
        & {\lim C_i} \\
        {C_{i+1}} && {C_i}
        \arrow["{\pi^A_{i+1}}"', from=1-2, to=2-1]
        \arrow[from=1-2, to=2-3]
        \arrow["{f_*}"'{pos=0.7}, from=1-2, to=3-2]
        \arrow[from=2-1, to=2-3]
        \arrow["{f_{i+1}}"', from=2-1, to=4-1]
        \arrow["{f_i}", from=2-3, to=4-3]
        \arrow[from=3-2, to=4-1]
        \arrow[from=3-2, to=4-3]
        \arrow["{g_*}"'{pos=0.7}, from=3-2, to=5-2]
        \arrow[from=4-1, to=4-3]
        \arrow["{g_{i+1}}"', from=4-1, to=6-1]
        \arrow["{g_i}", from=4-3, to=6-3]
        \arrow[from=5-2, to=6-1]
        \arrow[from=5-2, to=6-3]
        \arrow[from=6-1, to=6-3]
    \end{tikzcd}\]
    Let us first show that $\lim A_i\to \lim B_i$ is injective. Let $x \in \lim A_i$ and suppose $f_*(x) = 0$. By commutativity of the diagram we have $f_{i}(\pi_{i}^A(x)) = 0$, so by injectivity of $f_{i}$ we know $\pi_{i}^A(x) = 0$ for all $i$. It follows that $x=0$. 
    
    For surjectivity of $\lim B_i \to \lim C_i$, take some $y \in \lim C_i$. Write $c_i$ for the projections $\pi^C_i(y)$. By surjectivity of $g_0$, we can choose a lift $b_0$ of $c_0$. Inductively, given a lift $b_i$ of $c_i$, choose a lift $b_{i+1}'$ of $c_{i+1}$. Then 
    \[g_i(\beta_{i+1}(b_{i+1}') - b_i) = \gamma_{i+1}(g_{i+1}(b_{i+1}')) - c_i = \gamma_{i+1}(c_{i+1})-c_i = 0,\]
    so $\beta_{i+1}(b_{i+1}') - b_i \in \ker g_i = \im f_i$, so take some $a_i \in A_i$ mapping to it. By surjectivity of the $\alpha_i$, there exists some $a_{i+1}$ with $\alpha_{i+1}(a_{i+1}) = a_i$. Then the element $b_{i+1} := b'_{i+1}-f_{i+1}(a_{i+1})$ satisfies 
    \[g_{i+1}(b_{i+1}) = g_{i+1}(b'_{i+1})-g_{i+1}(f_{i+1}(a_{i+1})) = c_i\]
    and 
    \[\beta_{i+1}(b_{i+1}) = \beta_{i+1}(b'_{i+1}) - \beta_{i+1}(f_{i+1}(a_{i+1})) =  \beta_{i+1}(b'_{i+1})  - f_i(\alpha_{i+1}(a_{i+1})) = b_i\]
    so we have produced a $(b_i) \in \lim B_i$ mapping to $y$.

    Finally, for exactness in the middle. Clearly $\im f_* \subset \ker g_*$, since any $x \in \lim A_i$ has to satisfy $\pi^C_i(g_*f_*(x)) =  gf(\pi^A_{i}(x)) = 0$ for all $i$. Conversely, take some $z = \{b_i\} \in \ker g_*$. By commutativity, each $b_i \in \ker g_{i+1} = \im f_{i+1}$, so start with some $a_0 \in A_0$ with $f_0(a_0) = b_0$. Now inductively, given some $a_i$ with $f_i(a_i) = b_i$, choose a lift $a_{i+1}'$ of $b_{i+1}$. Then 
    \[f_i(\alpha_{i+1}(a_{i+1}') - a_i) = \beta_{i}(f_{i+1}(a_{i+1}')) -b_i = \beta_i(b_{i+1}) - b_i = 0,\]
    so $\alpha_{i+1}(a_{i+1}') - a_i$ is in $\ker f_i = 0$, so actually $\alpha_{i+1}(a_{i+1}') = a_i$, so we have found an element $\{a_i\} \in \lim A_i$ mapping to $z$, showing that $\im f_* = \ker g_*$.
    \end{proof} 
\end{exer}

\subsection{Spectral sequences (tbd)}
\begin{quote}
``You should not read this section when you are reading the rest of Chapter 1. Instead, you should read it just before you need it for the first time.'' 
\end{quote} 


