\newpage\section{Sheaves}
\subsection{Motivating example: the sheaf of smooth functions}

\begin{exer}[2.1.A]
Show that $\mfm_p$ is the only maximal ideal of $\mco_p$.
\begin{proof}
    It suffices to show that any $f$ not in $\mfm_p$ is invertible. If $f \notin \mfm_p$, then $f$ is nonzero at $p$, so by smoothness there is some open subset $U$ around $p$ where $f$ is also nonzero, hence $1/f$ is a well-defined function on $U$. Then $(1/f, U)$ is an inverse to $f$ in $\mco_p$.
\end{proof}
\end{exer}

\begin{exer}[2.1.B]
    Let $X$ be a differentiable manifold, $p \in X$, $\mco_p$ and $\mfm_p$ as above. Prove that $\mfm_p/\mfm_p^2$ is naturally the cotangent space to $X$ at $p$.
    \begin{proof}
        One way to define the tangent space of $X$ at $p$ is as the space of derivations at $p$:
        \[T_pX = \{D: C^\infty(X)\to \R: D(fg) = f(p)D(g) + g(p)D(f)\}\]
        so that the cotangent space $T^*_pX$ is just the dual $\Hom_{\R}(T_pX, \R)$. Consider the map $\phi: \mfm_p \to T_p^*X$ defined as follows. Given a germ $(f, U) \in \mfm_p$, we can extend $f: U\to\R$ to a function $\tilde{f}: X\to \R$ via bump functions. Then $(D\mapsto D(\tilde{f}))$ yields an element in $T^*pX$, which we define to be $\phi(f,U)$. This is well-defined for the following reason. If $(f,U)$ and $(g,V)$ represent the same germ, then there is some neighborhood of $p$ in which $f-g$ is zero. We can define a bump function $b$ to be one inside this neighborhood where $f-g$ is zero, and zero outside. Then $b(f-g)$ is identically zero on $X$. Then $0 = D(b(f-g)) = b(p)D(f-g) + D(b)(f-g)(p) = D(f-g)$. 

        Clearly if $f, g\in \mfm_p$, then $\phi(fg) = D(\tilde{f}\tilde{g}) = f(p)D(\tilde{g})+g(p)D(\tilde{f}) = 0$, so $\phi$ descends to a map $\mfm_p/\mfm_p^2 \to T^*_pX$. ... tbd
    \end{proof}
\end{exer}

\subsection{Definition of sheaf and presheaf}
\begin{exer}[2.2.A]
    Given a topological space $X$, let $\catname{Open}(X)$ be the category of open sets where the morhpisms are inclusions. Show that the data of a presheaf is the data of a contravariant functor from $\catname{Open}(X)$ to the category of sets.
    \begin{proof}
    Let us start with a presheaf $\mathcal{F}$. We can define a functor $F: \catname{Open}(X) \to \catname{Set}$ by sending an open set $U$ to $\mathcal{F}(U)$, and an inclusion $U\subset V$ to the restriction map $\res_{V,U}: \mathcal{F}(V)\to \mathcal{F}(U)$. Then the functor respects composition since the restriction maps do, and the identity inclusion maps to the identity map.  Conversely, given a functor $F: \catname{Open}(X)^\mathrm{op}\to\catname{Set}$, we can define a presheaf $\mathcal{F}$ via $\mathcal{F}(U) = F(U)$. For an inclusion $i: U\to V$ we define $\res_{V,U}$ to be $F(i)$. Then the definition of a functor (identity, composition) give us the presheaf conditions.
    \end{proof}
\end{exer}

\begin{exer}[2.2.B]
    Show that the following are presheaves on $\C$ with the standard topology, but not sheaves:
    \begin{enumerate}[(a)]
        \item Bounded functions.
        \begin{proof}
            Take an open cover of $\C$ by open balls $U_n = \{|z|<n\}$. Then the identity map is an element of each $\mathcal{F}(U_n)$. But there is no bounded function that on $\C$ that these glue to.
        \end{proof}
        \item Holomorphic functions admitting a holomorphic square root.
        \begin{proof}
            Recall the argument principle: if $f$ is a meromorphic function inside and on a closed contour $C$, then $\int_C f'/f$ is some integer multiple (number of zeros minus number of poles) of $2\pi i$. Take $C$ to be the unit circle and let $f$ be the identity function. We claim that $f$ has no square root in the annulus $A= \{1-\epsilon < |z| < 1+\epsilon\}$ for some $0<\epsilon <1$. Suppose otherwise, i.e. there is some holomorphic $g$ defined on $A$ with $g^2 =f$. Then by the argument principle, we have 
            \[2\pi i = \int_C \frac{f'(z)}{f(z)} dz = 2\int_C \frac{g'(z)}{g(z)} dz \in 4\pi i \Z\]
            which is a contradiction. Thus $f(z)= z$ admits no holomorphic square root in $A$.But now we can cover the annulus $A$ with simply connected regions, on each of which we can define a holomorphic square root of $f$. So on each of these regions $f(z)= z$ restricts to the identity, so they agree on all intersections, but cannot patch together to a function which admits a holomorphic square root.
        \end{proof}
    \end{enumerate}
\end{exer}

\begin{exer}[2.2.C] The identity and gluability axioms for a sheaf may be interpreted as saying that $\mathcal{F}(\cup_{i} U_i)$ is a certain limit. What limit?
    \begin{soln}
        Let $\mathcal{F}$ be a sheaf over $X$ and let $U_i$ be an open cover of open $U \subset X$. This answer has to do with the ``equalizer exact sequence'' in the paragraph preceeding the exercise. 

        Consider the diagram in $\catname{Set}$ whose objects are the $\mathcal{F}(U_i)$ as well as pairwise intersections $\mathcal{F}(U_i \cap U_j)$ for all $i,j$. We claim that $\mathcal{F}(U) = \mathcal{F}(\cup_i U_i)$ is the limit of this diagram, where the structure maps are induced by the inclusions in $\catname{Open}(X)$, which obviously commute. Let $G$ be another cone of this diagram with structure maps $\phi_i: G \to \mathcal{F}(U_i)$ and $\phi_{ij}: G\to F(U_i\cap U_j)$. Then for any $g \in G$, the images $\phi_i(g)$ are elements of each $\mathcal{F}(U_i)$ whose restrictions to each intersection agree, which by the glueabilty and identity axioms yields a global element in $\mathcal{F}(U)$, which yields our function $\phi: G\to \mathcal{F}(U)$. The axioms further tell us that the restriction of $\phi(g)$ to each $U_i$ agree with the $\phi_i(g)$. This shows that $\mathcal{F}(U)$ is the limit.
    \end{soln}
\end{exer}

\begin{exer}[2.2.D] Sheaf checking.
\begin{enumerate}[(a)]
    \item Verify that the following are sheaves: smooth functions, continuous functions, real-analytic, real-valued functions on a manifold $X$.
    \begin{soln}
        It is easy to see that these are presheaves: the restriction of any of these classes of functions to a smaller open set preserves their smoothness/continuity/analyticity/real-valuedness, and the rules of function composition and restriction yield functoriality. 

        To see these satisfy the identity axiom, let $U$ be an open set in $X$, $\{U_i\}$ an open cover of it. Let $\mathcal{F}$ be the presheaf of any of the above over $X$. Suppose $f,g \in \mathcal{F}(U)$ restrict to the same function on all $U_i$. Then for any $x \in U$, it belongs to some $U_i$, whereby $f(x) = f|_{U_i}(x)=g|_{U_i}(x)=g(x)$. 

        For the glueability axiom, again let $\{U_i\}$ be an open cover of $U$ and suppose we are given $f_i \in \mathcal{F}(U_i)$ that agree on the intersections. We wish to define a function $f$ on $U$ that restricts to each of the $f_i$. So for each $x \in U$, choose some $U_i$ which $x$ belongs to and define $f(x) = f_i(x)$. This is well-defined since the $f_i$ agree on intersections. And $f$ remains smooth/continuous/analytic/real-valued since these are local properties.
    \end{soln}
    \item Show that real-valued continous functions on a topological space $X$ form a sheaf.
    \begin{proof}
        Call this $\mathcal{F}$. Again, $\mathcal{F}$ is a presheaf by virtue of function composition and restriction: if $U\subset V$ and $f: V\to X$ is continuous, then so is $f|_U: U\to X$, since the preimage of an open set $A\subset X$ is just $f|_U^{-1}(A) = U\cap f^{-1}(A)$, which is open in the subspace topology. The same argument as above gives the identity axiom, and the glueability axiom comes from the pasting lemma (which says that the $f$ constructed in (a) is continuous).
    \end{proof}
\end{enumerate}
\end{exer}

\begin{exer}[2.2.E] Let $X$ be a topological space and let $S$ be a set. Let $\mathcal{F}(U)$ be the set of maps $U\to S$ that are locally constant, i.e. for any $p \in U$ there is an open neighborhood around $p$ where the map is constant. Show that $\mathcal{F}$ is a sheaf on $X$.
    \begin{proof}
        The restriction of a locally constant function is clearly locally constant, and the restriction of a restriction is just restriction, so $\mathcal{F}$ is a presheaf.

        The identity axiom is the same as above. For the glueability axiom, given $f_i \in \mathcal{F}(U_i)$ and define the glued $f$ the same as above. Then for any $x \in U$, there is some $U_i$ containing $x$ and a neighborhood $V$ of $x$ contained in $U_i$ where $f_i|_V = f|_V$ is constant. 
    \end{proof}
\end{exer}

\begin{exer}[2.2.F] Suppose $Y$ is a topological space. Show that continuous maps to $Y$ form a sheaf of sets on a space $X$. (This is a generalization of the previous exercises).
    \begin{proof}
   There is nothing new here, the proof is exactly the same.
    \end{proof}
\end{exer}

\begin{exer}[2.2.G] Fancier sheaves.
\begin{enumerate}[(a)]
    \item Show that the sections of a continuous map $\mu: Y\to X$ yield a sheaf on $X$.
    \begin{proof}
        For $U \subset X$ open we let $\mathcal{F}(U)$ be those maps $s: U\to Y$ for which $s \circ \mu = \id|_U$. Let us first show this is a presheaf on $\catname{Open}(X)$. To an inclusion $U\subset V$ we define the restriction map $\res_{V,U}(f) = f|_U$, which remains a section since $(f|_U \circ \mu)(x) = (f\circ \mu)(x) = x$. And restrictions of restrictions are restrictions, so we are done.
        
        For the identity axiom, again let $U$ be open in $X$ and $\{U_i\}$ an open cover of it. Suppose $f|_{U_i} = g|_{U_i}$ for all $i$. Then for any $x \in U$, it belongs to some $U_i$, upon which $f=g$ on all of $U$. For glueability, let $\{U_i\}$ be same as above and suppose we have sections $f_i \in \mathcal{F}(U_i)$ agreeing on intersections. Then define $f: U\to Y$ via the pasting lemma. Then $(f\circ \mu)(x) = (f_i\circ \mu)(x)$ for some $i$, showing that $f$ is a section.
    \end{proof}
    \item Suppose $(Y,+)$ is a topological group. Show that continuous maps $X\to Y$ form a sheaf of groups. 
    \begin{proof}
        The group structure on $\mathcal{F}(U)$ is given by letting $f+g$ be the map $x \mapsto f(x)+g(x)$. The identity is the map sending all elements of $X$ to $0 \in Y$, and the inverse of a map $f$ is the map $x\mapsto -f(x)$. For an inclusion $U\subset V$ again define $\res_{V,U}(f) = f|_U$, which remains continuous. This is a group homomorphism since $(f+g)|_U = f|_U +g|_U$. Restrictions of restrictions are restrictions, so this makes $\mathcal{F}$ into a presheaf of groups.
        
        The identity axiom is the same as above. For glueability, let $\{U_i\}$ be an open cover of open $U \subset X$ and choose $f_i$ in each $\mathcal{F}(U_i)$ agreeing on intersections. Define $f: U\to Y$ again via the pasting lemma.
    \end{proof}
\end{enumerate}
\end{exer}

\begin{exer}[2.2.H]
    Let $\pi: X\to Y$ be a continuous map, and let $\mathcal{F}$ be a presheaf on $X$. Define a presheaf $\pi_*\mathcal{F}$ by $\pi_*\mathcal{F}(V) = \mathcal{F}(\pi^{-1}(V))$. Show this is a presheaf, and a sheaf if $\mathcal{F}$ is a sheaf.
    \begin{proof}
        Let us first show it is a presheaf. Given an inclusion $W\subset V$ of open sets of $Y$, we know $\pi^{-1}(W)\subset \pi^{-1}(V)$ are open in $X$, so we can define $\res_{W,V}(f) = \res_{\pi^{-1}(W), \pi^{-1}(V)}(f)$, upon which composition and identity follow from the fact that $\mathcal{F}$ is a presheaf.  

        Now suppose $\mathcal{F}$ is a sheaf. Suppose we have an open cover $\{V_i\}$ of $V$. Then $\{\pi^{-1}(V_i)\}$ is an open cover of $\pi^{-1}(V)$. So if $f,g \in \pi_*\mathcal{F}(V) = \mathcal{F}(\pi^{-1}(V))$ agree on all their restrictions to $\pi^{-1}(V_i)$, then by the identity axiom on $\mathcal{F}$, we know $f=g$ in $\pi_*\mathcal{F}(V) = \mathcal{F}(\pi^{-1}(V))$. Likewise, for glueability, if we are given compatible $f_i \in \pi_*\mathcal{F}(V_i) = \mathcal{F}(\pi^{-1}(V_i))$, then they glue to an element in $\pi_*\mathcal{F}(V) = \mathcal{F}(\pi^{-1}(V))$ as desired.
    \end{proof}
\end{exer}

\begin{exer}[2.2.I] Let $\pi: X\to Y$ be a continuous map, and $\mathcal{F}$ a sheaf of sets (or rings or modules) on $X$. if $\pi(p) = q$, describe the natural morphism of stalks $(\pi_*\mathcal{F})_q \to \mathcal{F}_p$. 
    \begin{soln}
        The first approach is to use the explicit definition of stalks via representatives, the second via colimits. 

        For the first, recall that an element of $(\pi_*\mathcal{F})_q$ is represented by a tuple $(f,V)$ where $f \in \pi_*\mathcal{F}(V) = \mathcal{F}(\pi^{-1}(V))$ and $q \in V$. It follows that $p \in \pi^{-1}(V)$, so we can send $(f, V)$ to $(f, \pi^{-1}(V))$. Let us see this is well-defined. Suppose $(f, V)\sim (g, W)$, i.e. there is some open $U\subset V, W$ such that $\res_{U,V}(f) = \res_{U,W}(g)$. By how we have defined the pushforward sheaf, $\res_{\pi^{-1}(U), \pi^{-1}(V)}(f) = \res_{\pi^{-1}(U),\pi^{-1}(W)}(g)$, so that $(f, \pi^{-1}(V))\sim (g, \pi^{-1}(W))$. 

        If we work with colimits, notice that for any open $V \subset Y$ containing $q$, that elements of $\pi_*\mathcal{F}(V) = \mathcal{F}(\pi^{-1}(V))$ are representatives in the colimit $\colim_{U \ni p}(\mathcal{F}(U)) = \mathcal{F}_p$, so we have maps from each $\pi_*(\mathcal{F}(V))$ to $\mathcal{F}_p$, which are compatible with the restriction maps (since the restriction maps for $\pi_*\mathcal{F}$ are just those of $\mathcal{F}$). Thus by the universal property of colimits this yields a unique map $(\pi_*\mathcal{F})_q = \colim_{V\ni q}(\pi_*\mathcal{F}(V)) \to \colim_{U \ni p}(\mathcal{F}(U)) = \mathcal{F}_p$.
    \end{soln}
\end{exer}

\begin{exer}[2.2.J]
    If $(X, \mco_X)$ is a ringed space, and $\mathcal{F}$ is an $\mco_X$-module, describe how for each $p\in X$, $\mathcal{F}_p$ is an $\mco_{X,p}$-module.
    \begin{soln}
        Take $(g, V) \in \mco_{X,p}$ and $(f,U) \in \mathcal{F}_p$. Then $W:= V\cap U$ is open, so we can consider the restrictions $g|_W \in \mco_X(W)$ and $f|_W \in \mathcal{F}(W)$, whereupon the $\mco_X$-module structure gives an element $(g|_W)\cdot(f|_W) \in \mathcal{F}(W)$. Then define $(g, V)\cdot (f, U)$ to be $((g|_W)\cdot(f|_W), W) \in \mathcal{F}_p$.

        To see this is well defined, take other representatives $(g', V')$ and $(f', U')$, with $g'|_{V''} = g|_{V''}$ and $f'|_{U''} = f|_U$. Let $W' = U'\cap W'$ and $W''= U''\cap W''$. Then the restrictions of $(g|_W)\cdot(f|_W)$ and $(g'|_{W'})\cdot(f'|_{W'})$ to $W''$ are the same by the $\mco_X$-module structure. The module axioms follow from the fact that $\mathcal{F}$ is an $\mco_X$-module and working with intersections of open sets.
    \end{soln}
\end{exer}

\subsection{Morphisms of presheaves and sheaves}
\begin{exer}[2.3.A]
    If $\phi: \mathcal{F}\to \mathcal{G}$ is a morphism of presheaves on $X$, describe an induced morphism of stalks $\phi_p: \mathcal{F}_p\to \mathcal{G}_p$. (So that taking the stalk at a point $p$ yields a functor from the category of presheaves over $X$ to the category of sets.)
    \begin{soln}
        We define $\phi_p(f, U) := (\phi(U)(f), U)$. This is well-defined, for if we have another representative $(g, V)$ such that $f|_W = g|_W$ for $W \subset U,V$, then by naturality of $\phi$, we get that $\phi(U)(f)|_W = \phi(U)(f|_W) = \phi(U)(g|_W) = \phi(U)(g)|_W$. 

        On the other hand, using the colimit definition of a stalk, for each $U \in \catname{Open}(X)$, we have a map $\phi(U): \mathcal{F}(U) \to \mathcal{G}(U) \to \colim_{p \in U}\mathcal{G} U$ which commutes with the restriction maps by definition of $\phi$, so by the universal property of colimits this induces the desired map $\mathcal{F}_p\to\mathcal{G}_p$.
    \end{soln}
\end{exer}

\begin{exer}[2.3.B]
    Suppose $\pi: Y\to X$ is a continuous map of topological spaces. Show that pushforward gives a functor $\catname{Set}_X \to \catname{Set}_Y$.
    \begin{proof}
    We have already defined this on the objects, so we need to specify what happens to morphisms. Let $\phi: \mathcal{F}\to\mathcal{G}$ be a morphism of presheaves on $X$. Then we need to define a family of maps $\pi_*\phi: \pi_*\mathcal{F}(V)\to \pi_*\mathcal{G}(V)$ for each open $V \subset Y$. But this is the same thing as defining maps $\mathcal{F}(\pi^{-1}(V)) \to \mathcal{G}(\pi^{-1}(V))$, and we can just define these to be $\pi_*\phi(V):= \phi(\pi^{-1}(V))$. Then by the fact that $\phi$ is a morphism of presheaves, so is $\pi_*\phi$. For functoriality, clearly if $\phi$ is the identity then so is $\pi_*\phi$, and given another morphism $\psi: \mathcal{G}\to\mathcal{H}$ of presheaves over $X$, we get that $(\pi_*\psi \circ \pi_*\phi )(V) = (\psi \circ \pi)(\pi^{-1}(V)) = \psi(\pi^{-1}(V))\circ \phi(\pi^{-1}(V)) = \pi_*\psi(V) \circ \psi_*\phi(V)$.
    \end{proof}
\end{exer}

\begin{exer}[2.3.C] Let $\mathcal{F}$ and $\mathcal{G}$ be sheaves of sets on $X$. Show that ``sheaf hom,'' $\shom(\mathcal{F},{G})(U):= \mathrm{Mor}(\mathcal{F}|_U, \mathcal{G}|_U)$, is a sheaf on $X$.
    \begin{proof}
        Let $U\subset V$ be an inclusion of open sets in $X$. We need to define the restriction function $\mathrm{Mor}(\mathcal{F}|_V, \mathcal{G}|_V) \to \mathrm{Mor}(\mathcal{F}|_U, \mathcal{G}|_U)$. Given a natural transformation $\alpha \in \mathrm{Mor}(\mathcal{F}|_V, \mathcal{G}|_V)$, we have for any open set $W$ in $U$ (and hence in $V$) a map $\alpha(W): \mathcal{F}(W) \to \mathcal{G}(W)$. So just send $\alpha$ to $\alpha|_U$. Then the identity gets sent to the identity, and composition is respected by restriction. 
                                     
        For the identity axiom. Suppose $\{U_i\}$ is an open cover of $U$ and that $f, g \in \shom(\mathcal{F},\mathcal{G})(U)$ agree on all their restrictions $f_i := f|_{U_i}, g_i = g|_{U_i} \in \mathrm{Mor}(\mathcal{F}|_{U_i}, \mathcal{G}|_{U_i})$, that is, for any open set $V_i \subset U_i$,  $f_i(V_i)$ and $g_i(V_i)$ are the same function. Now take an element $x \in \mathcal{F}(U)$. We then get the commutative diagram
        \[\begin{tikzcd}
            % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXG1hdGhjYWx7Rn0oVSkiXSxbMCwxLCJcXG1hdGhjYWx7Rn0oVV9pKSJdLFsxLDAsIlxcbWF0aGNhbHtHfShVKSJdLFsxLDEsIlxcbWF0aGNhbHtHfShVX2kpIl0sWzAsMSwiXFxyZXNeXFxtYXRoY2Fse0Z9X3tVLFVfaX0iLDJdLFsxLDMsImZ8X3tVX2l9PWd8X3tVX2l9IiwyXSxbMiwzLCJcXHJlc15cXG1hdGhjYWx7R31fe1UsVV9pfSJdLFswLDIsImYiLDAseyJvZmZzZXQiOi0xfV0sWzAsMiwiZyIsMix7Im9mZnNldCI6MX1dXQ==
        {\mathcal{F}(U)} & {\mathcal{G}(U)} \\
        {\mathcal{F}(U_i)} & {\mathcal{G}(U_i)}
        \arrow["f(U)", shift left, from=1-1, to=1-2]
        \arrow["g(U)"', shift right, from=1-1, to=1-2]
        \arrow["{\res^\mathcal{F}_{U,U_i}}"', from=1-1, to=2-1]
        \arrow["{\res^\mathcal{G}_{U,U_i}}", from=1-2, to=2-2]
        \arrow["{f(U)|_{U_i}=g(U)|_{U_i}}"', from=2-1, to=2-2]
    \end{tikzcd}\]
    which implies $\res^{\mathcal{G}}_{U, U_i}(f(U)(x)) = \res^{\mathcal{G}}_{U, U_i}(g(U)(x))$ for all $i$, and because $\mathcal{G}$ is a sheaf this implies $f(U)(x)=g(U)(x)$. 

    For glueability. Let $\{U_i\}$ be an open cover of $U$ and suppose we have natural transformations $\alpha_i \in \shom(\mathcal{F},\mathcal{G})(U_i)$ for each $i$ that agree on intersections. We would like to define an element $\alpha \in \shom(\mathcal{F},\mathcal{G})(U) = \mathrm{Mor}(\mathcal{F}|_U, \mathcal{G}|_U)$ (i.e. a natural family of functions $\mathcal{F}(V)\to\mathcal{G}(V)$ for each open $V\subset U$), that restricts to each $U_i$. So fix an open subset $V\subset U$ and an element $x \in \mathcal{F}(V)$. Then $V_i = V \cap U_i$ yields an open cover of $V$. Consider the elements 
    \[\alpha_i(V_i)(\res^{\mathcal{F}}_{V, V_i}(x)) \in \mathcal{G}(V_i)\]
    which are a family of elements in each $\mathcal{G}(V_i)$ that agree on the intersections of the $V_i$, so because $\mathcal{G}$ is a sheaf, this yields an element in $\mathcal{G}(V)$ which we shall define to be $\alpha(V)(x)$. Then the restriction of $\alpha$ to $U_i$ is $\alpha_i$ by construction.
    \end{proof}
\end{exer}

\begin{exer}[2.3.D] More sheaf homs.
    \begin{enumerate}[(a)]
        \item If $\mathcal{F}$ is a sheaf of sets on $X$, show that $\shom(\uline{\{*\}}, \mathcal{F})\cong \mathcal{F}$, where $\uline{\{*\}}$ is the constant sheaf with values in the one-element set $\{*\}$. 
        \begin{proof}
            For any open set $U$, we have $\shom(\uline{\{*\}}, \mathcal{F})(U) = \mathrm{Mor}(\{*\}, \mathcal{F}(U))$, which is in natural bijection $\mathcal{F}(U)$ just by looking at where $*$ goes.
        \end{proof}
    
        \item If $\mathcal{F}$ is a sheaf of abelian groups on $X$, show that $\shom_{\catname{Ab}_X}(\uline{\Z}, \mathcal{F}) \cong \mathcal{F}$ as an isomorphism of sheaves of abelian groups.
        \begin{proof}
            Again, for open $U$, we have $\shom_{\catname{Ab}_X}(\uline{\Z},\mathcal{F})(U) = \Hom(\Z, \mathcal{F}(U))$, which is naturally isomorphic to $\mathcal{F}(U)$ by looking at where $1 \in \Z$ is sent.
        \end{proof}

        \item If $\mathcal{F}$ is an $\mco_X$-module, show that $\shom_{\catname{Mod}_{\mco_X}}(\mco_X, \mathcal{F})\cong \mathcal{F}$ as $\mco_X$-modules.
        \begin{proof}
            Same as above, we have $\shom_{\catname{Mod}_{\mco_X}}(\mco_X, \mathcal{F})(U) = \Hom(\mco_X(U), \mathcal{F}(U)) \cong \mathcal{F}(U)$ naturally via the map $f \mapsto f(1)$.
        \end{proof}
\end{enumerate}
\end{exer}

\begin{exer}[2.3.E]
If $\phi: \mathcal{F}\to \mathcal{G}$ is a morphism of presheaves (of abelian groups) on $X$, show that $\ker \phi$ given by $(\ker\phi)(U) = \ker(\phi(U))$ is a presheaf.
\begin{proof}
    Let $V \subset U$ be open subsets of $X$. Then we have exact sequences assembling into the following commutative diagram: 
    \[ \begin{tikzcd}
        % https://q.uiver.app/#q=WzAsOCxbMCwwLCIwIl0sWzEsMCwiXFxrZXIoXFxwaGkoVSkpIl0sWzIsMCwiXFxtYXRoY2Fse0Z9KFUpIl0sWzMsMCwiXFxtYXRoY2Fse0d9KFUpIl0sWzAsMSwiMCJdLFsxLDEsIlxca2VyKFxccGhpKFYpKSJdLFsyLDEsIlxcbWF0aGNhbHtGfShWKSJdLFszLDEsIlxcbWF0aGNhbHtHfShWKSJdLFsyLDYsIlxccmVzXlxcbWF0aGNhbHtGfV97VixVfSJdLFsyLDMsIlxccGhpKFUpIl0sWzMsNywiXFxyZXNee1xcbWF0aGNhbHtHfX1fe1YsVX0iXSxbNiw3LCJcXHBoaShWKSJdLFsxLDJdLFs1LDZdLFswLDFdLFs0LDVdXQ==
        0 & {\ker(\phi(U))} & {\mathcal{F}(U)} & {\mathcal{G}(U)} \\
        0 & {\ker(\phi(V))} & {\mathcal{F}(V)} & {\mathcal{G}(V)}
        \arrow[from=1-1, to=1-2]
        \arrow[color={rgb,255:red,214;green,92;blue,92}, from=1-2, to=1-3]
        \arrow[dashed, from=1-2, to=2-2]
        \arrow["{\phi(U)}", from=1-3, to=1-4]
        \arrow["{\res^\mathcal{F}_{V,U}}", color={rgb,255:red,214;green,92;blue,92}, from=1-3, to=2-3]
        \arrow["{\res^{\mathcal{G}}_{V,U}}", from=1-4, to=2-4]
        \arrow[from=2-1, to=2-2]
        \arrow[from=2-2, to=2-3]
        \arrow["{\phi(V)}", from=2-3, to=2-4]
    \end{tikzcd}\]
    By exactness and commutativity of the diagram, the composition of the two red arrows, after postcomposing with $\phi(V)$, yields the zero map, so by the universal property it has to factor through $\ker(\phi(V))$ via the dotted map above. Let this dotted arrow be $\res^{\ker\phi}_{V,U}$. 

    Then given another open subset $W \subset V$, we can just stack another row below the diagram above, and it follows by uniqueness that $\res_{W,V}^{\ker\phi}\circ \res_{V,U}^{\ker\phi}$ is equal to $\res_{W,U}^{\ker \phi}$ since the former is a factoring of $\res_{W,V}^{\mathcal{F}} \circ \res_{V,U}^\mathcal{F}$ and the latter is a factoring of $\res_{W,U}^{\mathcal{F}}$, but these two are the same since $\mathcal{F}$ is a presheaf. And clearly $\res^{\ker\phi}_{U,U}$ is the identity.
\end{proof} 
\end{exer}

\begin{exer}[2.3.F] Let $\phi: \mathcal{F}\to \mathcal{G}$ be as above. Show that $\coker \phi$ satisfies the universal property of cokernels in the category of presheaves.
    \begin{proof}
        Let $\psi: \mathcal{G}\to \mathcal{H}$ be a morphism of presheaves such that $\psi\circ \phi = 0$, i.e. $\psi(U)\circ \phi(U) = 0$ for all opens $U \subset X$. Let $q(U): \mathcal{G}(U) \to (\coker\phi)(U)$ be the canonical cokernel maps. By the universal property of cokernels in the category of abelian groups, there is a unique map $j(U): \coker(\phi(U)) = (\coker\phi)(U)\to \mathcal{H}(U)$ such that $\psi(U) = j(U)\circ q(U)$. It remains to show that the collection of $j(U)$ for each $U$ assemble into a morphism of presheaves $\coker\phi \to \mathcal{H}$. So let $V\subset U$ be an inclusion. We then get the diagram below:
        \[ \begin{tikzcd}[sep=2.25em]
            % https://q.uiver.app/#q=WzAsOCxbMSwxLCJcXG1hdGhjYWx7R30oVSkiXSxbMiwxLCJcXG1hdGhjYWx7SH0oVSkiXSxbMiwwLCJcXGNva2VyIChcXHBoaShVKSkiXSxbMiwyLCJcXG1hdGhjYWx7R30oVikiXSxbMywyLCJcXG1hdGhjYWx7SH0oVikiXSxbMywxLCJcXGNva2VyKFxccGhpKFYpKSJdLFswLDEsIlxcbWF0aGNhbHtGfShVKSJdLFsxLDIsIlxcbWF0aGNhbHtGfShWKSJdLFswLDFdLFswLDIsInEoVSkiXSxbMiwxLCJqKFUpIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzAsMywiXFxyZXNee1xcbWF0aGNhbHtHfX0iXSxbMSw0LCJcXHJlc15cXG1hdGhjYWx7SH0iXSxbMyw0XSxbMyw1LCJxKFYpIiwyXSxbNSw0LCJqKFYpIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzIsNSwiXFxyZXNee1xcY29rZXJ9IiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoiZGFzaGVkIn19fV0sWzYsMF0sWzYsNywiXFxyZXNee1xcbWF0aGNhbHtGfX0iXSxbNywzXV0=
            && {\coker (\phi(U))} & \\
            {\mathcal{F}(U)} & {\mathcal{G}(U)} & {\mathcal{H}(U)} & {\coker(\phi(V))} \\
            & {\mathcal{F}(V)} & {\mathcal{G}(V)} & {\mathcal{H}(V)}
            \arrow["{j(U)}", dashed, from=1-3, to=2-3]
            \arrow["{\res^{\coker}}", dashed, from=1-3, to=2-4]
            \arrow[from=2-1, to=2-2]
            \arrow["{\res^{\mathcal{F}}}", from=2-1, to=3-2]
            \arrow["{q(U)}", from=2-2, to=1-3]
            \arrow[from=2-2, to=2-3]
            \arrow["{\res^{\mathcal{G}}}", from=2-2, to=3-3]
            \arrow["{\res^\mathcal{H}}", from=2-3, to=3-4]
            \arrow["{j(V)}", dashed, from=2-4, to=3-4]
            \arrow[from=3-2, to=3-3]
            \arrow["{q(V)}"', from=3-3, to=2-4]
            \arrow[from=3-3, to=3-4]
        \end{tikzcd}\]
        On the right ``triangular prism'' looking thing, the bottom square (consisting of $\mathcal{G}$, $\mathcal{H}$) commutes, and the diagonal square (consisting of $\mathcal{G}$, $\coker\phi$) commutes. We then get the following sequence of equalities:
        \begin{align*}
        \res^{\mathcal{H}}\circ j(U)\circ q(U) &=\res^{\mathcal{H}}\circ \psi(U) \\
        &= \psi(V) \circ \res^{\mathcal{G}} \\
        &= j(V) \circ q(V)\circ \res^{\mathcal{G}} \\
        &= j(V) \circ \res^{\coker}\circ q(U)
        \end{align*}
        and because $q(U)$ is an epimorphism we conclude the the back square commutes, i.e. $j$ is a morphism of presheaves which satisfies $\psi(U) = j(U)\circ q(U)$ for all $U$. Uniqueness follows from uniqueness in the category of abelian groups for each $U$.
    \end{proof}
\end{exer}

\begin{exer}[2.3.G] Show that for a topological space $X$ and open $U\subset X$, $\mathcal{F}\mapsto \mathcal{F}(U)$ is a functor from $\Ab^{\mathrm{pre}}_X$ to $\Ab$. Then show that this functor is exact.
    \begin{proof}
        For a morphism of sheaves $\phi: \mathcal{F}\to \mathcal{G}$ we automatically get a map $\phi(U): \mathcal{F}(U)\to \mathcal{G}(U)$. For another morphism $\psi: \mathcal{G}\to\mathcal{H}$, we get $(\psi\circ \phi)(U) = \psi(U)\circ \phi(U)$ by definition, and the identity presheaf morphism $\id: \mathcal{F}\to \mathcal{F}$ is also the identity on each open set. So this is a functor.

        By the way we have defined the kernel and cokernel of a presheaf, we know that $(\ker \phi)(U) = \ker(\phi(U))$ and likewise for the cokernel. So this functor preserves (co)kernels and is therefore exact.
    \end{proof}
\end{exer}

\begin{exer}[2.3.H] Show that a sequence of presheaves $0 \to \mathcal{F}_1\xrightarrow{\phi_1} \cdots \xrightarrow{\phi_{n-1}} \mathcal{F}_n\to 0$ is exact iff $0 \to \mathcal{F}_1(U)\to \cdots \to \mathcal{F}_n(U)\to 0$ is exact for all $U$.
    \begin{proof}
        The forward direction follows from the previous exercise. Conversely, we have that 
        \[(\ker \phi_i)(U) = \ker(\phi_i(U)) = \im(\phi_{i-1}(U)) = (\im \phi_{i-1})(U)\]
        for all $U$ and $i$, so $\ker\phi_i = \im \phi_{i-1}$ for all $i$. (Here $\phi_0$ and $\phi_n$ are the zero maps.)
    \end{proof}
\end{exer}

\begin{exer}[2.3.I]
    Let $\phi: \mathcal{F}\to \mathcal{G}$ be a morphism of sheaves on $X$. Show that the presheaf kernel is also a sheaf, and that it satifes the universal property.
    \begin{proof}
        We already know it is a presheaf. For the identity axiom, let $U$ be an open set and $\{U_i\}$ an open cover. Suppose we have two elements $f, g \in \ker_\pre\phi$ whose restrictions $f|_{U_i}$ and $g|_{U_i}$ agree for all $i$. Let $\iota: \ker_\pre\phi \to \mathcal{F}$ denote the canonical monomorphism. By this being a morphism of presheaves, we have 
        \[\iota(U)(f)|_{U_i} = \iota(U_i)(f|_{U_i}) = \iota(U_i)(g|_{U_i})= \iota(U)(g)|_{U_i}\]
        for all $i$, and because $\mathcal{G}$ is a sheaf we get by the identity axiom that $\iota(U)(f) = \iota(U)(g)$. But $\iota(U)$ is injective, so $f=g$.
        
        For glueability, again let $U$ be open and $\{U_i\}$ an open cover. Suppose we have $f_i \in \ker_\pre\phi(U_i)$ agreeing on all intersections. Then 
        \[\iota(U_i)(f_i)|_{U_i\cap U_j} = \iota(U_i\cap U_j)(f_i|_{U_i\cap U_j}) =  \iota(U_i\cap U_j)(f_j|_{U_i\cap U_j}) = \iota(U_j)(f_j)|_{U_i\cap U_j}\]
        so the $\iota(U_i)(f_i)$ are also a compatible family of sections in $\mathcal{F}$, so by glueability there is some $\tilde{f} \in \mathcal{F}(U)$ such that $\tilde{f}|_{U_i} = \iota(U_i)(f_i)$ for all $i$. Notice that for each $U_i$, 
        \[\phi(U)(\tilde{f})|_{U_i} = \phi(U_i)(\tilde{f}|_{U_i}) = \phi(U_i)(f_i) = 0\]
        since $f_i \in \ker_\pre\phi(U_i)$. Therefore $\phi(U)(\tilde{f})|_{U_i}$ is zero for all $i$, so $\phi(U)(\tilde{f}) = 0$ and there exists some $f \in \ker_\pre\phi(U)$ with $\iota(U)(f) = \tilde{f}$, from which it follows that 
        \[\iota(U_i)(f|_{U_i}) = \iota(U)(f)|_{U_i} = \tilde{f}|_{U_i} = \iota(U_i)(f_i)\]
        and because $\iota(U_i)$ is a mono we get $f|_{U_i} = f_i$ for all $i$.

        Suppose $\psi: \mathcal{E}\to \mathcal{F}$ is a morphism of sheaves with $\psi\circ \phi = 0$. Then $\psi(U)$ factors through $\ker_\pre\phi(U) = \ker(\phi(U))$ for each $U$, yielding a morphism of presheaves by 2.3.E. But a morphism of sheaves is just a morphism of underlying presheaves. This yields the universal property.
    \end{proof}
\end{exer}

\begin{exer}[2.3.J]
    Let $X$ be $\C$ with the standard topology, $\mco_X$ be the sheaf of holomorphic functions, and let $\mathcal{F}$ be the presheaf of functions admitting a holomorphic logarithm. Describe an exact sequence of presheaves on $X$ 
    \[0\to \uline{\Z}\to \mco_X \to \mathcal{F}\to 0\]
    but show that $\mathcal{F}$ is not a sheaf. (Hence the presheaf cokernel is not always the sheaf cokernel.)
    \begin{proof}
    The map $\phi: \uline{\Z}\to \mco_X$ is given by inclusion: each map $\Z = \uline{\Z}(U) \to \mco_X(U)$ sends $n \in \Z$ to the constant function at $n$. This is clearly injective. The map $\psi: \mco_X \to \mathcal{F}$ sends $f \in \mco_X(U)$ to $\exp(2\pi i f) \in \mathcal{F}(U)$. This is clearly surjective, since if $h$ admits a holomorphic logarithm then $\psi(\frac{\log h}{2\pi i}) = \exp(\log h) = h$. For exactness, we clearly have in one direction $\psi(U)\circ\phi(U)(n) = \exp(2\pi i n) = 1$. In the other, suppose $\exp(2\pi i f) = 1$. Then $f(z)$ is an integer for all $z \in U$, so $f$, being holomorphic, must be locally constant on $U$, i.e. $f \in \uline{\Z}(U)$. 
    
    But $\mathcal{F}$ is not a sheaf. Cover $\C^\times$ with two open sets $U_1, U_2$ and choose a branches of $\log z$ on each. Then $h(z) = z$ restricted to each $U_i$ admits a holomorphic logarithm, but the only possible glueing, which is again the identity function on $\C^\times$, does not.
    \end{proof}
\end{exer}

\subsection{Properties determined at the level of stalks, and sheafification}
\begin{exer}[2.4.A] Prove that a section of a sheaf of sets is determined by its germs, i.e. the natural map $\mathcal{F}(U)\to \prod_{p \in U}\mathcal{F}_p$  is injective.
\begin{proof}
The natural map sends a section $g \in \mathcal{F}(U)$ to the tuple $(f_p)_{p \in U}$. Suppose $(f_p)_{p \in U} = (g_p)_{p \in U}$ for all $p$. Then for each $p$, there exists some open $V_p$ with $f|_{V_p} = g|_{V_p}$. The collection of $V_p$ form an open cover of $U$, so by the identity axiom we know that $f=g$.
\end{proof}
\end{exer}

\begin{exer}[2.4.B]
    Prove that any choice of compatible germs for a sheaf of sets $\mathcal{F}$ over $U$ is the image of a section of $\mathcal{F}$ over $U$ under the map in the previous exercise.
    \begin{proof}
        Let $(s_p)_{p \in U}$ consist of compatible germs, i.e. for each $p \in U$ there is an open set $U_p \ni p$ and some $\tilde{s}_p \in \mathcal{F}(U_p)$ whose germ at $q \in U_p$ is $s_q$. We know that the $\{U_p\}$ are a open cover of $U$. Take $p, p' \in U$, and consider $\tilde{s}_p$ and $\tilde{s}_{p'}$. Since we have compatible germs, we know for each $q \in U_p \cap U_{p'}$ that $(\tilde{s}_p)_q = (\tilde{s}_{p'})_q$, i.e. there is an open set $V_q \subset U_p\cap U_{p'}$ containing $q$ where the restrictions $\tilde{s}_p$ and $\tilde{s}_{p'}$ agree. Since this holds for each $q$, and the $V_q$ form an open cover of $U_p \cap U_{p'}$, we get by the identity axiom that $\tilde{s}_p$ and $\tilde{s}_{p'}$ agree on the intersections. Therefore, by the glueability axiom there is a section $s \in \mathcal{F}(U)$ that restricts to $\tilde{s}_p$ on each $U_p$. Moreover, the germ of $s$ at $p$ is the germ of $\tilde{s}_p$ at $p$, which is $s_p$, completing the proof.
    \end{proof}
\end{exer}

\begin{exer}[2.4.C] If $\phi_1$ and $\phi_2$ are morphisms from a presheaf of sets $\mathcal{F}$ to a sheaf of sets $\mathcal{G}$ that induce the same map on each stalk, show that $\phi_1 = \phi_2$. 
    \begin{proof}
    Following the hint, we consider the following diagram
    \[\begin{tikzcd}
        % https://q.uiver.app/#q=WzAsNCxbMCwwLCJcXG1hdGhjYWx7Rn0oVSkiXSxbMSwwLCJcXG1hdGhjYWx7R30oVSkiXSxbMCwxLCJcXHByb2Rfe3BcXGluIFV9XFxtYXRoY2Fse0Z9X3AiXSxbMSwxLCJcXHByb2Rfe3BcXGluIFV9IFxcbWF0aGNhbHtHfV9wIl0sWzEsMywiIiwwLHsic3R5bGUiOnsidGFpbCI6eyJuYW1lIjoiaG9vayIsInNpZGUiOiJ0b3AifX19XSxbMCwxLCJcXHBoaV8yKFUpIiwyLHsib2Zmc2V0IjoxfV0sWzIsM10sWzAsMl0sWzAsMSwiXFxwaGlfMShVKSIsMCx7Im9mZnNldCI6LTF9XV0=
        {\mathcal{F}(U)} & {\mathcal{G}(U)} \\
        {\prod_{p\in U}\mathcal{F}_p} & {\prod_{p\in U} \mathcal{G}_p}
        \arrow["{\phi_2(U)}"', shift right, from=1-1, to=1-2]
        \arrow["{\phi_1(U)}", shift left, from=1-1, to=1-2]
        \arrow[from=1-1, to=2-1]
        \arrow[hook, from=1-2, to=2-2]
        \arrow[from=2-1, to=2-2]
    \end{tikzcd}\]
    But the maps induced by $\phi_1$ and $\phi_2$ agree on the stalks, so there is just one bottom arrow making the square commute for either $\phi_1(U)$ or $\phi_2(U)$, i.e. for each $f \in \mathcal{F}(U)$ and $p \in U$, we have $(\phi_1(U)(f))_p = (\phi_2(U)(f))_p$. By injectivity (Exercise 2.4.B), we get that $\phi_1(U)(f) = \phi_2(U)(f)$ for all $U$ and $f$, so $\phi_1 = \phi_2$.
    \end{proof}
\end{exer}

\begin{exer}[2.4.D] Show that a morphism $\phi: \mathcal{F} \to \mathcal{G}$ of sheaves of sets is an isomorphism if and only if it induces an isomorphism of all stalks.
    \begin{proof}
        For the forward direction, recall the definition of the induced map of stalks (Exercise 2.3.A). It is obvious that if $\phi$ is an isomorphism then each map on stalks $\phi_p$ also has an inverse given by the inverse of $\phi$. 

        For the backward direction, let $f, g \in \mathcal{F}(U)$ and suppose $\phi(U)(f) = \phi(U)(g)$. It follows that for each $p \in U$,
        \[\phi_p(f_p) = (\phi(U)(f))_p  = (\phi(U)(g))_p = \phi_p(g_p).\]
        Since the stalk maps are all isomorphisms, we have equality of germs $f_p = g_p$ for all $p$, so by Exercise 2.4.A we know that $f=g$. For surjectivity, choose $g \in \mathcal{G}(U)$. This yields a compatible family of germs in $\prod_{p \in U} \mathcal{G}_p$, and by the isomorphism also a compatible family $(f_p)_{p \in U}\mathcal{F}_p$ with $\phi_p(f_p) = g_p$ for all $p$. By Exercise 2.4.B, the family $(f_p)_{p \in U}$ comes from a section $f \in \mathcal{F}(U)$. Now using the same square as the previous exercise, we find that $g_p = \phi_p(f_p) = (\phi(U)(f))_p$, so by injectivity on the level of germs $\phi(U)(f) = g$, showing surjectivity.
    \end{proof}
\end{exer}